### 2022-11-30 DataExploratoryAnalyses.Rmd
More exploratory analyses

---
title: "Data Exploratory Analyses/Plots"
author: "Kathryn Wheeler"
date: "11/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source('sharedVariables.R')
source('NEON_Data_DownloadAndProcess.R')
```

```{r}
library(MuMIn)
library(ggplot2)
library(mgcv)
library(ggridges)

allPrecipData <- read.csv(paste0(dataPath,"NEON_PrecipitationDataDailydata_gapFilled.csv"))
allPrecipData$year <- lubridate::year(allPrecipData$date)
allPrecipData <- allPrecipData %>% group_by(year,siteID) %>% mutate(cumPrecip=cumsum(precipBulk)) #Calculates the cummulative sum of precip for each site-year for each date

allTempData <- read.csv(paste0(dataPath,"NEON_TemperatureDataDailydata_gapFilled.csv"))
allTempData$year <- lubridate::year(allTempData$date)

allTempData$GDDoffset_0 <- ifelse((allTempData$tempTripleMean-0)<0,0,allTempData$tempTripleMean-0)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_0=cumsum(GDDoffset_0))

allTempData$GDDoffset_5 <- ifelse((allTempData$tempTripleMean-5)<0,0,allTempData$tempTripleMean-5)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_5=cumsum(GDDoffset_5))

allTempData$GDDoffset_10 <- ifelse((allTempData$tempTripleMean-10)<0,0,allTempData$tempTripleMean-10)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_10=cumsum(GDDoffset_10))

allTempData$GDDoffset_15 <- ifelse((allTempData$tempTripleMean-15)<0,0,allTempData$tempTripleMean-15)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_15=cumsum(GDDoffset_15))

allTempData <- allTempData[,-c(5,7,9,11)] #Remove the offset columns to just keep cummulative

allSunlightTimes <- read.csv(paste0(dataPath,'NEON_sunlightTimes.csv'))[-c(3,4,5,6)]
```

```{r}
p <- 2 #Bud burst 
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  subDat$year <- as.numeric(subDat$year)
  subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
  subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
  subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
  subDat <- subDat %>% filter(year!=2022)
  subDat$Mycorrhizal.type <- as.factor(subDat$Mycorrhizal.type)

  #Deciduous Broadleaf
  subDatDB <- subDat %>% filter(growthForm=="Deciduous broadleaf")
  subDatDB_ECM <- subDatDB %>% filter(Mycorrhizal.type=="EcM",growthForm=="Deciduous broadleaf")
  subDatDB_AM <- subDatDB %>% filter(Mycorrhizal.type=="AM",growthForm=="Deciduous broadleaf")

  plot(density(subDatDB_AM$dayOfYear),main="Day of Year of Budburst for DB")
  lines(density(subDatDB_ECM$dayOfYear),col="red")
  legend('topleft',col=c("black","red"),legend = c("AM DB","ECM DB"),lty=1)

  ggplot(subDatDB,aes(as.numeric(as.character(dayOfYear)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Day of Year of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,200))

    ggplot(subDatDB,aes(as.numeric(as.character(dayOfYear)),Genus,fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Day of Year of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,200))

    output <- matrix(ncol=length(unique(subDatDB$Genus)),nrow=length_NEON_siteNames)
    for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      for(j in seq_along(unique(subDatDB$Genus))){
        output[s,j] <- nrow(subDatDB %>% 
                              filter(Genus==(unique(subDatDB$Genus)[j]),siteID==NEON_siteNames[s]))
      }
    }
    speciesPerSite <- data.frame(output)
    colnames(speciesPerSite) <- unique(subDatDB$Genus)
    speciesPerSite <- cbind(NEON_siteNames,speciesPerSite)

    MTperSite <- data.frame(matrix(ncol=6,nrow=length_NEON_siteNames))
    colnames(MTperSite) <- c("siteID","Total_AM_ind","Total_ECM_ind","Total_AM_gen","Total_ECM_gen","Lat")
    MTperSite$siteID <- NEON_siteNames
    for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      siteDat <- subDatDB %>% filter(siteID==NEON_siteNames[s])
      MTperSite$Total_AM_ind[s] <- sum(siteDat$Mycorrhizal.type=="AM")
      MTperSite$Total_ECM_ind[s] <- sum(siteDat$Mycorrhizal.type=="EcM")
      MTperSite$Total_AM_gen[s] <- length(unique((siteDat %>% filter(Mycorrhizal.type=="AM"))$Genus))
      MTperSite$Total_ECM_gen[s] <- length(unique((siteDat %>% filter(Mycorrhizal.type=="EcM"))$Genus))
      MTperSite$Lat[s] <- as.numeric(siteData[siteData$field_site_id==NEON_siteNames[s],'field_latitude'])
    }
    MTperSite <- MTperSite[order(MTperSite$Lat,decreasing = TRUE),]

    mdl_gam <- gam(dayOfYear ~ s(decimalLatitude,k=25) + Mycorrhizal.type,data=subDatDB,
                   method="REML",
                   na.action="na.fail")
    plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
      gam.check(mdl_gam,page=1)
    plot(subDatDB$decimalLatitude,subDatDB$dayOfYear,pch=20,xlab="Latitude",ylab="Day Of Year of Budburst")
    abline(lm(dayOfYear ~ decimalLatitude,data=subDatDB),lwd=3)
    abline(lm(dayOfYear ~ decimalLatitude,data=subDatDB[subDatDB$Mycorrhizal.type=="AM",]),lwd=3,col="cyan")
    abline(lm(dayOfYear ~ decimalLatitude,data=subDatDB[subDatDB$Mycorrhizal.type=="EcM",]),lwd=3,col="red")
    legend('bottomright',col=c("black","cyan","red"),legend = c("All DB","AM DB","ECM DB"),lty=1,lwd=3)

  concurvity(mdl_gam,full=TRUE)

  ggplot(subDatDB,aes(as.numeric(as.character(GDD_10)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_10 (C)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("GDD_10 of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,600))

      ggplot(subDatDB,aes(as.numeric(as.character(GDD_10)),as.numeric(as.character(dayOfYear)),col=Mycorrhizal.type))+geom_point(cex=.1)+
        facet_wrap(~siteID,ncol=6)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_10 (C)")+
  ylab("Day of Year of Budburst")+
        geom_smooth(method="lm")+ 
  scale_x_continuous(limits=c(0,1500))

  gdd_doy_slopes <- data.frame(matrix(nrow=length_NEON_siteNames,ncol=3))
  colnames(gdd_doy_slopes) <- c("siteID","AM_slope","ECM_slope")
  gdd_doy_slopes$siteID <- NEON_siteNames
  for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      siteDat <- subDatDB %>% filter(siteID==NEON_siteNames[s])
      if(sum(siteDat$Mycorrhizal.type=="AM")>1){
      gdd_doy_slopes$AM_slope[s] <- summary(lm(dayOfYear~GDD_10,
                                               data=siteDat[siteDat$Mycorrhizal.type=="AM",]))$coefficients[2,1]
      }
      if(sum(siteDat$Mycorrhizal.type=="EcM")>3){
      gdd_doy_slopes$ECM_slope[s] <- summary(lm(dayOfYear~GDD_10,
                                               data=siteDat[siteDat$Mycorrhizal.type=="EcM",]))$coefficients[2,1]
      }
  }
  plot(density(na.omit(gdd_doy_slopes$AM_slope)),col="cyan",main="Slopes of Site-Specific Linear Regressions Between GDD_10 and DOY of Bud Burst")
  lines(density(na.omit(gdd_doy_slopes$ECM_slope)),col="red")
  legend('topright',col=c("cyan","red"),legend = c("AM DB","ECM DB"),lty=1,lwd=3)

  dl_doy_slopes <- data.frame(matrix(nrow=length_NEON_siteNames,ncol=3))
  colnames(dl_doy_slopes) <- c("siteID","AM_slope","ECM_slope")
  dl_doy_slopes$siteID <- NEON_siteNames
  for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      siteDat <- subDatDB %>% filter(siteID==NEON_siteNames[s])
      if(sum(siteDat$Mycorrhizal.type=="AM")>1){
      dl_doy_slopes$AM_slope[s] <- summary(lm(dayOfYear~daylength,
                                               data=siteDat[siteDat$Mycorrhizal.type=="AM",]))$coefficients[2,1]
      }
      if(sum(siteDat$Mycorrhizal.type=="EcM")>3){
      dl_doy_slopes$ECM_slope[s] <- summary(lm(dayOfYear~daylength,
                                               data=siteDat[siteDat$Mycorrhizal.type=="EcM",]))$coefficients[2,1]
      }
  }
  plot(density(na.omit(dl_doy_slopes$AM_slope)),col="cyan",main="Slopes of Site-Specific Linear Regressions Between Day length and DOY of Bud Burst")
  lines(density(na.omit(dl_doy_slopes$ECM_slope)),col="red")
  legend('topright',col=c("cyan","red"),legend = c("AM DB","ECM DB"),lty=1,lwd=3)

  mdl_gam <- gam(dayOfYear ~ s(daylength, by=as.factor(siteID)) + Mycorrhizal.type,data=subDatDB,
                 method="REML",
                 na.action="na.fail")
    plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
    gam.check(mdl_gam)

    plot(subDatDB$daylength,subDatDB$dayOfYear,pch=20)
    points(subDatDB[subDatDB$Mycorrhizal.type=="EcM",'daylength'],
           subDatDB[subDatDB$Mycorrhizal.type=="EcM",'dayOfYear'],pch=20,col="red")

    points(subDatDB[subDatDB$Mycorrhizal.type=="AM",'daylength'],
           subDatDB[subDatDB$Mycorrhizal.type=="AM",'dayOfYear'],pch=20,col="cyan")

    indCts <- subDatDB %>% count(individualID)
    indCts <- left_join(indCts,subDatDB[,c('siteID',"individualID")])

    ggplot(indCts,aes(x=n))+
      geom_histogram(binwidth = 1)+
      facet_wrap(~siteID,ncol=4)+
      xlab("Number of Repeated Measurements Per Individual")+
  theme_classic()

    subDatDB2 <- subDatDB %>% group_by(individualID) %>% mutate(doy_sd=sd(dayOfYear,na.rm=TRUE))
    subDatDB2 <- subDatDB2[,c('siteID','individualID','doy_sd','decimalLatitude','Mycorrhizal.type')] %>% unique()

    ggplot(subDatDB2,aes(as.numeric(as.character(doy_sd)),
                         fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year SD")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("SD in Day Of Year of Budburst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,30))

    plot(density(na.omit(subDatDB2$doy_sd)),main="SD in DOY of bud burst for DB individuals",xlim=c(0,40))
    lines(density(na.omit(as.numeric(subDatDB2[subDatDB2$Mycorrhizal.type=="AM",]$doy_sd))),col="cyan")
    lines(density(na.omit(as.numeric(subDatDB2[subDatDB2$Mycorrhizal.type=="EcM",]$doy_sd))),col="red")
    legend('topright',col=c("black","cyan","red"),legend = c("All DB","AM DB","ECM DB"),lty=1,lwd=3)

```

```{r}
p <- 3 #Senescence
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  subDat$year <- as.numeric(subDat$year)
  subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
  subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
  subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
  subDat <- subDat %>% filter(year!=2022)
  subDat$Mycorrhizal.type <- as.factor(subDat$Mycorrhizal.type)

  #Deciduous Broadleaf
  subDatDB <- subDat %>% filter(growthForm=="Deciduous broadleaf")
  subDatDB_ECM <- subDatDB %>% filter(Mycorrhizal.type=="EcM",growthForm=="Deciduous broadleaf")
  subDatDB_AM <- subDatDB %>% filter(Mycorrhizal.type=="AM",growthForm=="Deciduous broadleaf")

    ggplot(subDatDB,aes(as.numeric(as.character(dayOfYear)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Day of Year of Senescence in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(150,400))

  ggplot(subDatDB,aes(as.numeric(as.character(GDD_15)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_15 (C)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("GDD_10 of Senescence in Deciduous Broadleaf")

```

### 2022-11-30 manuscriptCode_phenologyAndMycorrhizae.Rmd
More exploratory analyses

---
title: "Phenology and Mycorrhizae Manuscript"
author: "Kathryn Wheeler"
date: "11/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Functions and Variables
```{r}
source('sharedVariables.R')
source('NEON_Data_DownloadAndProcess.R')
```

Download NEON Data

#Single Air Temperature At Various Heights 
```{r}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)

```

#Triple Air Temperature at Top of Canopy
```{r} 
##Need to redownload!! 
dataName="NEON_TemperatureData"
NEON_ID='DP1.00003.001'
selectColumns <- c('tempTripleMean','finalQF')
inFileName <- "TAAT_30min.csv"
varName <- 'tempTripleMean'

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean)
gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)

```

#Precipitation
```{r}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)
gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)

```

#NEON Phenology Observations 
```{r}
source('combineNEONdata_PhenoObs.R')
dataName="NEON_PhenologyObservations"
NEON_ID='DP1.10055.001'

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
```

#Calculate Cummulative Weather for Each Individual phenophase intensity pair
```{r}

```

#NEON PhenoCam Observations
```{r}
source('determinePhenoCamURLs.R')
source('downloadPhenoCamAndCalculateTransitions.R') #Still need to change to have it save it somewhere

```

### 2022-11-30 calculateNEON_PhenoObs_Covariates.R

@@ -1,5 +1,6 @@
 #Calculate Cummulative Weather to Date from the start of year
 library(MuMIn)
+library(mgcv)
 
 allPrecipData <- read.csv(paste0(dataPath,"NEON_PrecipitationDataDailydata_gapFilled.csv"))
 allPrecipData$year <- lubridate::year(allPrecipData$date)
@@ -27,11 +28,13 @@ allSunlightTimes <- read.csv(paste0(dataPath,'NEON_sunlightTimes.csv'))[-c(3,4,5
 for(p in seq_along(NEON_phenophase_names)){
   print(NEON_phenophase_names[p])
   subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
   subDat$year <- as.numeric(subDat$year)
   subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
   subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
   subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
   subDat <- subDat %>% filter(year!=2022)
+  subDatDB$Mycorrhizal.type <- as.factor(subDatDB$Mycorrhizal.type)
   
   mdl <- lm(dayOfYear ~ cumPrecip + GDD_15 + daylength,data=subDat,na.action = "na.fail")
   
@@ -39,9 +42,29 @@ for(p in seq_along(NEON_phenophase_names)){
   
   #subDat <- subDat %>% group_by(individualID) %>% mutate(precip_sd=sd(cumPrecip))
   subDatECM <- subDat %>% filter(Mycorrhizal.type=="EcM",growthForm=="Deciduous broadleaf")
-  subDatAM <- subDat %>% filter(Mycorrhizal.type=="AM",growthForm=="Deciduous broadleaf")
-  mdl <- lm(dayOfYear ~ cumPrecip + GDD_15 + daylength,data=subDatECM,na.action = "na.fail")
-  dredge(mdl)
+  subDatAM <- subDatDB %>% filter(Mycorrhizal.type=="AM",growthForm=="Deciduous broadleaf")
[…]

### 2022-11-30 sharedVariables.R

@@ -24,4 +24,4 @@ siteData <- read_csv(paste0(dataPath,'NEON_Field_Site_Metadata_20220412.csv'))
 siteData <- siteData %>% filter(field_site_type%in%c("Gradient Terrestrial","Core Terrestrial"))
 
 NEON_phenophase_names <- c("Young leaves","Breaking leaf buds","Colored leaves","Increasing leaf size","Leaves","Falling leaves","Young needles","Breaking needle buds","Initial growth","Emerging needles","Colored needles","Needles","Falling needles")
-
+mediumIntensity_phenophases <- c("11 to 100","11 to 100","25-49%","25-49%","25-49%","50-74%","11 to 100","11 to 100",NA,"11 to 100","25-49%","25-49%",NA)

### 2022-12-05 DataExploratoryAnalyses.Rmd
Added specific questions to the exploratory analyses

@@
 
-```{r}
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
 source('sharedVariables.R')
@@
 
-```{r}
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
 library(MuMIn)
@@
 
+#For each site-PFT combination: How many individuals of the different associations are present?
+
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=15}
+#Number of Individuals of AM and EcM that are present
+uniqueIndividuals <- matrix(nrow=0,ncol=5)
+for(p in seq_along(NEON_phenophase_names)){
+  #Bud burst 
+  print(NEON_phenophase_names[p])
+
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat[,c('siteID','individualID','growthForm','Mycorrhizal.type','decimalLatitude')]
+  subDat <- subDat %>% unique()
+  uniqueIndividuals <- rbind(uniqueIndividuals,subDat)
+  uniqueIndividuals <- uniqueIndividuals %>% unique()
+}
+uniqueIndividuals <- uniqueIndividuals[!(uniqueIndividuals$siteID%in%c("2019","2020","2021","2017","2018","2022")),]
+#uniqueIndividuals <- uniqueIndividuals %>% filter(Mycorrhizal.type %in% c("AM","EcM"))
+uniqueIndividuals <- uniqueIndividuals %>% filter(!is.na(growthForm))
+uniqueIndividuals[uniqueIndividuals$growthForm=="Pine",'growthForm'] <- "Evergreen conifer"
+uniqueIndividuals <- uniqueIndividuals %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) #Exclude the others
+
+uniqueIndividuals2 <- uniqueIndividuals %>% group_by(siteID,Mycorrhizal.type,growthForm,decimalLatitude) %>% summarise(n=n())
+
+ggplot(uniqueIndividuals2,aes(fill=Mycorrhizal.type,y=n,x=fct_reorder(siteID,decimalLatitude))) + 
+  geom_bar(position="dodge",stat="identity")+
+  facet_wrap(~growthForm,ncol=4)+
+  theme_classic()+
+  theme(axis.text.x = element_text(angle=90))+
+  xlab("Site ID (Ordered by Latitude)")+
+  ylab("Number of Individuals")+
+  coord_flip()
+
+```
+
+What I learned is that DB has the best variation between different mycorrhizal associations so that's where I should focus my comparitive studies and then do across PFTs for the overall.
+
+#For each site-phenophase combination: how many years are individuals re-measured?
+```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10}
+for(p in seq_along(NEON_phenophase_names)){
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','year')]
+  subDat <- subDat %>% unique()
+
+  subDat2 <- subDat %>% group_by(siteID,Mycorrhizal.type,individualID,decimalLatitude) %>% summarise(n=n())
+  if(nrow(subDat2)>2){
+    print(ggplot(subDat2,aes(n,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+            geom_density_ridges2(scale=1)+
+            theme_classic()+
+            theme(axis.text.x = element_text(angle=90))+
+            xlab("Number Of Years Per Individual")+
+            ylab("Site ID (Ordered by Latitude)")+
+            ggtitle(NEON_phenophase_names[p])+
+            scale_x_continuous(limits=c(0,8)))
+  }
+}
+
+```
+
+#For each PFT-phenophase combination: Does the Standard Deviation in DOYs and lengths between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
+
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
+for(p in seq_along(NEON_phenophase_names)){
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+  subDat <- subDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm')]
+  subDat <- subDat %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Forb","Graminoid"))
+  subDat2 <- subDat %>% group_by(individualID) %>% mutate(doy_sd=sd(dayOfYear,na.rm=TRUE))
+
+  if(nrow(subDat2)>2){
+    print(ggplot(subDat2,aes(doy_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+            geom_density_ridges2(scale=1)+
+            theme_bw()+
+            theme(axis.text.x = element_text(angle=90))+
+            xlab("SD in DOY Per Individual")+
+            ylab("Site ID (Ordered by Latitude)")+
+            facet_wrap(~growthForm)+
+            ggtitle(NEON_phenophase_names[p])+
+            scale_x_continuous(limits=c(0,100)))
+  }
+}
+
+#Lengths Between Phenophases:
+
+```
+
+#For each PFT-phenophase combination: Does the DOY of the timing and the lengths between phenophases differ between EcM and AM assocated plants across all sites and within each site?
+
 ```{r}
+
+```
+
+#For each individual and phenophase, what predictors seem to be the most important?
+
+```{r}
+
+```
+
+#Do the basic GAMs work for any of the phenophase and PFTs?
+
+```{r}
+
+```
+
+```{r,eval=FALSE}
 p <- 2 #Bud burst 
@@
 
-    indCts <- subDatDB %>% count(individualID)
-    indCts <- left_join(indCts,subDatDB[,c('siteID',"individualID")])
-
-    ggplot(indCts,aes(x=n))+
-      geom_histogram(binwidth = 1)+
-      facet_wrap(~siteID,ncol=4)+
-      xlab("Number of Repeated Measurements Per Individual")+
-  theme_classic()
-
     subDatDB2 <- subDatDB %>% group_by(individualID) %>% mutate(doy_sd=sd(dayOfYear,na.rm=TRUE))
@@
 
-```{r}
+```{r,eval=FALSE}
 p <- 3 #Senescence

### 2022-12-05 sharedVariables.R

@@ -25,3 +25,4 @@ siteData <- siteData %>% filter(field_site_type%in%c("Gradient Terrestrial","Cor
 
 NEON_phenophase_names <- c("Young leaves","Breaking leaf buds","Colored leaves","Increasing leaf size","Leaves","Falling leaves","Young needles","Breaking needle buds","Initial growth","Emerging needles","Colored needles","Needles","Falling needles")
 mediumIntensity_phenophases <- c("11 to 100","11 to 100","25-49%","25-49%","25-49%","50-74%","11 to 100","11 to 100",NA,"11 to 100","25-49%","25-49%",NA)
+NEON_PFTs <- c("Deciduous broadleaf","Semi-evergreen broadleaf","Evergreen broadleaf","Drought deciduous broadleaf","Graminoid","Forb","Evergreen conifer","Semi-evergreen forb","Pine","Deciduous conifer")

### 2022-12-06 DataExploratoryAnalyses.Rmd
More exploratory analyses

@@
 source('NEON_Data_DownloadAndProcess.R')
-```
-
-```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
 library(MuMIn)
@@
 library(ggridges)
+```
 
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
 allPrecipData <- read.csv(paste0(dataPath,"NEON_PrecipitationDataDailydata_gapFilled.csv"))
@@
 
-#For each site-phenophase combination: how many years are individuals re-measured?
+#For each phenophase, what growth forms (PFT) are measured?
+```{r,echo=FALSE,message=FALSE,warning=FALSE}
+allDat <- matrix(nrow=0,ncol=6)
+for(p in seq_along(NEON_phenophase_names)){
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat[,c('siteID','individualID','growthForm','decimalLatitude','year','phenophaseName')]
+  subDat <- subDat %>% unique() %>% filter(!is.na(growthForm))
+  allDat <- rbind(allDat,subDat)
+}
+  allDat <- allDat %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf"))
+
+  growthFormTotal <- allDat %>% group_by(growthForm) %>% summarise(growthFormTotal=n())
+  allDat <- left_join(allDat,growthFormTotal,by="growthForm")
+
+  allDat2 <- allDat %>% group_by(phenophaseName,growthForm,growthFormTotal) %>% summarise(n=(n()))
+  # ggplot(allDat2,aes(n,phenophaseName,fill=growthForm)) +
+  #           geom_bar(position="dodge",stat="identity")+
+  #           scale_fill_brewer(palette="Accent")+
+  #           theme_classic()+
+  #           theme(axis.text.x = element_text(angle=90))+
+  #           xlab("Number Of Total Measurements (Ratio of Total Per Growth Form")+
+  #           ylab("Phenophase")+
+  #           ggtitle(NEON_phenophase_names[p])
+
+    ggplot(allDat2,aes((n/growthFormTotal),growthForm,fill=phenophaseName)) +
+            geom_bar(position="dodge",stat="identity")+
+            scale_fill_brewer(palette="Set3")+
+            theme_classic()+
+            theme(axis.text.x = element_text(angle=90))+
+            xlab("Number Of Total Measurements (Ratio of Total Per Growth Form)")+
+            ylab("Growth Form")+
+            ggtitle("Which Phenophases are Monitored for with Growth Forms")
+
+```
+
+#For each site-phenophase combination: how many years are individuals re-measured by mycorrhizae type?
 ```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10}
@@
 
-#For each PFT-phenophase combination: Does the Standard Deviation in DOYs and lengths between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
+#For each PFT-phenophase combination: Does the timing and Standard Deviation in DOYs differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
 
@@
 
-#Lengths Between Phenophases:
-
 ```
 
-#For each PFT-phenophase combination: Does the DOY of the timing and the lengths between phenophases differ between EcM and AM assocated plants across all sites and within each site?
+#For each PFT-phenophase combination: Does the length and Standard Deviation differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
 
-```{r}
+##There are various definitions of growing season length depending on PFT:
+*Semi-evergreen broadleaf: budburst-colored; leaves (varying intensities); Young-leaves-colored
+*Graminoid: leaves (varying intensities)
+*Forb: leaves (varying intensities); Young-leaves-colored
+*Evergreen conifer: No lengths
+*Evergreen broadleaf: No lengths
+*Drought deciduous broadleaf: leaves (varying intensities); young leaves-colored leaves
+*Deciduous broadleaf: leaves (varying intensities); budburst-colored
+
+##Different definitions of growing season length:
+*Budburst-colored: semi-evergreen broadleaf; deciduous broadleaf
+*Leaf presence: semi-evergreen broadleaf; graminoid; forb; drought deciduous broadleaf; deciduous broadleaf
+*Young-leaves-colored:semi-evergreen broadleaf; forb; drought-deciduous broadleaf
+
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
+for(initialP in c(1,2)){
+  p=initialP
+  budBurstDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  budBurstDat <- budBurstDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+
+  budBurstDat <- budBurstDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')] %>% mutate(winterYear=as.numeric(year),year=as.numeric(year))
+
+  p=3
+  coloredLeavesDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  coloredLeavesDat <- coloredLeavesDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+
+  coloredLeavesDat <- coloredLeavesDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')]%>% mutate(winterYear=(year+1),year=as.numeric(year))
+
+  winterLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
+                            by=c("winterYear","individualID",'siteID',"Mycorrhizal.type","decimalLatitude",
+                                     "growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf"))%>%
+    mutate(winterLength=as.Date(date.y)-as.Date(date.x)) %>%
+    group_by(individualID) %>% mutate(winter_sd=sd(winterLength,na.rm=TRUE)) %>%
+    ungroup() %>%
+    dplyr::select(individualID,winter_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
+
+  summerLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
+                                by=c("year","individualID",'siteID',"Mycorrhizal.type",
+                                     "decimalLatitude","growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) %>%
+    mutate(summerLength=as.Date(date.x)-as.Date(date.y)) %>%
+    group_by(individualID) %>% mutate(summer_sd=sd(summerLength,na.rm=TRUE))%>%
+    ungroup() %>%
+    dplyr::select(individualID,summer_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
+
+  print(ggplot(winterLengthDat,
+         aes(winter_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+    geom_density_ridges2(scale=1)+
+    theme_bw()+
+    theme(axis.text.x = element_text(angle=90))+
+    xlab("SD")+
+    ylab("Site ID (Ordered by Latitude)")+
+    facet_wrap(~growthForm)+
+    ggtitle(paste("SD in Winter Length Per Individual: Colored-",NEON_phenophase_names[initialP]))+
+    scale_x_continuous(limits=c(0,100)))
+}
+# #Based on Leaf Numbers
+# leavesDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+# initialGrowth <- leavesDat %>% filter(phenophaseIntensity=="5-")
 
@@
 ```{r}
+p=5
 

### 2022-12-06 manuscriptCode_phenologyAndMycorrhizae.Rmd
More exploratory analyses

@@
 combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
+combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
 ```

### 2022-12-06 combineNEONdata_PhenoObs.R

@@ -41,6 +41,11 @@ combineNEONdata_PhenoObs <- function(saveType=""){
       subDat <- allPhenoObsDat %>% filter(phenophaseName==NEON_phenophase_names[p],phenophaseStatus=="yes",phenophaseIntensity!="") %>% group_by(individualID,phenophaseIntensity,year) %>% slice(1:1)
       write.csv(subDat,file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'),row.names=FALSE,quote=FALSE)
     }
+  }else if(saveType=="allOfPhenophase"){
+    p <- 5 #Just done for the Leaves phenophase
+    print(NEON_phenophase_names[p])
+    subDat <- allPhenoObsDat %>% filter(phenophaseName==NEON_phenophase_names[p],phenophaseStatus=="yes",phenophaseIntensity!="")
+    write.csv(subDat,file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_AllIntensities_',gsub(" ","",NEON_phenophase_names[p]),'.csv'),row.names=FALSE,quote=FALSE)
   }
 
 }

### 2022-12-28 DataExploratoryAnalyses.Rmd
Working on exploratory analyses

@@
 
+#Load Covariate Data
 ```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
@@
 
+What I learned: Measured phenophases differ a lot by PFT. Evergreen don't have an end of growing season measurement. Many just have leaves as their changing phenophase.
+
 #For each site-phenophase combination: how many years are individuals re-measured by mycorrhizae type?
@@
 
-#For each PFT-phenophase combination: Does the timing and Standard Deviation in DOYs differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
+What I learned: There aren't large sample sizes per individual and the sample sizes range between 1 and 8.
+
+#For each PFT-phenophase combination: Does the timing in DOYs differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
+
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
+for(p in seq_along(NEON_phenophase_names)){
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+  subDat <- subDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm')]
+  subDat <- subDat %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Forb","Graminoid"))
+
+  if(nrow(subDat)>2){
+    print(ggplot(subDat,aes(dayOfYear,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+            geom_density_ridges2(scale=1)+
+            theme_bw()+
+            theme(axis.text.x = element_text(angle=90))+
+            xlab("DOY")+
+            ylab("Site ID (Ordered by Latitude)")+
+            facet_wrap(~growthForm)+
+            ggtitle(NEON_phenophase_names[p]))
+          #+
+           # scale_x_continuous(limits=c(0,100)))
+  }
+}
+
+```
+
+What I learned: For most sites, AM budburst earlier and senescened earlier than ECM
+
+#For each PFT-phenophase combination: Does the Standard Deviation in DOYs differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
 
@@
 
-#For each PFT-phenophase combination: Does the length and Standard Deviation differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
+What I learned: EcM seem maybe have less sd in timing in budburst. SD in Colored leaves doesn't seem to differ as much between mycorrhizae types.
+
+New question: Do they break buds earlier when corrected for site or latitude effects?
+
+#For each PFT-phenophase combination: Does the length of winter and summer differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
 
@@
 *Young-leaves-colored:semi-evergreen broadleaf; forb; drought-deciduous broadleaf
+
+```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
+for(initialP in c(1,2)){
+  p=initialP
+  budBurstDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  budBurstDat <- budBurstDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+
+  budBurstDat <- budBurstDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')] %>% mutate(winterYear=as.numeric(year),year=as.numeric(year))
+
+  p=3
+  coloredLeavesDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  coloredLeavesDat <- coloredLeavesDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+
+  coloredLeavesDat <- coloredLeavesDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')]%>% mutate(winterYear=(year+1),year=as.numeric(year))
+
+  winterLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
+                            by=c("winterYear","individualID",'siteID',"Mycorrhizal.type","decimalLatitude",
+                                     "growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf"))%>%
+    mutate(winterLength=as.Date(date.y)-as.Date(date.x))
+
+  summerLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
+                                by=c("year","individualID",'siteID',"Mycorrhizal.type",
+                                     "decimalLatitude","growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) %>%
+    mutate(summerLength=as.Date(date.x)-as.Date(date.y))
+
+  print(ggplot(winterLengthDat,
+         aes(winterLength,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+    geom_density_ridges2(scale=1)+
+    theme_bw()+
+    theme(axis.text.x = element_text(angle=90))+
+    xlab("Winter Length (days)")+
+    ylab("Site ID (Ordered by Latitude)")+
+    facet_wrap(~growthForm)+
+    ggtitle(paste("Winter Length Per Individual: Colored-",NEON_phenophase_names[initialP])))
+
+    print(ggplot(summerLengthDat,
+         aes(summerLength,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+    geom_density_ridges2(scale=1)+
+    theme_bw()+
+    theme(axis.text.x = element_text(angle=90))+
+    xlab("Summer Length (days)")+
+    ylab("Site ID (Ordered by Latitude)")+
+    facet_wrap(~growthForm)+
+    ggtitle(paste("Summer Length Per Individual: Colored-",NEON_phenophase_names[initialP])))
+
+}
+# #Based on Leaf Numbers
+# leavesPhenophases <- determinePhenophaseTimingForLeaves(dataPath) %>% 
+#   filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) 
+# 
+# greenupDat <- leavesPhenophases %>% dplyr::select(-c(greendownDate,greendownDOY)) %>%
+#   mutate(winterYear=(year),year=as.numeric(year))
+# greendownDat <- leavesPhenophases %>% dplyr::select(-c(greenupDate,greenupDOY)) %>%
+#   mutate(winterYear=(year+1),year=as.numeric(year))
+# 
+# winterLengthDat <- inner_join(greendownDat,greenupDat,
+#                                 by=c("winterYear","individualID",'siteID',"Mycorrhizal.type",
+#                                      "decimalLatitude","growthForm")) %>%
+#   mutate(winterLength=as.Date(greenupDate)-as.Date(greendownDate)) %>%
+#     group_by(individualID) %>% mutate(winter_sd=sd(winterLength,na.rm=TRUE)) %>%
+#     ungroup() %>%
+#     dplyr::select(individualID,winter_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
+#   
+#   summerLengthDat <- inner_join(greendownDat,greenupDat,
+#                                 by=c("year","individualID",'siteID',"Mycorrhizal.type",
+#                                      "decimalLatitude","growthForm")) %>%
+#   mutate(summerLength=as.Date(greendownDate)-as.Date(greenupDate)) %>%
+#     group_by(individualID) %>% mutate(summer_sd=sd(summerLength,na.rm=TRUE)) %>%
+#     ungroup() %>%
+#     dplyr::select(individualID,summer_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
+#   
+#   ggplot(winterLengthDat,
+#          aes(winter_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+#     geom_density_ridges2(scale=1)+
+#     theme_bw()+
+#     theme(axis.text.x = element_text(angle=90))+
+#     xlab("SD")+
+#     ylab("Site ID (Ordered by Latitude)")+
+#     facet_wrap(~growthForm)+
+#     ggtitle(paste("SD in Winter Length Per Individual: Number of Leaves"))+
+#     scale_x_continuous(limits=c(0,50))
+#   
+#     ggplot(summerLengthDat,
+#          aes(summer_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+#     geom_density_ridges2(scale=1)+
+#     theme_bw()+
+#     theme(axis.text.x = element_text(angle=90))+
+#     xlab("SD")+
+#     ylab("Site ID (Ordered by Latitude)")+
+#     facet_wrap(~growthForm)+
+#     ggtitle(paste("SD in Summer Length Per Individual: Number of Leaves"))+
+#     scale_x_continuous(limits=c(0,50))
+#
+
+```
+
+What I learned: EcM maybe has a slightly shorter winter and AM maybe has a slightly shorter summer.
+
+#For each PFT-phenophase combination: Does the SD of winter and summer lengths differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?
 
@@
     scale_x_continuous(limits=c(0,100)))
+
+    print(ggplot(summerLengthDat,
+         aes(summer_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+    geom_density_ridges2(scale=1)+
+    theme_bw()+
+    theme(axis.text.x = element_text(angle=90))+
+    xlab("SD")+
+    ylab("Site ID (Ordered by Latitude)")+
+    facet_wrap(~growthForm)+
+    ggtitle(paste("SD in Summer Length Per Individual: Colored-",NEON_phenophase_names[initialP]))+
+    scale_x_continuous(limits=c(0,100)))
 }
-# #Based on Leaf Numbers
-# leavesDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
-# initialGrowth <- leavesDat %>% filter(phenophaseIntensity=="5-")
 
 ```
+
+What I learned: The standard deviations in winter and summer lengths don't really seem to differ between EcM and AM.
 
@@
 ```{r}
+p <- 2 #Bud burst 
+  print(NEON_phenophase_names[p])
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],
+                              growthForm=="Deciduous broadleaf")
+  subDat$year <- as.numeric(subDat$year)
+
+  allIndividuals <- unique(subDat$individualID)
+  subDat <- subDat %>% dplyr::select(siteID,date,dayOfYear,individualID,canopyPosition,
+                           height,growthForm,Mycorrhizal.type,year)
+
+  allOutput <- matrix(nrow=0,ncol=10)
+  colnames(allOutput) <- c('siteID','date','dayOfYear','individualID',
+                           'canopyPosition','height','growthForm',
+                           'Mycorrhizal.type','year','phenophaseOccurred')
+  for(i in seq_along(allIndividuals)){
+    if(i %% 100==0){
+      print(i)
+    }
+    subSubDat <- subDat %>% filter(individualID==allIndividuals[i])
+    for(j in 1:nrow(subSubDat)){
+      currentRow <- subSubDat[j,]
+      newOutput <- currentRow %>% slice(rep(1:n(), each = (subSubDat$dayOfYear[j]-1)))
+      newOutput <- as.data.frame(newOutput)
+      newOutput$date <- seq((as.Date(currentRow$date)-currentRow$dayOfYear+1),
+                            (as.Date(currentRow$date)-1),by="day")
+      newOutput$dayOfYear <- as.integer(row.names(newOutput))
+      newOutput$phenophaseOccurred <- FALSE
+      currentRow$phenophaseOccurred <- TRUE
+      newOutput <- rbind(newOutput,currentRow)
+      newOutput <- newOutput[(max((nrow(newOutput)-29),0)):nrow(newOutput),]
+
+      allOutput <- rbind(allOutput,newOutput)
+    }
+
+  }
+  OGallOutput <- allOutput
+  allOutput$date <- as.character(as.Date(allOutput$date))
+  allOutput <- left_join(allOutput,allPrecipData[,-3],by=c('siteID','date','year'))
+  allOutput <- left_join(allOutput,allTempData,by=c('siteID','date','year'))
+  allOutput <- left_join(allOutput,allSunlightTimes,by=c('siteID','date'))
+  allOutput <- allOutput %>% filter(year!=2022)
+  allOutput$Mycorrhizal.type <- as.factor(allOutput$Mycorrhizal.type)
+
+  #Deciduous Broadleaf
+  subDatDB <- allOutput %>% filter(growthForm=="Deciduous broadleaf",canopyPosition %in% c("Mostly shaded","Partially shaded","Full sun","Full shade"))
+
+  # mdl_gam1 <- gam(dayOfYear ~ s(GDD_15,k=10) + s(GDD_5,k=10) + s(GDD_0,k=10) + s(GDD_10,k=10),data=subDatDB,
+  #                  method="REML",
+  #                  na.action="na.fail")
+
+  mdl_gam <- gam(phenophaseOccurred ~ s(GDD_10) + s(daylength),data=subDatDB,
+                   method="REML",
+                   na.action="na.fail")
+
+  mdl <- lm <- lm(phenophaseOccurred ~ (GDD_10) + (daylength),data=subDatDB)
+  #######********Editing here: How to get it to predict a categorical response variable?****
+
+  gam.check(mdl_gam,page=1)
+  plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
+  gam.check(mdl_gam1,page=1)
+
+  plot(subDatDB$daylength,subDatDB$dayOfYear,pch=20)
+  plot(subDatDB$GDD_5,subDatDB$dayOfYear,pch=20)
+  plot(subDatDB$cumPrecip,subDatDB$dayOfYear,pch=20)
+
+  mdl_gam2 <- gam(dayOfYear ~ s(daylength,by=Mycorrhizal.type) + s(GDD_10,by=Mycorrhizal.type) + s(cumPrecip,by=Mycorrhizal.type) + ,data=subDatDB,
+                   method="REML",
+                   na.action="na.fail")
+
+    plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
+      gam.check(mdl_gam1,page=1)
 

### 2023-01-03 DataExploratoryAnalyses.Rmd
More exploratory analyses including correlations between NEON soil microbe biodiversity and phenocam.

@@
 
+#For each site, do the covariates that occur with each phenophase differ between MTs? 
+```{r}
+p <- 2 #Bud burst 
+  print(NEON_phenophase_names[p])
+  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],
+                              growthForm=="Deciduous broadleaf")
+  subDat$year <- as.numeric(subDat$year)
+  subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
+  subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
+  subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
+
+  ggplot(subDat,aes(as.numeric(as.character(GDD_10)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+  geom_density_ridges2(scale=1)+
+  theme_classic()+
+  theme(axis.text.x = element_text(angle=90))+
+  xlab("GDD_10 (C)")+
+  ylab("Site ID (Ordered by Latitude)")+
+    ggtitle("GDD_10 of Bud Burst in Deciduous Broadleaf")+
+  scale_x_continuous(limits=c(0,600))
+
+    ggplot(subDat,aes(as.numeric(as.character(GDD_5)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+  geom_density_ridges2(scale=1)+
+  theme_classic()+
+  theme(axis.text.x = element_text(angle=90))+
+  xlab("GDD_5 (C)")+
+  ylab("Site ID (Ordered by Latitude)")+
+    ggtitle("GDD_5 of Bud Burst in Deciduous Broadleaf")+
+  scale_x_continuous(limits=c(0,600))
+
+  ggplot(subDat,aes(as.numeric(as.character(daylength)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+  geom_density_ridges2(scale=1)+
+  theme_classic()+
+  theme(axis.text.x = element_text(angle=90))+
+  xlab("Daylength (hours)")+
+  ylab("Site ID (Ordered by Latitude)")+
+    ggtitle("Daylength of Bud Burst in Deciduous Broadleaf")
+
+    ggplot(subDat,aes(as.numeric(as.character(height)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
+  geom_density_ridges2(scale=1)+
+  theme_classic()+
+  theme(axis.text.x = element_text(angle=90))+
+  xlab("Plant Height")+
+  ylab("Site ID (Ordered by Latitude)")+
+    ggtitle("Plant Height in Deciduous Broadleaf")
+
+```
+
+What I learned: I don't really see patterns in if a MT covariates varied more for one that the other.
+
+AM-associated plants are shorter than the EcM-associated ones so the earlier budburst is really just like because they are understory plants. Well crap.
+
 #Do the basic GAMs work for any of the phenophase and PFTs?
@@
 
+#Is phenology correlated with soil microbial biodiversity? 
+```{r}
+allBioDat <- read.csv(paste0(dataPath,dataName,"/soilMicrobediversityData.csv"))
+
+allPlotIDLatLong <- matrix(nrow=0,ncol=3)
+for(s in seq_along(NEON_siteNames)){
+  print(NEON_siteNames[s])
+  files <- dir(path=paste0(dataPath,'NEON_presence-cover-plant-CLEAN'),
+               pattern=NEON_siteNames[s])
+  for(f in 1:5){
+    subDat <- read.csv(paste0(dataPath,'NEON_presence-cover-plant-CLEAN/',files[f]))[,c('decimalLatitude','decimalLongitude','plotID')] %>% unique()
+    allPlotIDLatLong <- rbind(allPlotIDLatLong,subDat)
+  }
+}
+
+allPlotIDLatLong <- allPlotIDLatLong %>% unique()
+allBioDat <- left_join(allBioDat,allPlotIDLatLong,by="plotID")
+
+phenoCamURLs <- read.csv(paste0(dataPath,'phenocamURLS.csv'))
+
+files <- dir(path=paste0(dataPath,'phenoCamData'),pattern="dates")
+allPCdat <- matrix(nrow=0,ncol=19)
+for(f in seq_along(files)){
+  subDat <- read.csv(paste0(dataPath,'phenoCamData/',files[f]),skip=16) %>%
+    filter(gcc_value=="gcc_90")
+  allPCdat <- rbind(allPCdat,subDat)
+
+}
+allPCdat_cleaned <- matrix(nrow=0,ncol=8)
+subDat <- allPCdat[,c('site','veg_type','roi_id','direction',
+                                                   'transition_15','transition_15_lower_ci',
+                                                   'transition_15_upper_ci')]
+colnames(subDat) <- c('site','veg_type','roi_id','direction',
+                                                   'date','lower_ci',
+                                                   'upper_ci')
+subDat$transition <- 15
+allPCdat_cleaned <- rbind(allPCdat_cleaned,subDat)
+subDat <- allPCdat[,c('site','veg_type','roi_id','direction',
+                                                   'transition_50','transition_50_lower_ci',
+                                                   'transition_50_upper_ci')]
+colnames(subDat) <- c('site','veg_type','roi_id','direction',
+                                                   'date','lower_ci',
+                                                   'upper_ci')
+subDat$transition <- 50
+allPCdat_cleaned <- rbind(allPCdat_cleaned,subDat)
+subDat <- allPCdat[,c('site','veg_type','roi_id','direction',
+                                                   'transition_85','transition_85_lower_ci',
+                                                   'transition_85_upper_ci')]
+colnames(subDat) <- c('site','veg_type','roi_id','direction',
+                                                   'date','lower_ci',
+                                                   'upper_ci')
+subDat$transition <- 85
+allPCdat_cleaned <- rbind(allPCdat_cleaned,subDat)
+allPCdat_cleaned$siteID <- sapply(strsplit(as.character(allPCdat_cleaned$site), "[.]"), `[`, 3)
+allPCdat_cleaned <- left_join(allPCdat_cleaned,allTempData,by=c('siteID','date'))
+allPCdat_cleaned <- left_join(allPCdat_cleaned,allSunlightTimes,by=c('siteID','date'))
+allPCdat_cleaned <- left_join(allPCdat_cleaned,allPrecipData,by=c('siteID','date','year'))
+
+phenoCam_siteData <- read.csv(paste0(dataPath,"NEON_PhenoCam_SiteData.csv"))
+phenoCam_siteData$siteID <- sapply(strsplit(as.character(phenoCam_siteData$phenoCamID), "[.]"), `[`, 3)
+
+allPlotIDLatLong$difference <- NA
+allPlotIDLatLong$siteID <- sapply(strsplit(as.character(allPlotIDLatLong$plotID), "_"), `[`, 1)
+allPlotIDLatLong <- left_join(allPlotIDLatLong,phenoCam_siteData,by="siteID")
+allPlotIDLatLong$direction[is.na(allPlotIDLatLong$direction)] <- "N" #Assume missing directions are North because most cameras are pointed North
+allPlotIDLatLong[allPlotIDLatLong$direction=="N",'difference'] <- allPlotIDLatLong[allPlotIDLatLong$direction=="N",'decimalLatitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="N",'Lat']
+
+allPlotIDLatLong[allPlotIDLatLong$direction=="W",'difference'] <- allPlotIDLatLong[allPlotIDLatLong$direction=="W",'decimalLongitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="W",'Lon']
+
+allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'difference'] <- sqrt((allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'decimalLongitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'Lon'])**2 + (allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'decimalLatitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'Lat'])**2)
+
+allPlotIDLatLong_filtered <- allPlotIDLatLong[allPlotIDLatLong$difference>0,] %>%
+  filter(direction!="NNE") #Deal with NNE later because it's more complicated because latitude and longitude differences have to be positive
+
+allPlotIDLatLong_filtered <- allPlotIDLatLong_filtered %>% group_by(siteID) %>%
+  slice(which.min(difference))
+
+allBioDat_plotFiltered <- allBioDat %>% 
+  filter(plotID %in% allPlotIDLatLong_filtered$plotID) %>%
+  mutate(year=lubridate::year(date))%>%
+  group_by(year,siteID) %>%
+  summarise(year_totalSpecies=sum(totalSpecies),year_totalIndividual=sum(totalIndividuals))
+
+allBioDat_plotFiltered$biodiversity <- allBioDat_plotFiltered$year_totalSpecies/allBioDat_plotFiltered$year_totalIndividual
+
+allPCdat_cleaned_15 <- allPCdat_cleaned %>% filter(direction=="rising",transition==15,veg_type=="DB")
+
+allBioDat_plotFiltered_15 <- left_join(allBioDat_plotFiltered,allPCdat_cleaned_15,by=c('year','siteID'))
+
+plot(allBioDat_plotFiltered_15$biodiversity,allBioDat_plotFiltered_15$GDD_0,pch=20)
+mdl <- lm(GDD_0~biodiversity,data = allBioDat_plotFiltered_15)
+abline(mdl)
+summary(mdl)
+
+```
+
+What I learned: There might be some positive correlations between soil microbe biodiversity and phenocam, but there aren't enough site-years to test because soil microbe data started years before phenocam, but is 4 years delayed.
+
+#Extra Code
 ```{r,eval=FALSE}

### 2023-01-03 manuscriptCode_phenologyAndMycorrhizae.Rmd
More exploratory analyses including correlations between NEON soil microbe biodiversity and phenocam.

@@
 
-#Calculate Cummulative Weather for Each Individual phenophase intensity pair
+#Download NEON Soil Microbe Data
 ```{r}
+dataName="NEON_SoilMicrobeComposition"
+NEON_ID='DP1.10081.001'
+selectColumns <-
+inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
+varName <-
 
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #Note: I had to modify this function to remove the indices for sites that didn't seem to have data. 
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
 ```

### 2023-01-03 combineNEONdata_PhenoObs.R

@@ -50,6 +50,29 @@ combineNEONdata_PhenoObs <- function(saveType=""){
 
 }
 
+determinePhenophaseTimingForLeaves <- function(dataPath){
+  p <- 5
+  phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_AllIntensities_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+  lowIntDat <- phenoDat %>% filter(phenophaseIntensity == "5-24%") %>% dplyr::select(-c(phenophaseIntensity,phenophaseStatus,phenophaseIntensityDefinition))
+  greenUpDat <- lowIntDat %>% group_by(individualID,year) %>% slice(1:1) %>% rename(greenupDate=date,greenupDOY=dayOfYear)
+  
+  highIntDat <- phenoDat %>% filter(phenophaseIntensity == "75-94%") %>% 
+    dplyr::select(-c(phenophaseIntensity,phenophaseStatus,phenophaseIntensityDefinition)) %>% 
+    group_by(individualID,year) %>% slice(1:1)
+  
+  greenDownDat <- full_join(lowIntDat,highIntDat,by=c('siteID','plotID','individualID','decimalLatitude',
+                                                      'decimalLongitude','elevation','scientificName','growthForm','Genus','Mycorrhizal.type','year')) %>% 
+    filter(date.x > date.y) %>% 
+    group_by(individualID,year) %>% 
+    slice(1:1) %>%
+    ungroup() %>%
+    dplyr::select(-date.y) %>%
+    rename(greendownDate=date.x,greendownDOY=dayOfYear.x) %>%
+    dplyr::select(individualID,year,greendownDate,greendownDOY)
+  
+  leavesPhenophases <- full_join(greenUpDat,greenDownDat,by=c('individualID','year'))
+  return(leavesPhenophases)
+}
 
 s=14
 pheDat <- read.csv(paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',NEON_siteNames[s],'.csv'))

### 2023-01-03 downloadPhenoCamAndCalculateTransitions.R

@@ -15,7 +15,7 @@ for(i in 1:nrow(phenoCamURLs)){ #issue: 16,20
   df <- read_phenocam(file.path(tempdir(),
                                 paste0(phenoCamURLs$phenocam_id[i],"_",
                                        phenoCamURLs$ROI[i],"_1day.csv")))
-  phenophases(df,out_dir = paste0(dataPath,'phenoCamData'),internal=FALSE,
+  test <- phenophases(df,out_dir = paste0(dataPath,'phenoCamData'),internal=FALSE,
               lower_thresh=0.15,middle_thresh=0.50,upper_thresh=0.85)
 }
 

### 2023-01-10 sharedVariables.R
testing2

@@ -9,7 +9,6 @@ library("geoNEON")
 library('suncalc')
 library(daymetr)
 
-
 #library(inborutils)
 options(stringsAsFactors=FALSE)
 NEON_siteNames <- c("ABBY","BARR","BART","BLAN","BONA","CLBJ","CPER","DCFS","DEJU","DELA","DSNY","GRSM","GUAN","HARV",

### 2023-01-10 sharedVariables.R
testing4

@@ -9,6 +9,7 @@ library("geoNEON")
 library('suncalc')
 library(daymetr)
 
+
 #library(inborutils)
 options(stringsAsFactors=FALSE)
 NEON_siteNames <- c("ABBY","BARR","BART","BLAN","BONA","CLBJ","CPER","DCFS","DEJU","DELA","DSNY","GRSM","GUAN","HARV",

### 2023-01-10 DataExploratoryAnalyses.Rmd
Downloading more NEON data

@@
 
-```{r}
+```{r,eval=FALSE}
 p <- 2 #Bud burst 
@@
 ```{r}
+dataName <- "NEON_SoilMicrobeComposition"
 allBioDat <- read.csv(paste0(dataPath,dataName,"/soilMicrobediversityData.csv"))
@@
 
-allPCdat_cleaned_15 <- allPCdat_cleaned %>% filter(direction=="rising",transition==15,veg_type=="DB")
+transitions <- c(15,50,85)
+t=1
 
-allBioDat_plotFiltered_15 <- left_join(allBioDat_plotFiltered,allPCdat_cleaned_15,by=c('year','siteID'))
+par(mfrow=c(2,3))
+for(drt in c("rising","falling")){
+  for(t in seq_along(transitions)){
+    allPCdat_cleaned_trans <- allPCdat_cleaned %>% 
+      filter(direction==drt,transition==transitions[t],veg_type=="DB")
+    allBioDat_plotFiltered_trans <- left_join(allBioDat_plotFiltered,allPCdat_cleaned_trans,by=c('year','siteID'))
 
-plot(allBioDat_plotFiltered_15$biodiversity,allBioDat_plotFiltered_15$GDD_0,pch=20)
-mdl <- lm(GDD_0~biodiversity,data = allBioDat_plotFiltered_15)
+    mdl <- lm(GDD_5~biodiversity,data = allBioDat_plotFiltered_trans)
+    sm <- summary(mdl)
+    plot(allBioDat_plotFiltered_trans$biodiversity,allBioDat_plotFiltered_trans$GDD_5,pch=20,
+         ylab="Biodiversity",xlab=paste0("GDD_5 at ",transitions[t],"% ",drt),main=paste("p-value on slope:",round(sm$coefficients[2,4],digits=3)))
+
     abline(mdl)
     summary(mdl)
+  }
+}
 
+par(mfrow=c(1,1))
 ```

### 2023-01-10 manuscriptCode_phenologyAndMycorrhizae.Rmd
Downloading more NEON data

@@
 NEON_ID='DP1.10081.001'
-selectColumns <-
+#selectColumns <-
 inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
-varName <-
+#varName <-
 
@@
                 inFileName=inFileName,dataPath=dataPath)
+```
+
+#Download NEON Soil Physical and Chemical Properties
+```{r}
+dataName <- "NEON_soilProperties"
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+NEON_ID <- "DP1.10086.001"
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+#inFileNames <- c(,"sls_soilMoisture","sls_soilpH")
+inFileName <- "sls_soilCoreCollection.csv"
+selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
+                   'soilTemp','litterDepth','sampleTopDepth','sampleBottomDepth')
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+inFileName <- "sls_soilpH.csv"
+selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH','pHSoilInWaterMass','pHWaterVol',
+                   'waterpHRatio','pHSoilInCaClMass','pHCaClVol','caclpHRatio')
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))
+
+inFileName <- "sls_soilMoisture.csv"
+selectColumns <- c('plotID','horizon','boatMass','freshMassBoatMass','dryMassBoatMass','soilMoisture','dryMassFraction')
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))
+
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allData,row.names = FALSE,quote=FALSE)
+
+```
+
+#Download Photosynthetically active radiation (PAR)
+```{r}
+dataName="NEON_PAR"
+NEON_ID='DP1.00024.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+# selectColumns <- c('precipBulk','precipExpUncert','precipQF')
+# inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
+# varName <- "precipBulk"
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
+
 ```

### 2023-01-10 NEON_Data_DownloadAndProcess.R

@@ -16,16 +16,19 @@ downloadNEONdata <- function(dataName,NEON_ID){
   }
 }
 
-combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath){
+combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath,saveFile=TRUE){
   allData <- matrix(nrow=0,ncol=(length(selectColumns)+2))
   IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
   if(length(inFileName)==1){
-  for(s in seq_along(NEON_siteNames)){
-    print(NEON_siteNames[s])
-    subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))
-    
-    allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])
-  }
+    for(s in seq_along(NEON_siteNames)){
+      print(NEON_siteNames[s])
+      subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))
+      if(dataName=="NEON_soilProperties"){
+        allData <- rbind(allData,subDat[,c('siteID','collectDate',selectColumns)])
+      }else{
+        allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])
+      }
+    }
   }else if(length(inFileName)==2){
     for(s in seq_along(NEON_siteNames)){
       print(NEON_siteNames[s])
@@ -37,11 +40,15 @@ combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath){
         subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName[2]))
         subDat <- subDat %>% mutate(precipBulk=secPrecipBulk,precipExpUncert=secPrecipExpUncert,precipQF=secPrecipSciRvwQF)
       }
-      allData <- rbind(allData,subDat[,c('siteID','startDateTime','precipBulk','precipExpUncert','precipQF')])
+      allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])
     }
   }
   outFileName <- paste0(dataName,"ALLdata.csv")
[…]

### 2023-01-12 manuscriptCode_phenologyAndMycorrhizae.Rmd
Prepare .Rmd to download new data.

@@
 #Single Air Temperature At Various Heights 
-```{r}
+```{r,eval=FALSE}
 dataName="NEON_SingleAirTemperature"
@@
 #Triple Air Temperature at Top of Canopy
-```{r} 
+```{r,eval=FALSE} 
 ##Need to redownload!! 
@@
 #Precipitation
-```{r}
+```{r,eval=FALSE}
 dataName="NEON_PrecipitationData"
@@
 #NEON Phenology Observations 
-```{r}
+```{r,eval=FALSE}
 source('combineNEONdata_PhenoObs.R')
@@
 #Download NEON Soil Microbe Data
-```{r}
+```{r,eval=FALSE}
 dataName="NEON_SoilMicrobeComposition"
@@
 #Download NEON Soil Physical and Chemical Properties
-```{r}
+```{r,eval=FALSE}
 dataName <- "NEON_soilProperties"
@@
 #NEON PhenoCam Observations
-```{r}
+```{r,eval=FALSE}
 source('determinePhenoCamURLs.R')

### 2023-01-12 sharedVariables.R

@@ -2,13 +2,12 @@
 library(tidyverse)
 library(scales)
 library("raster")
-library("rhdf5")
-library("neonUtilities")
-library("devtools")
-library("geoNEON")
-library('suncalc')
-library(daymetr)
-
+library("devtools") #
+library("rhdf5") #
+library("neonUtilities") #
+library('suncalc') ##
+library(daymetr) #
+library("geoNEON") #
 
 #library(inborutils)
 options(stringsAsFactors=FALSE)

### 2023-01-12 manuscriptCode_currentScript.R
added basic r script for supercloud test

@@ -1,0 +1,18 @@
+print("entered script")
+
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
+print("loaded packages")
+dataName="NEON_PAR"
+NEON_ID='DP1.00024.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+print("Created directories")
+# selectColumns <- c('precipBulk','precipExpUncert','precipQF')
+# inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
+# varName <- "precipBulk"
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+print("finished downloading data")

### 2023-01-12 sharedVariables.R
Generalized data path hopefully

@@ -18,7 +18,7 @@ NEON_siteNames <- c("ABBY","BARR","BART","BLAN","BONA","CLBJ","CPER","DCFS","DEJ
 length_NEON_siteNames <- length(NEON_siteNames)
 fungalRootDat <- read.csv('Data/fungalRootAssociations.csv',header=TRUE)
 mycorrhizeTypes <- unique(fungalRootDat$Mycorrhizal.type)
-dataPath <- "/Users/Kathryn/Documents/Postdoc_Research/phenologyAndMycorrhizae/Data/"
+dataPath <- "Data/"
 
 siteData <- read_csv(paste0(dataPath,'NEON_Field_Site_Metadata_20220412.csv'))
 siteData <- siteData %>% filter(field_site_type%in%c("Gradient Terrestrial","Core Terrestrial"))

### 2023-01-13 NEON_Data_DownloadAndProcess.R
removing stacking from the current code to run

@@ -1,4 +1,4 @@
-downloadNEONdata <- function(dataName,NEON_ID){
+downloadNEONdata <- function(dataName,NEON_ID,andStack=TRUE){
   #Create Site-Specific Folders for Downloading 
   for(s in seq_along(NEON_siteNames)){
     print(NEON_siteNames[s])
@@ -11,8 +11,9 @@ downloadNEONdata <- function(dataName,NEON_ID){
     savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
     zipsByProduct(dpID=NEON_ID,site=NEON_siteNames[s],
                   savepath=savePath,check.size = F)
-    
-    stackByTable(paste0(savePath,'/filesToStack',IDnum))
+    if(andStack){
+      stackByTable(paste0(savePath,'/filesToStack',IDnum))
+    }
   }
 }
 

### 2023-01-13 manuscriptCode_currentScript.R

@@ -14,5 +14,5 @@ print("Created directories")
 # inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
 # varName <- "precipBulk"
 
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE)
 print("finished downloading data")

### 2023-01-13 NEON_Data_DownloadAndProcess.R
debugging

@@ -6,7 +6,7 @@ downloadNEONdata <- function(dataName,NEON_ID,andStack=TRUE){
   }
   #Download and Stack the Data
   IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
-  for(s in seq_along(NEON_siteNames)){
+  for(s in seq_along(NEON_siteNames)[3:47]){
     print(s)
     savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
     zipsByProduct(dpID=NEON_ID,site=NEON_siteNames[s],

### 2023-01-13 NEON_Data_DownloadAndProcess.R
trying

@@ -6,7 +6,7 @@ downloadNEONdata <- function(dataName,NEON_ID,andStack=TRUE){
   }
   #Download and Stack the Data
   IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
-  for(s in seq_along(NEON_siteNames)[3:47]){
+  for(s in seq_along(NEON_siteNames)[4:47]){
     print(s)
     savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
     zipsByProduct(dpID=NEON_ID,site=NEON_siteNames[s],

### 2023-01-20 manuscriptCode_currentScript.R
trying

@@ -1,23 +1,24 @@
-args = commandArgs(trailingOnly=TRUE)
-print(args)
-my_task_id=as.numeric(args[1])
-num_tasks=as.numeric(args[2])
-fnames <- 10:47
-my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+# args = commandArgs(trailingOnly=TRUE)
+# print(args)
+# my_task_id=as.numeric(args[1])
+# num_tasks=as.numeric(args[2])
+# fnames <- 10:47
+# my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+# 
+# for(s in my_fnames){
 
-for(s in my_fnames){
-  
-  source('sharedVariables.R')
-  source('NEON_Data_DownloadAndProcess.R')
-  
-  # print("loaded packages")
-  # dataName="NEON_SoilTemp"
-  # NEON_ID='DP1.00041.001'
-  
-  dataName="NEON_PAR"
-  NEON_ID='DP1.00024.001'
-  
-  IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
+# print("loaded packages")
+# dataName="NEON_SoilTemp"
+# NEON_ID='DP1.00041.001'
+
+dataName="NEON_PAR"
+NEON_ID='DP1.00024.001'
+
+IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
+for(s in seq_along(NEON_siteNames)){
   
   print(s)
   savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])

### 2023-01-20 manuscriptCode_currentScript.R
updated

@@ -16,17 +16,21 @@ source('NEON_Data_DownloadAndProcess.R')
 
 dataName="NEON_PAR"
 NEON_ID='DP1.00024.001'
+selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
+inFileName <- "PARPAR_30min.csv"
 
 IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
 for(s in seq_along(NEON_siteNames)){
   
   print(s)
   savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
-  fls <- dir(path=paste0(savePath,'/filesToStack',IDnum),pattern="NEON")
-  if(file.exists(paste0(savePath,'/filesToStack',IDnum))
-     &(length(fls)>0)){
-    stackByTable(paste0(savePath,'/filesToStack',IDnum))
-  }
+  combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                  inFileName=inFileName,dataPath=dataPath)
+  # fls <- dir(path=paste0(savePath,'/filesToStack',IDnum),pattern="NEON")
+  # if(file.exists(paste0(savePath,'/filesToStack',IDnum))
+  #    &(length(fls)>0)){
+  #   stackByTable(paste0(savePath,'/filesToStack',IDnum))
+  # }
   
   # if(!file.exists(paste0(dataPath,"/",dataName))){
   #   dir.create(paste0(dataPath,"/",dataName))

### 2023-01-20 manuscriptCode_currentScript.R
update

@@ -10,93 +10,16 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-# print("loaded packages")
-# dataName="NEON_SoilTemp"
-# NEON_ID='DP1.00041.001'
-
-dataName="NEON_PAR"
-NEON_ID='DP1.00024.001'
-selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
-inFileName <- "PARPAR_30min.csv"
-
-IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
-for(s in seq_along(NEON_siteNames)){
-  
-  print(s)
-  savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
-  combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                  inFileName=inFileName,dataPath=dataPath)
-  # fls <- dir(path=paste0(savePath,'/filesToStack',IDnum),pattern="NEON")
-  # if(file.exists(paste0(savePath,'/filesToStack',IDnum))
-  #    &(length(fls)>0)){
-  #   stackByTable(paste0(savePath,'/filesToStack',IDnum))
-  # }
-  
-  # if(!file.exists(paste0(dataPath,"/",dataName))){
-  #   dir.create(paste0(dataPath,"/",dataName))
-  # }
-  
-  # downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE,
-  #                  includedSeq=seq(46,47))
-  # dataName="NEON_Roots"
-  # NEON_ID='DP1.10067.001'
-  
-  # IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
-  # for(s in seq_along(NEON_siteNames)[1:47]){
-  #   print(s)
-  #   savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
-  #   if(file.exists(paste0(savePath,'/filesToStack',IDnum))){
-  #     stackByTable(paste0(savePath,'/filesToStack',IDnum))
-  #   }
-  # }
-  # 
-  # dataName="NEON_relativeHumidity"
-  # NEON_ID='DP1.00098.001'
-  # 
-  # IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
-  # for(s in seq_along(NEON_siteNames)[1:47]){
[…]

### 2023-01-20 manuscriptCode_currentScript.R
update

@@ -16,7 +16,7 @@ if(!file.exists(paste0(dataPath,"/",dataName))){
   dir.create(paste0(dataPath,"/",dataName))
 }
 
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30 
+#downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30 
 
 selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
 inFileName <- "ST_30_minute.csv"

### 2023-01-20 NEON_Data_DownloadAndProcess.R
update

@@ -23,11 +23,13 @@ combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath,s
   if(length(inFileName)==1){
     for(s in seq_along(NEON_siteNames)){
       print(NEON_siteNames[s])
-      subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))
-      if(dataName=="NEON_soilProperties"){
-        allData <- rbind(allData,subDat[,c('siteID','collectDate',selectColumns)])
-      }else{
-        allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])
+      if(file.exists(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))){
+        subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))
+        if(dataName=="NEON_soilProperties"){
+          allData <- rbind(allData,subDat[,c('siteID','collectDate',selectColumns)])
+        }else{
+          allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])
+        }
       }
     }
   }else if(length(inFileName)==2){

### 2023-01-20 NEON_Data_DownloadAndProcess.R
update

@@ -25,7 +25,7 @@ combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath,s
       print(NEON_siteNames[s])
       if(file.exists(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))){
         subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))
-        if(dataName=="NEON_soilProperties"){
+        if(dataName%in%c("NEON_soilProperties","NEON_Roots")){
           allData <- rbind(allData,subDat[,c('siteID','collectDate',selectColumns)])
         }else{
           allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])

### 2023-01-20 manuscriptCode_currentScript.R

@@ -10,16 +10,43 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-dataName="NEON_SoilTemp"
-NEON_ID='DP1.00041.001'
+dataName="NEON_Roots"
+NEON_ID='DP1.10067.001'
+
 if(!file.exists(paste0(dataPath,"/",dataName))){
   dir.create(paste0(dataPath,"/",dataName))
 }
 
-#downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30 
+inFileName <- 'bbc_dilution'
+selectColumns <- c('plotID','sampleVolume',
+                   'dryMass','somDryMass')
 
-selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
-inFileName <- "ST_30_minute.csv"
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
 
-combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath)
+inFileName <- 'bbc_percore'
+selectColumns <- c('plotID','decimalLatitude','decimalLongitude',
+                   'litterDepth','rootSampleDepth')
+
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID'))
+
+inFileName <- 'bbc_rootChemistry'
+selectColumns <- c('plotID','plotType',
+                   'd15N','d13C','nitrogenPercent','carbonPercent',
+                   'CNratio','cnIsotopeQF','cnPercentQF')
+
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID'))
+
+inFileName <- "bbc_rootmass"
[…]

### 2023-01-20 sharedVariables.R

@@ -8,7 +8,6 @@ library("neonUtilities") #
 library('suncalc') ##
 library(daymetr) #
 library("geoNEON") #
-library(doParallel)
 
 #library(inborutils)
 options(stringsAsFactors=FALSE)

### 2023-01-20 manuscriptCode_currentScript.R
update

@@ -17,14 +17,14 @@ if(!file.exists(paste0(dataPath,"/",dataName))){
   dir.create(paste0(dataPath,"/",dataName))
 }
 
-inFileName <- 'bbc_dilution'
+inFileName <- 'bbc_dilution.csv'
 selectColumns <- c('plotID','sampleVolume',
                    'dryMass','somDryMass')
 
 dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                         selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
 
-inFileName <- 'bbc_percore'
+inFileName <- 'bbc_percore.csv'
 selectColumns <- c('plotID','decimalLatitude','decimalLongitude',
                    'litterDepth','rootSampleDepth')
 
@@ -33,7 +33,7 @@ dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
 
 allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID'))
 
-inFileName <- 'bbc_rootChemistry'
+inFileName <- 'bbc_rootChemistry.csv'
 selectColumns <- c('plotID','plotType',
                    'd15N','d13C','nitrogenPercent','carbonPercent',
                    'CNratio','cnIsotopeQF','cnPercentQF')
@@ -43,10 +43,12 @@ dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
 
 allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID'))
 
-inFileName <- "bbc_rootmass"
+inFileName <- "bbc_rootmass.csv"
 selectColumns <- c('plotID','dryMass','mycorrhizaeVisible')
 
 dat4 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                         selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
 
 allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','plotID'))
+
+

### 2023-01-20 manuscriptCode_currentScript.R
update

@@ -13,10 +13,6 @@ source('NEON_Data_DownloadAndProcess.R')
 dataName="NEON_Roots"
 NEON_ID='DP1.10067.001'
 
-if(!file.exists(paste0(dataPath,"/",dataName))){
-  dir.create(paste0(dataPath,"/",dataName))
-}
-
 inFileName <- 'bbc_dilution.csv'
 selectColumns <- c('plotID','sampleVolume',
                    'dryMass','somDryMass')
@@ -50,5 +46,5 @@ dat4 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                         selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
 
 allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','plotID'))
-
-
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)

### 2023-01-21 manuscriptCode_phenologyAndMycorrhizae.Rmd
Generalized data path hopefully
Added new NEON data download and processing

@@
 Download NEON Data
+
+#NEON Phenology Observations 
+```{r,eval=FALSE}
+source('combineNEONdata_PhenoObs.R')
+dataName="NEON_PhenologyObservations"
+NEON_ID='DP1.10055.001'
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
+combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
+combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
+```
 
@@
 
-#NEON Phenology Observations 
-```{r,eval=FALSE}
-source('combineNEONdata_PhenoObs.R')
-dataName="NEON_PhenologyObservations"
-NEON_ID='DP1.10055.001'
+#Download Photosynthetically active radiation (PAR)
+```{r}
+dataName="NEON_PAR"
+NEON_ID='DP1.00024.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
+inFileName <- "PARPAR_30min.csv"
+# varName <- "precipBulk"
 
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
-combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
-combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
-combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)
+
 ```
@@
 
-#Download NEON Soil Physical and Chemical Properties
+#Download NEON Soil Physical and Chemical Properties (Need to finish combining)
 ```{r,eval=FALSE}
 dataName <- "NEON_soilProperties"
+NEON_ID <- "DP1.10086.001"
 if(!file.exists(paste0(dataPath,"/",dataName))){
@@
 }
-NEON_ID <- "DP1.10086.001"
+
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
@@
 outFileName <- paste0(dataName,"ALLdata.csv")
-write.csv(file=paste0(dataPath,outFileName),allData,row.names = FALSE,quote=FALSE)
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
 
@@
 
-#Download Photosynthetically active radiation (PAR)
+#Download Soil Temp
 ```{r}
-dataName="NEON_PAR"
-NEON_ID='DP1.00024.001'
+dataName="NEON_SoilTemp"
+NEON_ID='DP1.00041.001'
 if(!file.exists(paste0(dataPath,"/",dataName))){
@@
 }
-# selectColumns <- c('precipBulk','precipExpUncert','precipQF')
-# inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
-# varName <- "precipBulk"
 
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30
+
+selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
+inFileName <- "ST_30_minute.csv"
+
 combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                 inFileName=inFileName,dataPath=dataPath)
+
+```
+
+#NEON Root Characteristics
+```{r, eval=FALSE}
+dataName="NEON_Roots"
+NEON_ID='DP1.10067.001'
+
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30
+
+inFileName <- 'bbc_dilution.csv'
+selectColumns <- c('plotID','sampleVolume',
+                   'dryMass','somDryMass')
+
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                       selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+dat1 <- dat1 %>% mutate(density=dryMass/sampleVolume,
+                        somDensity=somDryMass/sampleVolume) %>%
+  dplyr::select(-c(sampleVolume,dryMass,somDryMass)) %>%
+  group_by(siteID,collectDate,plotID) %>% summarise(densityMean=mean(density),somDensityMean=mean(somDensity))
+
+inFileName <- 'bbc_percore.csv'
+selectColumns <- c('plotID','decimalLatitude','decimalLongitude',
+                   'litterDepth')
+
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                       selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat2 <- dat2 %>% group_by(siteID,collectDate,plotID) %>%
+  summarise(litterDepth=mean(litterDepth))
+
+allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID'))
+
+inFileName <- 'bbc_rootChemistry.csv'
+selectColumns <- c('plotID','plotType',
+                   'd15N','d13C','nitrogenPercent','carbonPercent',
+                   'CNratio','cnIsotopeQF','cnPercentQF')
+
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                       selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
+  filter(cnIsotopeQF=="OK",cnPercentQF=="OK") %>%
+  group_by(siteID,collectDate,plotID) %>% summarise(d15N=mean(d15N),
+                                                    d13C=mean(d13C),
+                                                    nitrogenPercent=
+                                                      mean(nitrogenPercent),
+                                                    carbonPercent=
+                                                      mean(carbonPercent),
+                                                    CNratio=
+                                                      mean(CNratio))
+
+allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID'))
+
+inFileName <- "bbc_rootmass.csv"
+selectColumns <- c('plotID','dryMass','mycorrhizaeVisible')
+
+dat4 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                       selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+names(dat4)[names(dat4)=="dryMass"] <- "rootDryMass"
+dat4$mycorrhizaeVisible[dat4$mycorrhizaeVisible=="N"] <- 0
+dat4$mycorrhizaeVisible[dat4$mycorrhizaeVisible=="Y"] <- 1
+dat4$mycorrhizaeVisible[dat4$mycorrhizaeVisible==""] <- NA
+
+dat4 <- dat4 %>% group_by(siteID,collectDate,plotID) %>%
+  summarise(rootDryMass=mean(rootDryMass),
+            mycorrhizaeVisiblePercent=mean(as.numeric(mycorrhizaeVisible),na.rm=TRUE))
+
+allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','plotID'))
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
+```
+
+#NEON Plant Structural Characteristics
+```{r}
+
+```
+
+#NEON Litterfall
+```{r}
+
+```
+
+#NEON Foliar Traits
+```{r}
 

### 2023-01-25 sharedVariables.R
Trying to create merge conflict

@@ -1,15 +1,15 @@
 #Shared Variables
 library(tidyverse)
 library(scales)
-library("raster")
 library("devtools") #
-library("rhdf5") #
 library("neonUtilities") #
 library('suncalc') ##
 library(daymetr) #
 library("geoNEON") #
-
+library("rhdf5") 
+library("raster")
 #library(inborutils)
+
 options(stringsAsFactors=FALSE)
 NEON_siteNames <- c("ABBY","BARR","BART","BLAN","BONA","CLBJ","CPER","DCFS","DEJU","DELA","DSNY","GRSM","GUAN","HARV",
                     "HEAL","JERC","JORN","KONA","KONZ","LAJA","LENO","MLBS","MOAB","NIWO","NOGP","OAES","ONAQ",

### 2023-01-25 manuscriptCode_phenologyAndMycorrhizae.Rmd

@@
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
-#inFileNames <- c(,"sls_soilMoisture","sls_soilpH")
+
 inFileName <- "sls_soilCoreCollection.csv"
 selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
-                   'soilTemp','litterDepth','sampleTopDepth','sampleBottomDepth')
+                   'soilTemp','litterDepth')
 dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
@@
 
+dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
+  group_by(siteID,collectDate,plotID,decimalLatitude,decimalLongitude,elevation,horizon) %>% 
+  summarise(soilTemp=mean(soilTemp),litterDepth=mean(litterDepth))
+
 inFileName <- "sls_soilpH.csv"
-selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH','pHSoilInWaterMass','pHWaterVol',
-                   'waterpHRatio','pHSoilInCaClMass','pHCaClVol','caclpHRatio')
+selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH')
 dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                 inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% group_by(siteID,collectDate,plotID,horizon) %>%
+  summarise(soilInWaterpH=mean(soilInWaterpH),soilInWaterpH=mean(soilInWaterpH))
+
 allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))
@@
 inFileName <- "sls_soilMoisture.csv"
-selectColumns <- c('plotID','horizon','boatMass','freshMassBoatMass','dryMassBoatMass','soilMoisture','dryMassFraction')
+selectColumns <- c('plotID','horizon','soilMoisture','dryMassFraction')
 dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                 inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d"))%>% group_by(siteID,collectDate,plotID,horizon) %>%
+  summarise(soilMoisture=mean(soilMoisture),dryMassFraction=mean(dryMassFraction)) 
 allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))
@@
 write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
-
 ```
@@
 ```{r}
+dataName="NEON_litterfall" #No: 2, 7,8, 11, 17, 18, 20, 23, 25, 27, 38, 41, 45
+NEON_ID="DP1.10033.001"
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+
+inFileName <- "ltr_litterCarbonNitrogen.csv"
+
+selectColumns <- c('plotID','plotType','setDate','d15N','d13C',
+                   'nitrogenPercent','carbonPercent','CNratio')
+
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
+  group_by(siteID,collectDate,plotID,plotType,setDate) %>%
+  summarise(d15N=mean(d15N), d13C=mean(d13C),nitrogenPercent=mean(nitrogenPercent),
+            carbonPercent=mean(carbonPercent), CNratio=mean(CNratio))
+
+inFileName <- "ltr_litterLignin.csv"
+selectColumns <- c('plotID','setDate','ligninPercent',
+                   'cellulosePercent')
+
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
+  group_by(siteID,collectDate,plotID,setDate) %>%
+  summarise(ligninPercent=mean(ligninPercent),
+            cellulosePercent=mean(cellulosePercent))
+
+allDat <- full_join(dat1,dat2,by=c('siteID','plotID','setDate'))
+
+inFileName <- "ltr_massdata.csv"
+selectColumns <- c('plotID','setDate','functionalGroup',
+                   'dryMass')
+
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+dat3 <- dat3 %>%
+  group_by(siteID,collectDate,plotID,setDate,functionalGroup) %>%
+  summarise(dryMass=mean(dryMass))
+
+allDat <- full_join(allDat,dat3,by=c('siteID','plotID','setDate'))
+
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
 
@@
 ```{r}
+dataName="NEON_plantFoliarTraits"
+NEON_ID="DP1.10026.001"
+
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30
+
+inFileName <- "cfc_LMA.csv"
+selectColumns <- c('sampleID','plotType','percentGreen','leafMassPerArea','dryMassFraction')
+
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+inFileName <- "cfc_carbonNitrogen.csv"
+selectColumns <- c('plotID','sampleID','plotType','d15N','d13C',
+                   'nitrogenPercent','carbonPercent','CNratio')
+
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+inFileName <- "cfc_chlorophyll.csv"
+# selectColumns <- c('plotID','chlCarotWavelength1'),'chlCarotWavelength2',
+#                    'chlCarotWavelength3','chlCarotWavelength4',
+#                    'chlCarotWavelength1Abs','chlCarotWavelength2Abs',
+#                    'chlCarotWavelength3Abs','chlCarotWavelength4Abs',
+#                    'extractChlAConc','extractChlBConc')
+selectColumns <- c('plotID','extractChlAConc','extractChlBConc','extractCarotConc','sampleID')
+
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+inFileName <- "cfc_elements.csv"
+selectColumns <- c("plotID",'sampleID','foliarPhosphorusConc','foliarPotassiumConc',
+                   'foliarMagnesiumConc','foliarSulfurConc',
+                   'foliarManganeseConc','foliarIronConc',
+                   'foliarCopperConc','foliarBoronConc','foliarZincConc')
+
+dat4 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+inFileName <- "cfc_lignin.csv"
+selectColumns <- c('plotID','sampleID','plotType','ligninPercent','cellulosePercent')
+
+dat5 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','sampleID','plotType'))
+allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','sampleID','plotID'))
+allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','sampleID','plotID'))
+allDat <- full_join(allDat,dat5,by=c('siteID','collectDate','sampleID','plotID','plotType'))
+##
+allDat <- full_join(dat2,dat3,by=c('siteID','plotID','collectDate','sampleID'))
+allDat <- full_join(allDat,dat4,by=c('siteID','plotID','collectDate','sampleID'))
+allDat <- full_join(allDat,dat5,by=c('siteID','plotID','collectDate','sampleID','plotType'))
+allDat <- full_join(allDat,dat1,by=c('siteID','collectDate','sampleID','plotType'))
+
+allDat <- allDat %>% dplyr::select(-sampleID) %>%
+  mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
+  group_by(siteID,collectDate,plotID,plotType) %>%
+  summarise(percentGreen=mean(percentGreen),leafMassPerArea=mean(leafMassPerArea),
+            dryMassFraction=mean(dryMassFraction),
+            d15N=mean(d15N),
+            d13C=mean(d13C),
+            nitrogenPercent=mean(nitrogenPercent),
+            carbonPercent=mean(carbonPercent),
+            CNratio=mean(CNratio),
+            extractChlAConc=mean(extractChlAConc),
+            extractChlBConc=mean(extractChlBConc),
+            extractCarotConc=mean(extractCarotConc),
+            foliarPhosphorusConc=mean(foliarPhosphorusConc),
+            foliarPotassiumConc=mean(foliarPotassiumConc),
+            foliarMagnesiumConc=mean(foliarMagnesiumConc),
+            foliarSulfurConc=mean(foliarSulfurConc),
+            foliarManganeseConc=mean(foliarManganeseConc),
+            foliarIronConc=mean(foliarIronConc),
+            foliarCopperConc=mean(foliarCopperConc),
+            foliarBoronConc=mean(foliarBoronConc),
+            foliarZincConc=mean(foliarZincConc),
+            ligninPercent=mean(ligninPercent),
+            cellulosePercent=cellulosePercent)
+
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
 

### 2023-01-25 sharedVariables.R
creating example

@@ -1,13 +1,13 @@
 #Shared Variables
 library(tidyverse)
+library('suncalc') ##
 library(scales)
+library("geoNEON") #
 library("raster")
 library("devtools") #
 library("rhdf5") #
-library("neonUtilities") #
-library('suncalc') ##
 library(daymetr) #
-library("geoNEON") #
+library("neonUtilities") #
 
 #library(inborutils)
 options(stringsAsFactors=FALSE)

### 2023-01-30 manuscriptCode_phenologyAndMycorrhizae.Rmd
daily summaries for single air temperature

@@
 inFileName <- "SAAT_30min.csv"
+varName <- 'tempSingleMean'
 
@@
                 inFileName=inFileName,dataPath=dataPath)
-
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName="mean")
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=min,funName="min")
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=max,funName="max")
 ```
@@
 ##Need to redownload!! 
-dataName="NEON_TemperatureData"
+dataName="NEON_TopTemperatureData"
 NEON_ID='DP1.00003.001'
@@
 varName <- 'tempTripleMean'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
 
@@
 
-#Download NEON Soil Physical and Chemical Properties (Need to finish combining)
+#Download NEON Soil Physical and Chemical Properties
 ```{r,eval=FALSE}

### 2023-01-30 NEON_Data_DownloadAndProcess.R

@@ -54,11 +54,17 @@ combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath,s
   }
 }
 
-calculateDailyWeather <- function(dataName,dataPath,varName,funType){
+calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
   inFileName <- paste0(dataName,"ALLdata.csv")
-  outFileName <- paste0(dataName,"Dailydata.csv")
+  outFileName <- paste0(dataName,"Dailydata_",as.character(funName),".csv")
+  print(outFileName)
   allData <- read.csv(file=paste0(dataPath,inFileName))
-  allDaily <- matrix(nrow=0,ncol=3)
+  if(dataName=="NEON_SingleAirTemperature"){
+    allDaily <- matrix(nrow=0,ncol=5)
+  }else{
+    allDaily <- matrix(nrow=0,ncol=4)
+  }
+  
   if("precipQF" %in% colnames(allData)){
     names(allData)[names(allData)=="precipQF"] <- 'finalQF'
   }
@@ -66,12 +72,22 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType){
     siteName <- NEON_siteNames[s]
     print(siteName)
     allData$oldValue <- allData[,varName]
+    if(dataName=="NEON_SingleAirTemperature"){
+      subDat <- allData %>% filter(siteID==siteName) %>% 
+        filter(finalQF==0 | is.na(finalQF)) %>%
+        mutate(date = lubridate::floor_date(as.POSIXct(startDateTime))) %>%
+        group_by(date,verticalPosition) %>% mutate(value=funType(oldValue,na.rm=TRUE),n=sum(!is.na(oldValue)))
+      subDat <- data.frame(subDat)
+      subDat <-subDat[,which(names(subDat) %in% c('siteID','date','value','verticalPosition','n'))] %>% distinct()
+    }else{
     subDat <- allData %>% filter(siteID==siteName) %>% 
       filter(finalQF==0 | is.na(finalQF)) %>%
       mutate(date = lubridate::floor_date(as.POSIXct(startDateTime))) %>%
-      group_by(date) %>% mutate(value=funType(oldValue,na.rm=TRUE))
+      group_by(date) %>% mutate(value=funType(oldValue,na.rm=TRUE),n=n())
     subDat <- data.frame(subDat)
[…]

### 2023-01-30 manuscriptCode_currentScript.R

@@ -6,82 +6,19 @@
 # my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
 # 
 # for(s in my_fnames){
-
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
+dataName="NEON_TemperatureData"
+NEON_ID='DP1.00003.001'
+selectColumns <- c('tempTripleMean','finalQF')
+inFileName <- "TAAT_30min.csv"
+varName <- 'tempTripleMean'
 
-library('broom')
-
-tempDat <- read.csv('Data/NEON_SingleAirTemperatureALLdata.csv')
-tempDat <- tempDat %>% filter(finalQF==0) %>% filter(!is.na(tempSingleMean))
-fittedModelDat <- tempDat %>% group_by(siteID,startDateTime) %>% mutate(n=n()) %>% filter(n>1)
-
-fittedModels <- fittedModelDat %>% group_by(siteID,startDateTime) %>% 
-  do(model = lm(tempSingleMean ~ verticalPosition,data=.))
-
-fittedModelsTidied <- fittedModels %>% summarise(tidy(model))
-fittedModelsFit <- fittedModels %>% summarise(glance(model))
-fittedModels <- cbind(fittedModels,fittedModelsFit$r.squared)
-
-newDat <- matrix(nrow=nrow(fittedModelsTidied),ncol=3)
-
-ct <- 1
-for(i in 1:nrow(fittedModels)){
-  if(i%%1000==0){
-    print(i)
-  }
-  newDat[ct,1] <- as.character(fittedModels[i,1])
-  newDat[ct,2] <- as.character(fittedModels[i,2])
-  newDat[ct,3] <- as.character(fittedModels[i,4])
-  ct <- ct + 1
-  newDat[ct,1] <- as.character(fittedModels[i,1])
-  newDat[ct,2] <- as.character(fittedModels[i,2])
-  newDat[ct,3] <- as.character(fittedModels[i,4])
-  ct <- ct + 1
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
 }
-colnames(newDat) <- c('siteID','startDateTime','r.squared')
-fittedModelSummary <- cbind(newDat,fittedModelsTidied)
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+#}
 
-save(fittedModelSummary,file="fittedAirTempModels.RData")
[…]

### 2023-01-30 sharedVariables.R

@@ -8,6 +8,7 @@ library("devtools") #
 library("rhdf5") #
 library(daymetr) #
 library("neonUtilities") #
+library('broom')
 
 #library(inborutils)
 

### 2023-01-30 manuscriptCode_phenologyAndMycorrhizae.Rmd
Added code to process and gap-fill NEON air temperature at various heights of the tower

@@
                 inFileName=inFileName,dataPath=dataPath)
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName="mean")
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=min,funName="min")
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=max,funName="max")
+for(funName in c("mean","max","min")){
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName=funName)
+  #Calculate LRs
+  gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
+}
+
 ```
 
-#Triple Air Temperature at Top of Canopy
-```{r,eval=FALSE} 
-##Need to redownload!! 
-dataName="NEON_TopTemperatureData"
-NEON_ID='DP1.00003.001'
-selectColumns <- c('tempTripleMean','finalQF')
-inFileName <- "TAAT_30min.csv"
-varName <- 'tempTripleMean'
-if(!file.exists(paste0(dataPath,"/",dataName))){
-  dir.create(paste0(dataPath,"/",dataName))
-}
+<!-- #Triple Air Temperature at Top of Canopy -->
+<!-- ```{r,eval=FALSE}  -->
+<!-- ##Need to redownload!!  -->
+<!-- dataName="NEON_TopTemperatureData" -->
+<!-- NEON_ID='DP1.00003.001' -->
+<!-- selectColumns <- c('tempTripleMean','finalQF') -->
+<!-- inFileName <- "TAAT_30min.csv" -->
+<!-- varName <- 'tempTripleMean' -->
+<!-- if(!file.exists(paste0(dataPath,"/",dataName))){ -->
+<!--   dir.create(paste0(dataPath,"/",dataName)) -->
+<!-- } -->
 
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
-combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath)
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean)
-gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)
+<!-- downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) -->
+<!-- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns, -->
+<!--                 inFileName=inFileName,dataPath=dataPath) -->
+<!-- calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean) -->
+<!-- gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName) -->
 
-```
+<!-- ``` -->
 

### 2023-01-30 NEON_Data_DownloadAndProcess.R

@@ -151,3 +151,71 @@ gapFillFromDaymet <- function(dataName,dataPath,varName){
   # dev.off()
   write.csv(file=paste0(dataPath,dataName,'Dailydata_gapFilled.csv'),allOutput,row.names = FALSE,quote=FALSE)
 }
+
+gapFillFromDayMet_verticalProfiles <- function(dataName,dataPath,varName,funName){
+  allData <- read.csv(paste0(dataPath,dataName,"Dailydata_",as.character(funName),".csv"))
+  dayMetLRs <- read.csv(paste0(dataName,"towerHeight_LRfitsWithDayMet_",summaryStat,".csv"))
+  dayMetLRs <- dayMetLRs %>% dplyr::select(siteID,week,verticalPosition,term,estimate)
+  dayMetLRs <- pivot_wider(dayMetLRs,names_from = term,values_from = estimate)
+  colnames(dayMetLRs) <- c("siteID","week","verticalPosition","intercept","slope")
+  
+  allOutput <- matrix(nrow=0,ncol=4)
+
+  for(s in seq_along(NEON_siteNames)){
+    siteName <- NEON_siteNames[s]
+    print(siteName)
+    lat <- siteData$field_latitude[siteData$field_site_id==siteName]
+    lon <- siteData$field_longitude[siteData$field_site_id==siteName]
+    
+    siteDat <- allData %>% filter(siteID==siteName)
+    siteDat$date <- as.Date(siteDat$date)
+    siteHeights <- unique(siteDat$verticalPosition)
+    dayMet <- download_daymet(site=siteName,
+                              lat=lat,
+                              lon=lon,
+                              start=2014,
+                              end=2021,
+                              internal=TRUE,
+                              simplify=TRUE)
+    dayMet$date <- as.Date((dayMet$yday-1),origin=as.Date(paste0(dayMet$year,"-01-01")))
+    if(varName=='tempSingleMean'){
+      dayMetMax <- dayMet %>% filter(measurement=="tmax..deg.c.")
+      dayMetMax <- dayMetMax %>% dplyr::select(value,date)
+      
+      dayMetMin <- dayMet %>% filter(measurement=="tmin..deg.c.")
+      dayMetMin <- dayMetMin %>% dplyr::select(value,date)
[…]

### 2023-01-30 createVerticalProfileLRs.R

@@ -1,0 +1,212 @@
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
+dataName="NEON_SingleAirTemperature"
+
+for(summaryStat in c("mean","min","max")){
+  allData <- read.csv(paste0(dataPath,dataName,'Dailydata_',summaryStat,'.csv'))
+  
+  allData$week <- floor((lubridate::yday(allData$date)-0.01)/7)+1
+  
+  allFittedModelSummaries <- matrix(nrow=0,ncol=9)
+  
+  for(s in (seq_along(NEON_siteNames))){
+    siteName <- NEON_siteNames[s]
+    print(siteName)
+    lat <- siteData$field_latitude[siteData$field_site_id==siteName]
+    lon <- siteData$field_longitude[siteData$field_site_id==siteName]
+    
+    siteDat <- allData %>% filter(siteID==siteName)
+    
+    dayMet <- download_daymet(site=siteName,
+                              lat=lat,
+                              lon=lon,
+                              start=2014,
+                              end=2021,
+                              internal=TRUE,
+                              simplify=TRUE)
+    
+    
+    dayMet$date <- as.Date((dayMet$yday-1),origin=as.Date(paste0(dayMet$year,"-01-01")))
+    dayMetMax <- dayMet %>% filter(measurement=="tmax..deg.c.")
+    dayMetMax <- dayMetMax %>% dplyr::select(value,date)
+    
+    dayMetMin <- dayMet %>% filter(measurement=="tmin..deg.c.")
+    dayMetMin <- dayMetMin %>% dplyr::select(value,date)
+    dayMet <- merge(dayMetMax,dayMetMin,by="date")
+    if(summaryStat=="mean"){
+      dayMet$dayMetValue <- rowMeans(dayMet[,2:3])
+    }else if(summaryStat=="min"){
+      dayMet$dayMetValue <- dayMet[,3]
+    }else if(summaryStat=="max"){
+      dayMet$dayMetValue <- dayMet[,2]
+    }
+    dayMet <- dayMet %>% dplyr::select(date,dayMetValue)
+    
+    siteHeights <- unique(siteDat$verticalPosition)
+    siteDat$date <- as.Date(siteDat$date)
+    siteDat <- left_join(siteDat,dayMet,by="date")
+    
[…]

### 2023-01-31 NEON_Data_DownloadAndProcess.R
Updated function to apply to NEON_PAR

@@ -59,7 +59,7 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
   outFileName <- paste0(dataName,"Dailydata_",as.character(funName),".csv")
   print(outFileName)
   allData <- read.csv(file=paste0(dataPath,inFileName))
-  if(dataName=="NEON_SingleAirTemperature"){
+  if(dataName=="NEON_SingleAirTemperature" | dataName=="NEON_PAR"){
     allDaily <- matrix(nrow=0,ncol=5)
   }else{
     allDaily <- matrix(nrow=0,ncol=4)
@@ -67,12 +67,14 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
   
   if("precipQF" %in% colnames(allData)){
     names(allData)[names(allData)=="precipQF"] <- 'finalQF'
+  }else if(dataName=="NEON_PAR"){
+    names(allData)[names(allData)=="PARFinalQF"] <- 'finalQF'
   }
   for(s in seq_along(NEON_siteNames)){
     siteName <- NEON_siteNames[s]
     print(siteName)
     allData$oldValue <- allData[,varName]
-    if(dataName=="NEON_SingleAirTemperature"){
+    if(dataName=="NEON_SingleAirTemperature" | dataName=="NEON_PAR"){
       subDat <- allData %>% filter(siteID==siteName) %>% 
         filter(finalQF==0 | is.na(finalQF)) %>%
         mutate(date = lubridate::floor_date(as.POSIXct(startDateTime))) %>%

### 2023-01-31 NEON_Data_DownloadAndProcess.R
updated for soil temp

@@ -59,7 +59,7 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
   outFileName <- paste0(dataName,"Dailydata_",as.character(funName),".csv")
   print(outFileName)
   allData <- read.csv(file=paste0(dataPath,inFileName))
-  if(dataName=="NEON_SingleAirTemperature" | dataName=="NEON_PAR"){
+  if(dataName%in%c("NEON_SingleAirTemperature", "NEON_PAR","NEON_SoilTemp")){
     allDaily <- matrix(nrow=0,ncol=5)
   }else{
     allDaily <- matrix(nrow=0,ncol=4)
@@ -74,7 +74,7 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
     siteName <- NEON_siteNames[s]
     print(siteName)
     allData$oldValue <- allData[,varName]
-    if(dataName=="NEON_SingleAirTemperature" | dataName=="NEON_PAR"){
+    if(dataName%in%c("NEON_SingleAirTemperature", "NEON_PAR","NEON_SoilTemp")){
       subDat <- allData %>% filter(siteID==siteName) %>% 
         filter(finalQF==0 | is.na(finalQF)) %>%
         mutate(date = lubridate::floor_date(as.POSIXct(startDateTime))) %>%

### 2023-01-31 manuscriptCode_currentScript.R

@@ -8,17 +8,25 @@
 # for(s in my_fnames){
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
-dataName="NEON_TemperatureData"
-NEON_ID='DP1.00003.001'
-selectColumns <- c('tempTripleMean','finalQF')
-inFileName <- "TAAT_30min.csv"
-varName <- 'tempTripleMean'
+dataName="NEON_SoilTemp"
+NEON_ID='DP1.00041.001'
 
-if(!file.exists(paste0(dataPath,"/",dataName))){
-  dir.create(paste0(dataPath,"/",dataName))
-}
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
-#}
+selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
+inFileName <- "ST_30_minute.csv"
 
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
+
+funType=mean
+funName="mean"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=min
+funName="min"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=max
+funName="max"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 
 

### 2023-01-31 manuscriptCode_currentScript.R
typo

@@ -13,6 +13,7 @@ NEON_ID='DP1.00041.001'
 
 selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
 inFileName <- "ST_30_minute.csv"
+varName <- 'soilTempMean'
 
 combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                 inFileName=inFileName,dataPath=dataPath)

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
Added relative humidity download

@@
 inFileName <- "PARPAR_30min.csv"
-# varName <- "precipBulk"
+varName <- "PARMean"
 
@@
                 inFileName=inFileName,dataPath=dataPath)
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)
+funType=mean
+funName="mean"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=min
+funName="min"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=max
+funName="max"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+```
+
+#Download Relative Humidity
+```{r}
+dataName="NEON_RH"
+NEON_ID='DP1.00098.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
+# inFileName <- "PARPAR_30min.csv"
+# varName <- "PARMean"
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+# combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+#                 inFileName=inFileName,dataPath=dataPath)
+# funType=mean
+# funName="mean"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+# 
+# funType=min
+# funName="min"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+# 
+# funType=max
+# funName="max"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 
@@
 inFileName <- "ST_30_minute.csv"
+varName <- 'soilTempMean'
 
@@
                 inFileName=inFileName,dataPath=dataPath)
+
+funType=mean
+funName="mean"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=min
+funName="min"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=max
+funName="max"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 

### 2023-02-01 manuscriptCode_currentScript.R

@@ -8,26 +8,14 @@
 # for(s in my_fnames){
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
-dataName="NEON_SoilTemp"
-NEON_ID='DP1.00041.001'
 
-selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
-inFileName <- "ST_30_minute.csv"
-varName <- 'soilTempMean'
+dataName="NEON_RH"
+NEON_ID='DP1.00098.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
+# inFileName <- "PARPAR_30min.csv"
+# varName <- "PARMean"
 
-combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath)
-
-funType=mean
-funName="mean"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=min
-funName="min"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=max
-funName="max"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack = FALSE)

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
Add windspeed

@@
 NEON_ID='DP1.00098.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
+# inFileName <- "PARPAR_30min.csv"
+# varName <- "PARMean"
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+# combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+#                 inFileName=inFileName,dataPath=dataPath)
+# funType=mean
+# funName="mean"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+# 
+# funType=min
+# funName="min"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+# 
+# funType=max
+# funName="max"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+```
+
+#Download Windspeed
+```{r}
+dataName="NEON_Windspeed"
+NEON_ID='DP1.00001.001'
 if(!file.exists(paste0(dataPath,"/",dataName))){

### 2023-02-01 manuscriptCode_currentScript.R

@@ -9,8 +9,11 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-dataName="NEON_RH"
-NEON_ID='DP1.00098.001'
+# dataName="NEON_RH"
+# NEON_ID='DP1.00098.001'
+dataName="NEON_Windspeed"
+NEON_ID='DP1.00001.001'
+
 if(!file.exists(paste0(dataPath,"/",dataName))){
   dir.create(paste0(dataPath,"/",dataName))
 }

### 2023-02-01 manuscriptCode_currentScript.R
updated

@@ -21,4 +21,11 @@ if(!file.exists(paste0(dataPath,"/",dataName))){
 # inFileName <- "PARPAR_30min.csv"
 # varName <- "PARMean"
 
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack = FALSE)
+#downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack = FALSE)
+
+IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
+for(s in seq_along(NEON_siteNames)){
+  print(s)
+  savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
+  stackByTable(paste0(savePath,'/filesToStack',IDnum))
+}

### 2023-02-01 manuscriptCode_currentScript.R
updated

@@ -9,23 +9,29 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-# dataName="NEON_RH"
-# NEON_ID='DP1.00098.001'
+dataName="NEON_RH"
+NEON_ID='DP1.00098.001'
 dataName="NEON_Windspeed"
 NEON_ID='DP1.00001.001'
 
-if(!file.exists(paste0(dataPath,"/",dataName))){
-  dir.create(paste0(dataPath,"/",dataName))
-}
-# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
-# inFileName <- "PARPAR_30min.csv"
-# varName <- "PARMean"
+selectColumns <- c('verticalPosition','RHMean','RHMinimum','RHMaximum','RHVariance','dewTempMean',
+                   'RHFinalQF','dewTempFinalQF')
+inFileName <- "RH_30min.csv"
+varName <- "RHMean"
+
+# 
+# if(!file.exists(paste0(dataPath,"/",dataName))){
+#   dir.create(paste0(dataPath,"/",dataName))
+# }
+
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
 
 #downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack = FALSE)
 
-IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
-for(s in seq_along(NEON_siteNames)){
-  print(s)
-  savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
-  stackByTable(paste0(savePath,'/filesToStack',IDnum))
-}
+# IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
+# for(s in seq_along(NEON_siteNames)){
+#   print(s)
+#   savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
+#   stackByTable(paste0(savePath,'/filesToStack',IDnum))
+# }

### 2023-02-01 manuscriptCode_currentScript.R
merging

@@ -11,8 +11,8 @@ source('NEON_Data_DownloadAndProcess.R')
 
 dataName="NEON_RH"
 NEON_ID='DP1.00098.001'
-dataName="NEON_Windspeed"
-NEON_ID='DP1.00001.001'
+#dataName="NEON_Windspeed"
+#NEON_ID='DP1.00001.001'
 
 selectColumns <- c('verticalPosition','RHMean','RHMinimum','RHMaximum','RHVariance','dewTempMean',
                    'RHFinalQF','dewTempFinalQF')

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
updated

--- 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
@@
 ```{r}
-dataName="NEON_RH"
+dataName="NEON_relativeHumidity"
 NEON_ID='DP1.00098.001'
@@
 }
-# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
-# inFileName <- "PARPAR_30min.csv"
-# varName <- "PARMean"
+selectColumns <- c('verticalPosition','RHMean','RHMinimum','RHMaximum','RHVariance','dewTempMean',
+                   'RHFinalQF','dewTempFinalQF')
+inFileName <- "RH_30min.csv"
+varName <- "RHMean"
+
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
+
+# funType=mean
+# funName="mean"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+# 
+# funType=min
+# funName="min"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+# 
+# funType=max
+# funName="max"
+# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+```
+
+#Download Windspeed
+```{r}
+dataName="NEON_Windspeed"
+NEON_ID='DP1.00001.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+selectColumns <- c('verticalPosition','windSpeedMean','windSpeedMinimum','windSpeedMaximum','windSpeedFinalQF')
+inFileName <- "2DWSD_30min.csv"
+varName <- "windSpeedMean"
 

### 2023-02-01 manuscriptCode_currentScript.R

@@ -9,10 +9,10 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-dataName="NEON_RH"
+dataName="NEON_relativeHumidity"
 NEON_ID='DP1.00098.001'
-dataName="NEON_Windspeed"
-NEON_ID='DP1.00001.001'
+# dataName="NEON_Windspeed"
+# NEON_ID='DP1.00001.001'
 
 selectColumns <- c('verticalPosition','RHMean','RHMinimum','RHMaximum','RHVariance','dewTempMean',
                    'RHFinalQF','dewTempFinalQF')

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd

@@
 
-# funType=mean
-# funName="mean"
-# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-# 
-# funType=min
-# funName="min"
-# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-# 
-# funType=max
-# funName="max"
-# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+funType=mean
+funName="mean"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=min
+funName="min"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=max
+funName="max"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 
@@
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
-# combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-#                 inFileName=inFileName,dataPath=dataPath)
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
 # funType=mean

### 2023-02-01 NEON_Data_DownloadAndProcess.R
inconsistency

@@ -69,6 +69,10 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
     names(allData)[names(allData)=="precipQF"] <- 'finalQF'
   }else if(dataName=="NEON_PAR"){
     names(allData)[names(allData)=="PARFinalQF"] <- 'finalQF'
+  }else if(dataName=="NEON_relativeHumidity"){
+    names(allData)[names(allData)=="RHFinalQF"] <- 'finalQF'
+  }else if(dataName=="NEON_Windspeed"){
+    names(allData)[names(allData)=="windSpeedFinalQF"] <- 'finalQF'
   }
   for(s in seq_along(NEON_siteNames)){
     siteName <- NEON_siteNames[s]

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd

@@
                 inFileName=inFileName,dataPath=dataPath)
-# funType=mean
-# funName="mean"
-# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-# 
-# funType=min
-# funName="min"
-# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-# 
-# funType=max
-# funName="max"
-# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+funType=mean
+funName="mean"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=min
+funName="min"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+
+funType=max
+funName="max"
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 

### 2023-02-01 plotNEON_metData.R
Plotting NEON met data

@@ -1,0 +1,25 @@
+#Plot Data
+dataNames <- c("NEON_SingleAirTemperature","NEON_PrecipitationData","NEON_PAR",
+               "NEON_relativeHumidity","NEON_Windspeed","NEON_SoilTemp")
+varNames <- c("tempSingleMean","precipBulk","PARMean","RHMean","windSpeedMean","soilTempMean")
+pdf('NEON_metData.pdf',height=5,width=12)
+for(i in seq_along(dataNames)){
+  dataName <- dataNames[i]
+  varName <- varNames[i]
+  meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean_gapFilled.csv"),header=TRUE)
+  # minDat <- read.csv(paste0(dataPath,dataName,"Dailydata_min_gapFilled.csv"), header=TRUE)
+  # maxDat <- read.csv(paste0(dataPath,dataName,"Dailydata_max_gapFilled.csv"), header=TRUE)
+  for(s in seq_along(NEON_siteNames)){
+    siteName <- NEON_siteNames[s]
+    siteMeanDat <- meanDat %>% filter(siteID==siteName)
+    colnames(siteMeanDat)[4] <- "value"
+    ggplot(siteMeanDat,aes(x=as.Date(date),y=value,col=verticalPosition)) +
+      geom_point()+
+      theme_classic()+
+      ggtitle(siteName)+
+      xlab("Date")+
+      ylab(dataName)
+    
+  }
+}
+dev.off()

### 2023-02-01 plotNEON_metData.R
inconsistency

@@ -6,7 +6,13 @@ pdf('NEON_metData.pdf',height=5,width=12)
 for(i in seq_along(dataNames)){
   dataName <- dataNames[i]
   varName <- varNames[i]
-  meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean_gapFilled.csv"),header=TRUE)
+  if(dataName=="NEON_SingleAirTemperature"){
+    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean_gapFilled.csv"),header=TRUE)
+  }else if(dataName=="NEON_PrecipitationData"){
+    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_gapFilled.csv"),header=TRUE)
+  }else{
+    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean.csv"),header=TRUE)
+  }
   # minDat <- read.csv(paste0(dataPath,dataName,"Dailydata_min_gapFilled.csv"), header=TRUE)
   # maxDat <- read.csv(paste0(dataPath,dataName,"Dailydata_max_gapFilled.csv"), header=TRUE)
   for(s in seq_along(NEON_siteNames)){

### 2023-02-01 plotNEON_metData.R
typo

@@ -1,4 +1,7 @@
 #Plot Data
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
 dataNames <- c("NEON_SingleAirTemperature","NEON_PrecipitationData","NEON_PAR",
                "NEON_relativeHumidity","NEON_Windspeed","NEON_SoilTemp")
 varNames <- c("tempSingleMean","precipBulk","PARMean","RHMean","windSpeedMean","soilTempMean")

### 2023-02-01 NEON_Data_DownloadAndProcess.R
Added file to download ERA5

@@ -160,7 +160,7 @@ gapFillFromDaymet <- function(dataName,dataPath,varName){
 
 gapFillFromDayMet_verticalProfiles <- function(dataName,dataPath,varName,funName){
   allData <- read.csv(paste0(dataPath,dataName,"Dailydata_",as.character(funName),".csv"))
-  dayMetLRs <- read.csv(paste0(dataName,"towerHeight_LRfitsWithDayMet_",summaryStat,".csv"))
+  dayMetLRs <- read.csv(paste0(dataName,"towerHeight_LRfitsWithDayMet_",as.character(funName),".csv"))
   dayMetLRs <- dayMetLRs %>% dplyr::select(siteID,week,verticalPosition,term,estimate)
   dayMetLRs <- pivot_wider(dayMetLRs,names_from = term,values_from = estimate)
   colnames(dayMetLRs) <- c("siteID","week","verticalPosition","intercept","slope")

### 2023-02-01 downloadERA5.R

@@ -1,0 +1,58 @@
+library('devtools')
+library('ncdf4')
+library("reticulate")
+
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
+cdsapi <- reticulate::import_from_path("cdsapi",path="./.conda/envs/myR_new2/lib/python3.11/site-packages")
+cclient <- cdsapi$Client()
+
+start_date <- as.Date("2022-01-01")
+end_date <- as.Date("2022-12-31")
+
+variables <- tibble::tribble(
+  ~cf_name, ~units, ~api_name, ~ncdf_name,
+  "air_temperature", "Kelvin", "2m_temperature", "t2m",
+  "air_pressure", "Pa", "surface_pressure", NA_character_,
+  NA_character_, "Kelvin", "2m_dewpoint_temperature", NA_character_,
+  "precipitation_flux", "kg/m2/s", "total_precipitation", NA_character_,
+  "eastward_wind", "m/s", "10m_u_component_of_wind", NA_character_,
+  "northward_wind", "m/s", "10m_v_component_of_wind", NA_character_,
+  "surface_downwelling_shortwave_flux_in_air", "W/m2", "surface_solar_radiation_downwards", NA_character_,
+  "surface_downwelling_longwave_flux_in_air", "W/m2", "surface_thermal_radiation_downwards", NA_character_
+  
+) #Some examples (see more at: https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-single-levels?tab=overview)
+
+var <- variables[["api_name"]][[1]] #Only include the first variable
+
+for(s in seq_along(NEON_siteNames)){
+  siteID <- NEON_siteNames[s]
+  print(siteName)
+  lat <- siteData$field_latitude[siteData$field_site_id==siteName]
+  lon <- siteData$field_longitude[siteData$field_site_id==siteName]
+  area <- rep(round(c(lat, long) * 4) / 4, 2)
+  
+  
+  fileName <- paste0(dataPath,'ERA5/',siteID,"_",start_date,"_",end_date,"_era5AirTemperatureMembers.nc")
+  print(fileName)
+  do_next <- tryCatch({
+    cclient$retrieve(
+      "reanalysis-era5-single-levels",
+      list(
+        variable = var,
+        product_type = 'ensemble_members',
+        date = paste(start_date, end_date, sep = "/"),
+        time = "00/to/23/by/1",
+        area = area,
[…]

### 2023-02-01 plotNEON_metData.R

@@ -8,6 +8,7 @@ varNames <- c("tempSingleMean","precipBulk","PARMean","RHMean","windSpeedMean","
 pdf('NEON_metData.pdf',height=5,width=12)
 for(i in seq_along(dataNames)){
   dataName <- dataNames[i]
+  print(dataName)
   varName <- varNames[i]
   if(dataName=="NEON_SingleAirTemperature"){
     meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean_gapFilled.csv"),header=TRUE)
@@ -21,13 +22,22 @@ for(i in seq_along(dataNames)){
   for(s in seq_along(NEON_siteNames)){
     siteName <- NEON_siteNames[s]
     siteMeanDat <- meanDat %>% filter(siteID==siteName)
-    colnames(siteMeanDat)[4] <- "value"
-    ggplot(siteMeanDat,aes(x=as.Date(date),y=value,col=verticalPosition)) +
-      geom_point()+
-      theme_classic()+
-      ggtitle(siteName)+
-      xlab("Date")+
-      ylab(dataName)
+    if(dataName=="NEON_PrecipitationData"){
+      print(ggplot(siteMeanDat,aes(x=as.Date(date),y=precipBulk)) +
+        geom_point()+
+        theme_classic()+
+        ggtitle(siteName)+
+        xlab("Date")+
+        ylab(dataName))
+    }else{
+      colnames(siteMeanDat)[4] <- "value"
+      print(ggplot(siteMeanDat,aes(x=as.Date(date),y=value,col=verticalPosition)) +
+        geom_point()+
+        theme_classic()+
+        ggtitle(siteName)+
+        xlab("Date")+
+        ylab(dataName))
+    }
     
   }
 }

### 2023-02-01 downloadERA5.R
typo

@@ -5,11 +5,11 @@ library("reticulate")
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-cdsapi <- reticulate::import_from_path("cdsapi",path="./.conda/envs/myR_new2/lib/python3.11/site-packages")
+cdsapi <- reticulate::import_from_path("cdsapi",path="~/.conda/envs/myR_new2/lib/python3.11/site-packages")
 cclient <- cdsapi$Client()
 
 start_date <- as.Date("2022-01-01")
-end_date <- as.Date("2022-12-31")
+end_date <- as.Date("2022-01-31")
 
 variables <- tibble::tribble(
   ~cf_name, ~units, ~api_name, ~ncdf_name,

### 2023-02-01 downloadERA5.R
typo

@@ -28,7 +28,7 @@ var <- variables[["api_name"]][[1]] #Only include the first variable
 
 for(s in seq_along(NEON_siteNames)){
   siteID <- NEON_siteNames[s]
-  print(siteName)
+  print(siteID)
   lat <- siteData$field_latitude[siteData$field_site_id==siteName]
   lon <- siteData$field_longitude[siteData$field_site_id==siteName]
   area <- rep(round(c(lat, long) * 4) / 4, 2)

### 2023-02-01 downloadERA5.R
typo

@@ -29,8 +29,8 @@ var <- variables[["api_name"]][[1]] #Only include the first variable
 for(s in seq_along(NEON_siteNames)){
   siteID <- NEON_siteNames[s]
   print(siteID)
-  lat <- siteData$field_latitude[siteData$field_site_id==siteName]
-  lon <- siteData$field_longitude[siteData$field_site_id==siteName]
+  lat <- siteData$field_latitude[siteData$field_site_id==siteID]
+  lon <- siteData$field_longitude[siteData$field_site_id==siteID]
   area <- rep(round(c(lat, long) * 4) / 4, 2)
   
   

### 2023-02-01 downloadERA5.R
typo (again)

@@ -30,7 +30,7 @@ for(s in seq_along(NEON_siteNames)){
   siteID <- NEON_siteNames[s]
   print(siteID)
   lat <- siteData$field_latitude[siteData$field_site_id==siteID]
-  lon <- siteData$field_longitude[siteData$field_site_id==siteID]
+  long <- siteData$field_longitude[siteData$field_site_id==siteID]
   area <- rep(round(c(lat, long) * 4) / 4, 2)
   
   

### 2023-02-02 downloadERA5.R
updated ERA5 with more variables

@@ -8,7 +8,7 @@ source('NEON_Data_DownloadAndProcess.R')
 cdsapi <- reticulate::import_from_path("cdsapi",path="~/.conda/envs/myR_new2/lib/python3.11/site-packages")
 cclient <- cdsapi$Client()
 
-start_date <- as.Date("2022-01-01")
+start_date <- as.Date("2014-01-01")
 end_date <- as.Date("2022-01-31")
 
 variables <- tibble::tribble(
@@ -20,11 +20,18 @@ variables <- tibble::tribble(
   "eastward_wind", "m/s", "10m_u_component_of_wind", NA_character_,
   "northward_wind", "m/s", "10m_v_component_of_wind", NA_character_,
   "surface_downwelling_shortwave_flux_in_air", "W/m2", "surface_solar_radiation_downwards", NA_character_,
-  "surface_downwelling_longwave_flux_in_air", "W/m2", "surface_thermal_radiation_downwards", NA_character_
-  
+  "surface_downwelling_longwave_flux_in_air", "W/m2", "surface_thermal_radiation_downwards", NA_character_,
+  "soil_temperature_level_1","Kelvin","soil_temperature_level_1",NA_character_,
+  "soil_temperature_level_2","Kelvin","soil_temperature_level_2",NA_character_,
+  "soil_temperature_level_3","Kelvin","soil_temperature_level_3",NA_character_,
+  "soil_temperature_level_4","Kelvin","soil_temperature_level_4",NA_character_,
+  'volumetric_soil_water_layer_1','m3/m3','volumetric_soil_water_layer_1',NA_character_,
+  'volumetric_soil_water_layer_2','m3/m3','volumetric_soil_water_layer_2',NA_character_,
+  'volumetric_soil_water_layer_3','m3/m3','volumetric_soil_water_layer_3',NA_character_,
+  'volumetric_soil_water_layer_4','m3/m3','volumetric_soil_water_layer_4',NA_character_
 ) #Some examples (see more at: https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-single-levels?tab=overview)
 
-var <- variables[["api_name"]][[1]] #Only include the first variable
+var <- variables[["api_name"]]
 
 for(s in seq_along(NEON_siteNames)){
   siteID <- NEON_siteNames[s]
@@ -33,8 +40,7 @@ for(s in seq_along(NEON_siteNames)){
[…]

### 2023-02-06 NEON_Data_DownloadAndProcess.R
updated for plant structure

@@ -27,6 +27,8 @@ combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath,s
         subDat <- read.csv(paste0(dataPath,dataName,"/",NEON_siteNames[s],'/filesToStack',IDnum,'/stackedFiles/',inFileName))
         if(dataName%in%c("NEON_soilProperties","NEON_Roots","NEON_litterfall","NEON_plantFoliarTraits")){
           allData <- rbind(allData,subDat[,c('siteID','collectDate',selectColumns)])
+        }else if(dataName=="NEON_vegetation_structure"){
+          allData <- rbind(allData,subDat[,c('siteID','date',selectColumns)])
         }else{
           allData <- rbind(allData,subDat[,c('siteID','startDateTime',selectColumns)])
         }

### 2023-02-06 manuscriptCode_phenologyAndMycorrhizae.Rmd
Plotting NEON met data
Combining NEON data

@@
 source('NEON_Data_DownloadAndProcess.R')
+downloadData=FALSE #Change to true if you need to download data 
 ```
@@
 
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+}
 combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
@@
 varName <- 'tempSingleMean'
-
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+}
 combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
@@
 
-#Precipitation
+#NEON Precipitation
 ```{r,eval=FALSE}
@@
 varName <- "precipBulk"
-
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+}
 combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
@@
 calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)
+
 gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)
@@
 
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+}
 combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
@@
 
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+}
 
@@
 
-#Download NEON Soil Microbe Data
-```{r,eval=FALSE}
-dataName="NEON_SoilMicrobeComposition"
-NEON_ID='DP1.10081.001'
-#selectColumns <-
-inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
-#varName <-
-
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #Note: I had to modify this function to remove the indices for sites that didn't seem to have data. 
-combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath)
-```
-
-#Download NEON Soil Physical and Chemical Properties
-```{r,eval=FALSE}
-dataName <- "NEON_soilProperties"
-NEON_ID <- "DP1.10086.001"
-if(!file.exists(paste0(dataPath,"/",dataName))){
-  dir.create(paste0(dataPath,"/",dataName))
-}
-
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
-
-inFileName <- "sls_soilCoreCollection.csv"
-selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
-                   'soilTemp','litterDepth')
-dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
-
-dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
-  group_by(siteID,collectDate,plotID,decimalLatitude,decimalLongitude,elevation,horizon) %>% 
-  summarise(soilTemp=mean(soilTemp),litterDepth=mean(litterDepth))
-
-inFileName <- "sls_soilpH.csv"
-selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH')
-dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
-
-dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% group_by(siteID,collectDate,plotID,horizon) %>%
-  summarise(soilInWaterpH=mean(soilInWaterpH),soilInWaterpH=mean(soilInWaterpH))
-
-allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))
-
-inFileName <- "sls_soilMoisture.csv"
-selectColumns <- c('plotID','horizon','soilMoisture','dryMassFraction')
-dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
-                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
-dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d"))%>% group_by(siteID,collectDate,plotID,horizon) %>%
-  summarise(soilMoisture=mean(soilMoisture),dryMassFraction=mean(dryMassFraction)) 
-allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))
-
-outFileName <- paste0(dataName,"ALLdata.csv")
-write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
-```
-
 #Download Soil Temp
@@
 
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30 
+}
 
@@
 
+#Download NEON Soil Microbe Data
+```{r,eval=FALSE}
+dataName="NEON_SoilMicrobeComposition"
+NEON_ID='DP1.10081.001'
+#selectColumns <-
+inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
+#varName <- 
+if(downloadData){
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #Note: I had to modify this function to remove the indices for sites that didn't seem to have data. 
+}
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
+```
+
+#Download NEON Soil Physical and Chemical Properties
+```{r,eval=FALSE}
+dataName <- "NEON_soilProperties"
+NEON_ID <- "DP1.10086.001"
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+if(downloadData){
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+}
+
+inFileName <- "sls_soilCoreCollection.csv"
+selectColumns <- c('plotID','decimalLatitude','decimalLongitude','elevation','standingWaterDepth','horizon',
+                   'soilTemp','litterDepth')
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
+  mutate(year=lubridate::year(collectDate)) %>%
+  group_by(siteID,year,decimalLatitude,decimalLongitude,elevation,horizon) %>% 
+  summarise(soilTemp=mean(soilTemp),litterDepth=mean(litterDepth))
+
+inFileName <- "sls_soilpH.csv"
+selectColumns <- c('plotID','horizon','soilInWaterpH','soilInCaClpH')
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+
+dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
+  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year,horizon) %>%
+  summarise(soilInWaterpH=mean(soilInWaterpH),soilInWaterpH=mean(soilInWaterpH))
+
+allDat <- full_join(dat1,dat2,by=c('siteID','year','horizon'))
+
+inFileName <- "sls_soilMoisture.csv"
+selectColumns <- c('plotID','horizon','soilMoisture','dryMassFraction')
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
+  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year,horizon) %>%
+  summarise(soilMoisture=mean(soilMoisture),dryMassFraction=mean(dryMassFraction)) 
+allDat <- full_join(allDat,dat3,by=c('siteID','year','horizon'))
+
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
+```
+
 #NEON Root Characteristics
@@
 }
-
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30 
+}
 
@@
   dplyr::select(-c(sampleVolume,dryMass,somDryMass)) %>% 
-  group_by(siteID,collectDate,plotID) %>% summarise(densityMean=mean(density),somDensityMean=mean(somDensity))
+  mutate(year=lubridate::year(collectDate)) %>%
+  group_by(siteID,year) %>% summarise(densityMean=mean(density),somDensityMean=mean(somDensity))
 
@@
 
-dat2 <- dat2 %>% group_by(siteID,collectDate,plotID) %>%
+dat2 <- dat2  %>% 
+  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year) %>%
   summarise(litterDepth=mean(litterDepth))
 
-allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID'))
+allDat <- full_join(dat1,dat2,by=c('siteID','year'))
 
@@
 
-dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
+dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d"))%>% 
+  mutate(year=lubridate::year(collectDate)) %>%
   filter(cnIsotopeQF=="OK",cnPercentQF=="OK") %>%
-  group_by(siteID,collectDate,plotID) %>% summarise(d15N=mean(d15N),
+  group_by(siteID,year) %>% summarise(d15N=mean(d15N),
                                                     d13C=mean(d13C),
@@
 
-allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID'))
+allDat <- full_join(allDat,dat3,by=c('siteID','year'))
 
@@
 
-dat4 <- dat4 %>% group_by(siteID,collectDate,plotID) %>%
+dat4 <- dat4 %>% 
+  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year) %>%
   summarise(rootDryMass=mean(rootDryMass),
@@
 
-allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','plotID'))
+allDat <- full_join(allDat,dat4,by=c('siteID','year'))
+
 outFileName <- paste0(dataName,"ALLdata.csv")
@@
 ```{r}
+dataName="NEON_vegetation_structure"
+NEON_ID="DP1.10098.001"
+
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+if(downloadData){
+downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,includedSeq=42:47) #No: 2, 18,26, 38, 41
+}
+
+inFileName <- 'vst_apparentindividual.csv'
+selectColumns <- c('plotID','individualID','growthForm','plantStatus',
+                   'stemDiameter','measurementHeight','height',
+                   'baseCrownHeight','maxCrownDiameter','canopyPosition')
+dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,
+                        dataPath=dataPath, saveFile = FALSE)
+dat1 <- dat1 %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)
+
+inFileName <- 'vst_non-woody.csv'
+selectColumns <- c('plotID','individualID','growthForm','plantStatus',
+                   'stemDiameter','measurementHeight','height',
+                   'baseCrownHeight','maxCrownDiameter','canopyPosition',
+                   'scientificName')
+dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,
+                        dataPath=dataPath, saveFile = FALSE)
+dat2 <- dat2 %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)
+
+inFileName <- 'vst_mappingandtagging.csv'
+selectColumns <- c('plotID','individualID','scientificName')
+dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
+                        selectColumns=selectColumns, inFileName=inFileName,
+                        dataPath=dataPath, saveFile = FALSE)
+dat3 <- dat3 %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)
+allDat <- full_join(dat2,dat3,by=c('siteID','year','individualID','scientificName'))
+
+allDat <- full_join(allDat,dat1,by=c('siteID','year','individualID',
+                                   'growthForm','plantStatus',
+                                   'stemDiameter','measurementHeight','height',
+                                   'baseCrownHeight','maxCrownDiameter','canopyPosition'))
+outFileName <- paste0(dataName,"ALLdata.csv")
+write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
 
@@
 dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
-  group_by(siteID,collectDate,plotID,plotType,setDate) %>%
+  mutate(year=lubridate::year(collectDate)) %>%
+  group_by(siteID,year,plotType,setDate) %>%
   summarise(d15N=mean(d15N), d13C=mean(d13C),nitrogenPercent=mean(nitrogenPercent),
@@
 dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
-  group_by(siteID,collectDate,plotID,setDate) %>%
+  mutate(year=lubridate::year(collectDate)) %>%
+  group_by(siteID,year,setDate) %>%
   summarise(ligninPercent=mean(ligninPercent),
@@
 
-allDat <- full_join(dat1,dat2,by=c('siteID','plotID','setDate'))
+allDat <- full_join(dat1,dat2,by=c('siteID','year'))
 
@@
 dat3 <- dat3 %>%
-  group_by(siteID,collectDate,plotID,setDate,functionalGroup) %>%
+  mutate(year=lubridate::year(collectDate)) %>%
+  group_by(siteID,year,setDate,functionalGroup) %>%
   summarise(dryMass=mean(dryMass))
 
-allDat <- full_join(allDat,dat3,by=c('siteID','plotID','setDate'))
+allDat <- full_join(allDat,dat3,by=c('siteID','year'))
 
@@
 
+if(downloadData){
 downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30 
+}
 
@@
 inFileName <- "cfc_chlorophyll.csv"
-# selectColumns <- c('plotID','chlCarotWavelength1'),'chlCarotWavelength2',
-#                    'chlCarotWavelength3','chlCarotWavelength4',
-#                    'chlCarotWavelength1Abs','chlCarotWavelength2Abs',
-#                    'chlCarotWavelength3Abs','chlCarotWavelength4Abs',
-#                    'extractChlAConc','extractChlBConc')
 selectColumns <- c('plotID','extractChlAConc','extractChlBConc','extractCarotConc','sampleID')
@@
 
-allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','sampleID','plotType'))
-allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','sampleID','plotID'))
-allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','sampleID','plotID'))
-allDat <- full_join(allDat,dat5,by=c('siteID','collectDate','sampleID','plotID','plotType'))
-##
 allDat <- full_join(dat2,dat3,by=c('siteID','plotID','collectDate','sampleID'))
@@
   mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
-  group_by(siteID,collectDate,plotID,plotType) %>%
+  mutate(year=lubridate::year(collectDate)) %>%
+  group_by(siteID,year,plotType) %>%
   summarise(percentGreen=mean(percentGreen),leafMassPerArea=mean(leafMassPerArea),

### 2023-02-06 combineAllData.R

@@ -1,0 +1,81 @@
+#Load all NEON data 
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
+#NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association)
+p=2 #For only breaking leaf buds 
+phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
+phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
+
+#NEON Soil Physical and Chemical Properties
+dataName <- "NEON_soilProperties"
+outFileName <- paste0(dataName,"ALLdata.csv")
+soilPropDat <- read.csv(file=paste0(dataPath,outFileName)) %>% filter(horizon!="")
+soilPropDat <- pivot_wider(soilPropDat,names_from=6,values_from=7:11) %>%
+  dplyr::select(-decimalLatitude,decimalLongitude,elevation)
+
+allComDat <- left_join(phenoDat,soilPropDat,by=c('siteID','year'))
+
+#NEON Root Characteristics
+dataName="NEON_Roots"
+outFileName <- paste0(dataName,"ALLdata.csv")
+rootDat <- read.csv(file=paste0(dataPath,outFileName))
+colnames(rootDat)[3:12] <- paste0('root_',colnames(rootDat[3:12]))
+allComDat <- left_join(allComDat,rootDat,by=c('siteID','year'))
+
+#NEON Litterfall
+dataName="NEON_litterfall"
+outFileName <- paste0(dataName,"ALLdata.csv")
+litterDat <- read.csv(file=paste0(dataPath,outFileName)) %>% dplyr::select(-c(plotType,setDate.x,setDate.y,setDate))
+colnames(litterDat)[3:11] <- paste0('litter_',colnames(litterDat)[3:11])
+allComDat <- left_join(allComDat,litterDat,by=c('siteID','year'))
+
+#NEON Foliar Traits
+dataName="NEON_plantFoliarTraits"
+outFileName <- paste0(dataName,"ALLdata.csv")
+foliarTraitDat <- read.csv(file=paste0(dataPath,outFileName)) %>% dplyr::select(-plotType)
[…]

### 2023-02-06 combineERA5data.R

@@ -1,0 +1,47 @@
+library('devtools')
+library('ncdf4')
+library("reticulate")
+library(data.table)
+
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+
+combineERA5data <- function(siteID){
+  lat <- siteData$field_latitude[siteData$field_site_id==siteID]
+  long <- siteData$field_longitude[siteData$field_site_id==siteID]
+  siteDat <- matrix(nrow=0,ncol=7)
+  for(yr in 2014:2022){
+    start_date <- as.Date(paste0(yr,"-01-01"))
+    end_date <- as.Date(paste0(yr,"-12-31"))
+    
+    fileName <- paste0(dataPath,'ERA5/',siteID,"_",start_date,"_",end_date,"_era5Members.nc")
+    print(fileName)
+    if(file.exists(fileName)){
+      nc <- nc_open(fileName)
+      vars <- names(nc$var)
+      time <- as.integer(ncdf4::ncvar_get(nc, "time"))
+      time <- as.POSIXct(time*3600, origin = "1900-01-01",tz = "GMT")
+      time <- as.Date(time)
+      for(v in vars){
+        dat <- ncvar_get(nc,varid=v)
+        if(yr==2022){ #For some reason, 2022 has an extra NAs. 
+          dat <- dat[,1,]
+        }
+        dat <- colMeans(dat)
+        datTime <- data.frame(var=dat,date=time) %>% group_by(date) %>% 
+          summarise(mean=mean(var),min=min(var),max=max(var)) %>%
+          pivot_longer(cols=2:4,names_to="funName",values_to="value") %>%
+          mutate(siteID=siteID,lat=lat,long=long,var=v)
+        siteDat <- rbind(siteDat,datTime)
+      }
+      nc_close(nc)
+    }
+  }
+  return(siteDat)
+}
+
+named.list <- lapply(NEON_siteNames,combineERA5data)
+
+allDat.matrix <-rbindlist(named.list)
+
+write.csv(paste0(dataPath,"ERA5_metData.csv"),allDat.matrix,row.names = FALSE,quote = FALSE)

### 2023-02-07 NEON_Data_DownloadAndProcess.R
Added code to calculate DDs and combine with phenoDat

@@ -103,6 +103,35 @@ calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
   
 }
 
+calculateGDD <- function(values){
+  offsets <- values-5
+  return(sum(offsets[offsets>0]))
+}
+
+calculateCDD <- function(values){
+  offsets <- 5-values
+  return(sum(offsets[offsets>0]))
+}
+
+calculateWeeklyWeather <- function(X,phenoRow,dataName,dat){
+    weekDat <- dat %>% filter(siteID==phenoRow[1],as.Date(date)%in%seq((as.Date(as.character(phenoRow[3]))-X*7-6),
+                                                                (as.Date(as.character(phenoRow[3]))-X*7),by="day"))
+    if(dataName%in%c('NEON_SingleAirTemperature')){
+      weekDat <- weekDat %>% group_by(verticalPosition) %>% summarise(GDD=calculateGDD(tempSingleMean),
+                                                                      CDD=calculateCDD(tempSingleMean)) %>%
+        mutate(week=X)
+    }
+    return(weekDat)
+}
+calculateAllWeeklyWeather <- function(X,dataName,dat,nWeeks){
+  allWeekDatList <- lapply(X=(0:(nWeeks-1)),FUN=calculateWeeklyWeather,phenoRow=X,dataName=dataName,dat=dat)
+  allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
+  if(dataName%in%c('NEON_SingleAirTemperature')){
+    allWeeks <- pivot_wider(allWeeks,names_from=c(1,4),values_from=2:3)
+  }
+  return(allWeeks)
+}
+
 gapFillFromDaymet <- function(dataName,dataPath,varName){
   allData <- read.csv(paste0(dataPath,dataName,'Dailydata.csv'))
   allOutput <- matrix(nrow=0,ncol=3)

### 2023-02-07 combineAllData.R

@@ -2,12 +2,12 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-#NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association)
+#NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
 p=2 #For only breaking leaf buds 
 phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
 phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
 
-#NEON Soil Physical and Chemical Properties
+#NEON Soil Physical and Chemical Properties ----
 dataName <- "NEON_soilProperties"
 outFileName <- paste0(dataName,"ALLdata.csv")
 soilPropDat <- read.csv(file=paste0(dataPath,outFileName)) %>% filter(horizon!="")
@@ -16,21 +16,21 @@ soilPropDat <- pivot_wider(soilPropDat,names_from=6,values_from=7:11) %>%
 
 allComDat <- left_join(phenoDat,soilPropDat,by=c('siteID','year'))
 
-#NEON Root Characteristics
+#NEON Root Characteristics ----
 dataName="NEON_Roots"
 outFileName <- paste0(dataName,"ALLdata.csv")
 rootDat <- read.csv(file=paste0(dataPath,outFileName))
 colnames(rootDat)[3:12] <- paste0('root_',colnames(rootDat[3:12]))
 allComDat <- left_join(allComDat,rootDat,by=c('siteID','year'))
 
-#NEON Litterfall
+#NEON Litterfall ----
 dataName="NEON_litterfall"
 outFileName <- paste0(dataName,"ALLdata.csv")
 litterDat <- read.csv(file=paste0(dataPath,outFileName)) %>% dplyr::select(-c(plotType,setDate.x,setDate.y,setDate))
 colnames(litterDat)[3:11] <- paste0('litter_',colnames(litterDat)[3:11])
 allComDat <- left_join(allComDat,litterDat,by=c('siteID','year'))
 
-#NEON Foliar Traits
+#NEON Foliar Traits ----
[…]

### 2023-02-07 combineERA5data.R

@@ -1,8 +1,3 @@
-library('devtools')
-library('ncdf4')
-library("reticulate")
-library(data.table)
-
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 

### 2023-02-07 sharedVariables.R

@@ -9,6 +9,10 @@ library("rhdf5") #
 library(daymetr) #
 library("neonUtilities") #
 library('broom')
+library(data.table)
+library('devtools')
+library('ncdf4')
+library("reticulate")
 
 #library(inborutils)
 

### 2023-02-07 combineAllData.R
updated

@@ -6,7 +6,7 @@ source('NEON_Data_DownloadAndProcess.R')
 p=2 #For only breaking leaf buds 
 phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
 phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
-
+print("loaded PhenoDat")
 #NEON Soil Physical and Chemical Properties ----
 dataName <- "NEON_soilProperties"
 outFileName <- paste0(dataName,"ALLdata.csv")
@@ -15,28 +15,28 @@ soilPropDat <- pivot_wider(soilPropDat,names_from=6,values_from=7:11) %>%
   dplyr::select(-decimalLatitude,decimalLongitude,elevation)
 
 allComDat <- left_join(phenoDat,soilPropDat,by=c('siteID','year'))
-
+print("loaded soilProp")
 #NEON Root Characteristics ----
 dataName="NEON_Roots"
 outFileName <- paste0(dataName,"ALLdata.csv")
 rootDat <- read.csv(file=paste0(dataPath,outFileName))
 colnames(rootDat)[3:12] <- paste0('root_',colnames(rootDat[3:12]))
 allComDat <- left_join(allComDat,rootDat,by=c('siteID','year'))
-
+print("loaded rootDat")
 #NEON Litterfall ----
 dataName="NEON_litterfall"
 outFileName <- paste0(dataName,"ALLdata.csv")
 litterDat <- read.csv(file=paste0(dataPath,outFileName)) %>% dplyr::select(-c(plotType,setDate.x,setDate.y,setDate))
 colnames(litterDat)[3:11] <- paste0('litter_',colnames(litterDat)[3:11])
 allComDat <- left_join(allComDat,litterDat,by=c('siteID','year'))
-
+print("loaded litterDat")
 #NEON Foliar Traits ----
 dataName="NEON_plantFoliarTraits"
 outFileName <- paste0(dataName,"ALLdata.csv")
 foliarTraitDat <- read.csv(file=paste0(dataPath,outFileName)) %>% dplyr::select(-plotType)
 colnames(foliarTraitDat)[3:24] <- paste0('foliarTrait_',colnames(foliarTraitDat)[3:24])
[…]

### 2023-02-09 manuscriptCode_phenologyAndMycorrhizae.Rmd
Added scripts to compute weekly met data based off of dates of phenophases transitions

@@
 source('NEON_Data_DownloadAndProcess.R')
+source('computeWeeklyMetData.R')
 downloadData=FALSE #Change to true if you need to download data 
@@
 
-Download NEON Data
+#Download and Process Individual NEON Data Products
 
-#NEON Phenology Observations 
+##NEON Phenology Observations 
 ```{r,eval=FALSE}
@@
 
-#Single Air Temperature At Various Heights 
+##NEON Single Air Temperature At Various Heights 
 ```{r,eval=FALSE}
@@
                 inFileName=inFileName,dataPath=dataPath)
-for(funName in c("mean","max","min")){
-  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName=funName)
+
+for(f in seq_along(funTypes)){
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
   #Calculate LRs
-  gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
-}
+  # gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
+} #****Need to rerun
 
@@
 
-#NEON Precipitation
+##NEON Precipitation
 ```{r,eval=FALSE}
@@
 
-gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)
+#gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)
 
@@
 
-#Download Photosynthetically active radiation (PAR)
+##NEON Photosynthetically active radiation (PAR)
 ```{r}
@@
                 inFileName=inFileName,dataPath=dataPath)
-funType=mean
-funName="mean"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 
-funType=min
-funName="min"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=max
-funName="max"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
+for(f in seq_along(funTypes)){
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
+}
 
@@
 
-#Download Relative Humidity
+##NEON Relative Humidity
 ```{r}
@@
 
-funType=mean
-funName="mean"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=min
-funName="min"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=max
-funName="max"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
+for(f in seq_along(funTypes)){
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType[f],funName=funName[f])
+}
 ```
 
-#Download Windspeed
+##NEON Windspeed
 ```{r}
@@
                 inFileName=inFileName,dataPath=dataPath)
-funType=mean
-funName="mean"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
 
-funType=min
-funName="min"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=max
-funName="max"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
+for(f in seq_along(funTypes)){
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
+}
 ```
 
-#Download Soil Temp
+##NEON Soil Temp
 ```{r}
@@
 
-funType=mean
-funName="mean"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=min
-funName="min"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
-funType=max
-funName="max"
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
-
+for(f in seq_along(funTypes)){
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
+}
 ```
 
-#Download NEON Soil Microbe Data
+##NEON Soil Microbe Data
 ```{r,eval=FALSE}
@@
 
-#Download NEON Soil Physical and Chemical Properties
-```{r,eval=FALSE}
+##NEON Soil Physical and Chemical Properties
+```{r}
 dataName <- "NEON_soilProperties"
@@
 
+allDat %>% filter(horizon!="")
+allDat <- pivot_wider(allDat,names_from=6,values_from=7:11)
+
+##Still need to run:
+inFileName <- "sls_soilChemistry.csv"
+selectColumns <- c('plotID','d15N','organicd13C','nitrogenPercent','organicCPercent',
+                   'CNratio')
+dat4 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
+dat4 <- dat4 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
+  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year) %>%
+  summarise(d15N=mean(d15N),organicd13C=mean(organicd13C),
+            nitrogenPercent=mean(nitrogenPercent),organicCPercent=mean(organicCPercent),
+            CNratio=mean(CNratio)) 
+allDat <- full_join(allDat,dat4,by=c('siteID','year'))
+
 outFileName <- paste0(dataName,"ALLdata.csv")
@@
 
-#NEON Root Characteristics
-```{r, eval=FALSE}
+##NEON Root Characteristics
+```{r}
 dataName="NEON_Roots"
@@
 
-#NEON Plant Structural Characteristics
+##NEON Plant Structural Characteristics
 ```{r}
@@
 
-#NEON Litterfall
+##NEON Litterfall
 ```{r}
-dataName="NEON_litterfall" #No: 2, 7,8, 11, 17, 18, 20, 23, 25, 27, 38, 41, 45
+dataName="NEON_litterfall"
 NEON_ID="DP1.10033.001"
@@
 if(downloadData){
-downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
+  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,includedSeq=(1:47)[-c(2,7,8,11,17,18,20,23,25,27,38,41,45)])
 }
@@
 
-#NEON Foliar Traits
+##NEON Foliar Traits
 ```{r}
@@
 write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
+```
+
+##NEON PhenoCam Observations
+```{r,eval=FALSE}
+source('determinePhenoCamURLs.R')
+source('downloadPhenoCamAndCalculateTransitions.R') #Still need to change to have it save it somewhere
+```
+
+##ERA5 Met Data
+```{r}
+source('downloadERA5.R')
+source('combineERA5data.R')
+```
+
+##Calculate NEON Photoperiods
+```{r}
+source('calculateNEON_photoperiods.R')
 
@@
 
-#NEON PhenoCam Observations
-```{r,eval=FALSE}
-source('determinePhenoCamURLs.R')
-source('downloadPhenoCamAndCalculateTransitions.R') #Still need to change to have it save it somewhere
+#Combine NEON Data for each site
+```{r}
 

### 2023-02-09 NEON_Data_DownloadAndProcess.R

@@ -113,25 +113,6 @@ calculateCDD <- function(values){
   return(sum(offsets[offsets>0]))
 }
 
-calculateWeeklyWeather <- function(X,phenoRow,dataName,dat){
-    weekDat <- dat %>% filter(siteID==phenoRow[1],as.Date(date)%in%seq((as.Date(as.character(phenoRow[3]))-X*7-6),
-                                                                (as.Date(as.character(phenoRow[3]))-X*7),by="day"))
-    if(dataName%in%c('NEON_SingleAirTemperature')){
-      weekDat <- weekDat %>% group_by(verticalPosition) %>% summarise(GDD=calculateGDD(tempSingleMean),
-                                                                      CDD=calculateCDD(tempSingleMean)) %>%
-        mutate(week=X)
-    }
-    return(weekDat)
-}
-calculateAllWeeklyWeather <- function(X,dataName,dat,nWeeks){
-  allWeekDatList <- lapply(X=(0:(nWeeks-1)),FUN=calculateWeeklyWeather,phenoRow=X,dataName=dataName,dat=dat)
-  allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
-  if(dataName%in%c('NEON_SingleAirTemperature')){
-    allWeeks <- pivot_wider(allWeeks,names_from=c(1,4),values_from=2:3)
-  }
-  return(allWeeks)
-}
-
 gapFillFromDaymet <- function(dataName,dataPath,varName){
   allData <- read.csv(paste0(dataPath,dataName,'Dailydata.csv'))
   allOutput <- matrix(nrow=0,ncol=3)

### 2023-02-09 combineAllData.R

@@ -10,9 +10,8 @@ print("loaded PhenoDat")
 #NEON Soil Physical and Chemical Properties ----
 dataName <- "NEON_soilProperties"
 outFileName <- paste0(dataName,"ALLdata.csv")
-soilPropDat <- read.csv(file=paste0(dataPath,outFileName)) %>% filter(horizon!="")
-soilPropDat <- pivot_wider(soilPropDat,names_from=6,values_from=7:11) %>%
-  dplyr::select(-decimalLatitude,decimalLongitude,elevation)
+soilPropDat <- read.csv(file=paste0(dataPath,outFileName))
+soilPropDat <- soilPropDat %>% dplyr::select(-c(decimalLatitude,decimalLongitude,elevation))
 
 allComDat <- left_join(phenoDat,soilPropDat,by=c('siteID','year'))
 print("loaded soilProp")

### 2023-02-09 computeWeeklyMetData.R

@@ -1,0 +1,39 @@
+calculateWeeklyWeather <- function(X,phenoRow,dataName,dat){
+  weekDat <- dat %>% filter(siteID==phenoRow[1],as.Date(date)%in%seq((as.Date(as.character(phenoRow[2]))-X*7-6),
+                                                                     (as.Date(as.character(phenoRow[2]))-X*7),by="day"))
+  if(dataName%in%c('NEON_SingleAirTemperature')){
+    weekDat <- weekDat %>% group_by(verticalPosition) %>% summarise(GDD=calculateGDD(tempSingleMean),
+                                                                    CDD=calculateCDD(tempSingleMean)) %>%
+      mutate(week=X,siteID=phenoRow[1],date=phenoRow[2])
+  }
+  return(weekDat)
+}
+calculateAllWeeklyWeather <- function(X,dataName,dat,nWeeks){
+  allWeekDatList <- lapply(X=(0:(nWeeks-1)),FUN=calculateWeeklyWeather,phenoRow=X,dataName=dataName,dat=dat)
+  allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
+  if(dataName%in%c('NEON_SingleAirTemperature')){
+    allWeeks <- pivot_wider(allWeeks,names_from=c(1,4),values_from=2:3)
+  }
+  return(allWeeks)
+}
+
+computeWeeklyMetDataFiles <- function(p,siteID,dataName,dataPath,funName,nWeeks){
+  #p=2 #For only breaking leaf buds 
+  phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
+  phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p]) %>%
+    dplyr::select(siteID,date) %>% unique()
+  
+  metDat <- read.csv(paste0(dataPath,dataName,"Dailydata_",funName,".csv"))
+  
+  metList=apply(X=phenoDat,MARGIN=1,FUN=calculateAllWeeklyWeather,
+                 dataName=dataName,dat=metDat,nWeeks=nWeeks)
+  metList_unlisted <-rbindlist(metList,fill=TRUE)
+  write.csv(paste0(dataPath,dataName,"_computedWeeklydata_",funName,"_",siteID,".csv"))
+  
+}
+
+
+
+
+
+

### 2023-02-09 computeWeeklyMetData_Script.R

@@ -1,0 +1,16 @@
+args = commandArgs(trailingOnly=TRUE)
+print(args)
+my_task_id=as.numeric(args[1])
+num_tasks=as.numeric(args[2])
+fnames <- 1:47
+my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+
+for(s in my_fnames){
+  source('sharedVariables.R')
+  source('NEON_Data_DownloadAndProcess.R')
+  source('computeWeeklyMetData.R')
+  funName="mean"
+  dataName="NEON_SingleAirTemperature"
+  computeWeeklyMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+                            dataPath=dataPath,funName="mean",nWeeks=4) 
+}

### 2023-02-09 sharedVariables.R

@@ -32,3 +32,6 @@ siteData <- siteData %>% filter(field_site_type%in%c("Gradient Terrestrial","Cor
 NEON_phenophase_names <- c("Young leaves","Breaking leaf buds","Colored leaves","Increasing leaf size","Leaves","Falling leaves","Young needles","Breaking needle buds","Initial growth","Emerging needles","Colored needles","Needles","Falling needles")
 mediumIntensity_phenophases <- c("11 to 100","11 to 100","25-49%","25-49%","25-49%","50-74%","11 to 100","11 to 100",NA,"11 to 100","25-49%","25-49%",NA)
 NEON_PFTs <- c("Deciduous broadleaf","Semi-evergreen broadleaf","Evergreen broadleaf","Drought deciduous broadleaf","Graminoid","Forb","Evergreen conifer","Semi-evergreen forb","Pine","Deciduous conifer")
+
+funTypes <- c(mean,max,min)
+funNames <- c("mean","max","min")

### 2023-02-10 combineERA5data.R
typo

@@ -39,4 +39,4 @@ named.list <- lapply(NEON_siteNames,combineERA5data)
 
 allDat.matrix <-rbindlist(named.list)
 
-write.csv(paste0(dataPath,"ERA5_metData.csv"),allDat.matrix,row.names = FALSE,quote = FALSE)
+write.csv(file=paste0(dataPath,"ERA5_metData.csv"),allDat.matrix,row.names = FALSE,quote = FALSE)

### 2023-02-10 manuscriptCode_phenologyAndMycorrhizae.Rmd
Fit LRs to ERA data and used to gap fill temp and precip

@@
 for(f in seq_along(funTypes)){
-  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
-  #Calculate LRs
-  # gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
-} #****Need to rerun
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
+  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
+}
 
@@
                 inFileName=inFileName,dataPath=dataPath)
-calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)
+calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName="sum")
 
-#gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)
+gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName="sum")
 

### 2023-02-10 NEON_Data_DownloadAndProcess.R

@@ -56,7 +56,16 @@ combineNEONdata <- function(dataName,NEON_ID,selectColumns,inFileName,dataPath,s
   }
 }
 
-calculateDailyWeather <- function(dataName,dataPath,varName,funType,funName){
+calculateDailyWeather <- function(dataName,dataPath,varName,funName){
+  if(funName=="mean"){
+    funType <- mean
+  }else if(funName=="min"){
+    funType <- min
+  }else if(funName=="max"){
+    funType <- max
+  }else if(funName=="sum"){
+    funType <- sum
+  }
   inFileName <- paste0(dataName,"ALLdata.csv")
   outFileName <- paste0(dataName,"Dailydata_",as.character(funName),".csv")
   print(outFileName)
@@ -236,4 +245,88 @@ gapFillFromDayMet_verticalProfiles <- function(dataName,dataPath,varName,funName
   }
 
   write.csv(file=paste0(dataPath,dataName,'Dailydata_',funName,'_gapFilled.csv'),allOutput,row.names = FALSE,quote=FALSE)
+}
+
+gapFillFromERA_verticalProfiles <- function(dataName,dataPath,varName,funName){
+  allData <- read.csv(paste0(dataPath,dataName,"Dailydata_",as.character(funName),".csv"))
+  ERALRs <- read.csv(file=paste0(dataName,"towerHeight_LRfitsWithERA5_",dataName,"_",funName,".csv"))
+  
+  ERALRs <- ERALRs %>% dplyr::select(siteID,week,verticalPosition,term,estimate)
+  ERALRs <- pivot_wider(ERALRs,names_from = term,values_from = estimate)
+  colnames(ERALRs) <- c("siteID","week","verticalPosition","intercept","slope")
+  
+  ERAdat <- read.csv(paste0(dataPath,'ERA5_metData.csv'),header=TRUE)
+  if(dataName=="NEON_SingleAirTemperature"){
+    ERAdataName <- 't2m'
+  }else if(dataName=="NEON_PrecipitationData"){ #Total precipitation
+    ERAdataName <- "tp"
+  }
+  ERAdat <- ERAdat %>% filter(var==ERAdataName)
+  if(ERAdataName=="t2m"){
+    ERAdat$value <- as.numeric(ERAdat$value)-273 #Convert K to C
+  }
+  
[…]

### 2023-02-10 combineERA5data.R

@@ -24,8 +24,8 @@ combineERA5data <- function(siteID){
         }
         dat <- colMeans(dat)
         datTime <- data.frame(var=dat,date=time) %>% group_by(date) %>% 
-          summarise(mean=mean(var),min=min(var),max=max(var)) %>%
-          pivot_longer(cols=2:4,names_to="funName",values_to="value") %>%
+          summarise(mean=mean(var),min=min(var),max=max(var),sum=sum(var)) %>%
+          pivot_longer(cols=2:5,names_to="funName",values_to="value") %>%
           mutate(siteID=siteID,lat=lat,long=long,var=v)
         siteDat <- rbind(siteDat,datTime)
       }

### 2023-02-10 computeWeeklyMetData.R

@@ -28,7 +28,7 @@ computeWeeklyMetDataFiles <- function(p,siteID,dataName,dataPath,funName,nWeeks)
   metList=apply(X=phenoDat,MARGIN=1,FUN=calculateAllWeeklyWeather,
                  dataName=dataName,dat=metDat,nWeeks=nWeeks)
   metList_unlisted <-rbindlist(metList,fill=TRUE)
-  write.csv(paste0(dataPath,dataName,"_computedWeeklydata_",funName,"_",siteID,".csv"))
+  write.csv(metList_unlisted,file=paste0(dataPath,dataName,"_computedWeeklyData_",funName,"_",siteID,".csv"))
   
 }
 

### 2023-02-10 computeWeeklyMetData_Script.R

@@ -12,5 +12,10 @@ for(s in my_fnames){
   funName="mean"
   dataName="NEON_SingleAirTemperature"
   computeWeeklyMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
-                            dataPath=dataPath,funName="mean",nWeeks=4) 
+                            dataPath=dataPath,funName=funName,nWeeks=8) 
+  
+  funName="sum"
+  dataName="NEON_PrecipitationData"
+  computeWeeklyMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+                            dataPath=dataPath,funName=funName,nWeeks=8) 
 }

### 2023-02-10 createVerticalProfileLRs.R

@@ -2,8 +2,53 @@ source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
 dataName="NEON_SingleAirTemperature"
+dataName="NEON_PrecipitationData"
+varName="precipBulk"
 
-for(summaryStat in c("mean","min","max")){
+ERAdat <- read.csv(paste0(dataPath,'ERA5_metData.csv'),header=TRUE)
+if(dataName=="NEON_SingleAirTemperature"){
+  ERAdataName <- 't2m'
+  summaryStats <- c("mean","min","max")
+}else if(dataName=="NEON_PrecipitationData"){ #Total precipitation
+  ERAdataName <- "tp"
+  summaryStats <- "sum"
+}#else if(dataName==){ #Surface pressure
+#   ERAdataName <- "sp"
+# }else if(dataName==){ #2m dewpoint temperature
+#   ERAdataName <- 'd2m'
+# }else if(dataName==){ #10 metre u wind component
+#   ERAdataName <- "u10"
+# }else if(dataName==){ #10 metre V wind component
+#   ERAdataName <- "v10"
+# }else if(dataName==){#Soil temperature level 1
+#   ERAdataName <- "stl1"
+# }else if(dataName==){#Soil temperature level 2
+#   ERAdataName <- "stl2"
+# }else if(dataName==){#Soil temperature level 3
+#   ERAdataName <- "stl3"
+# }else if(dataName==){ #Soil temperature level 4
+#   ERAdataName <- "stl4"
+# }else if(dataName==){#Volumetric soil water layer 1
+#   ERAdataName <- "swvl1"
+# }else if(dataName==){#Volumetric soil water layer 2
+#   ERAdataName <- "swvl2"
+# }else if(dataName==){#Volumetric soil water layer 3
+#   ERAdataName <- "swvl3"
+# }else if(dataName==){ #Volumetric soil water layer 4
+#   ERAdataName <- "swvl4"
+# }
+
+
+
+ERAdat <- ERAdat %>% filter(var==ERAdataName)
+if(ERAdataName=="t2m"){
+  ERAdat$value <- as.numeric(ERAdat$value)-273 #Convert K to C
+}
+
+ERAdat <- pivot_wider(ERAdat,names_from=2,values_from=3)
+
+
+for(summaryStat in summaryStats){
   allData <- read.csv(paste0(dataPath,dataName,'Dailydata_',summaryStat,'.csv'))
   
[…]

### 2023-02-10 plotNEON_metData.R

@@ -2,18 +2,21 @@
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 
-dataNames <- c("NEON_SingleAirTemperature","NEON_PrecipitationData","NEON_PAR",
-               "NEON_relativeHumidity","NEON_Windspeed","NEON_SoilTemp")
+# dataNames <- c("NEON_SingleAirTemperature","NEON_PrecipitationData","NEON_PAR",
+#                "NEON_relativeHumidity","NEON_Windspeed","NEON_SoilTemp")
+dataNames <- c("NEON_SingleAirTemperature","NEON_PrecipitationData")
 varNames <- c("tempSingleMean","precipBulk","PARMean","RHMean","windSpeedMean","soilTempMean")
-pdf('NEON_metData.pdf',height=5,width=12)
+pdf('NEON_metData2.pdf',height=5,width=12)
 for(i in seq_along(dataNames)){
   dataName <- dataNames[i]
   print(dataName)
   varName <- varNames[i]
   if(dataName=="NEON_SingleAirTemperature"){
-    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean_gapFilled.csv"),header=TRUE)
+    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean_ERAgapFilled.csv"),header=TRUE)
+    meanDat$value <- meanDat$tempSingleMean_mean
   }else if(dataName=="NEON_PrecipitationData"){
-    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_gapFilled.csv"),header=TRUE)
+    meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_sum_ERAgapFilled.csv"),header=TRUE)
+    meanDat$value <- meanDat$precipBulk_sum
   }else{
     meanDat <- read.csv(paste0(dataPath,dataName,"Dailydata_mean.csv"),header=TRUE)
   }
@@ -23,14 +26,13 @@ for(i in seq_along(dataNames)){
     siteName <- NEON_siteNames[s]
     siteMeanDat <- meanDat %>% filter(siteID==siteName)
     if(dataName=="NEON_PrecipitationData"){
-      print(ggplot(siteMeanDat,aes(x=as.Date(date),y=precipBulk)) +
+      print(ggplot(siteMeanDat,aes(x=as.Date(date),y=value)) +
         geom_point()+
         theme_classic()+
         ggtitle(siteName)+
[…]

### 2023-02-17 computeWeeklyMetData.R
Updated met functions to calcuate total over 4 months.

@@ -35,7 +35,7 @@ computeWeeklyMetDataFiles <- function(p,siteID,dataName,dataPath,funName,nWeeks)
     metDat <- read.csv(paste0(dataPath,dataName,"Dailydata_",funName,".csv"))
     
     metList=apply(X=phenoDat,MARGIN=1,FUN=calculateAllWeeklyWeather,
-                  dataName=dataName,dat=metDat,nWeeks=nWeeks)
+                  dataName=dataName,dat=metDat,nWeeks=nWeeks) #Calculates for each row 
     metList_unlisted <-rbindlist(metList,fill=TRUE)
     write.csv(metList_unlisted,file=paste0(dataPath,dataName,"_computedWeeklyData_",funName,"_",siteID,".csv"))
   }
@@ -47,6 +47,39 @@ readWeeklyMetDataFiles <- function(p,X,dataName,dataPath,funName){
     siteDat <- read.csv(file=paste0(dataPath,dataName,"_computedWeeklyData_",funName,"_",X,".csv"),header=TRUE)
     siteDat$X <- NULL
     return(siteDat)
+  }
+}
+
+calculateTotalWeather <- function(X,dataName,dat){
+  phenoRow=X
+  weekDat <- dat %>% filter(siteID==as.character(phenoRow[1]),as.Date(date)%in%seq((as.Date(as.character(phenoRow[2]))-120),
+                                                                                   (as.Date(as.character(phenoRow[2]))-1),by="day"))
+  if(dataName%in%c('NEON_SingleAirTemperature')){
+    weekDat <- weekDat %>% group_by(verticalPosition) %>% summarise(GDD=calculateGDD(tempSingleMean),
+                                                                    CDD=calculateCDD(tempSingleMean))
+  }else if(dataName=="NEON_PrecipitationData"){
+    weekDat <- weekDat %>% summarise(sumPrecip=sum(precipBulk)) 
+  }
+  weekDat <- weekDat %>%
+    mutate(siteID=as.character(phenoRow[1]),date=as.character(phenoRow[2]))
+  return(weekDat)
+}
+
+computeTotalMetDataFiles <- function(p,siteID,dataName,dataPath,funName,nWeeks){
+  siteName <- siteID
[…]

### 2023-02-17 computeWeeklyMetData_Script.R

@@ -1,27 +1,41 @@
-# args = commandArgs(trailingOnly=TRUE)
-# print(args)
-# my_task_id=as.numeric(args[1])
-# num_tasks=as.numeric(args[2])
+args = commandArgs(trailingOnly=TRUE)
+print(args)
+my_task_id=as.numeric(args[1])
+num_tasks=as.numeric(args[2])
 fnames <- 1:47
-my_fnames=fnames#[seq((my_task_id+1),47,num_tasks)]
-source('sharedVariables.R')
-source('NEON_Data_DownloadAndProcess.R')
-source('computeWeeklyMetData.R')
+my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+# source('sharedVariables.R')
+# source('NEON_Data_DownloadAndProcess.R')
+# source('computeWeeklyMetData.R')
 
 for(s in my_fnames){
-  # source('sharedVariables.R')
-  # source('NEON_Data_DownloadAndProcess.R')
-  # source('computeWeeklyMetData.R')
-  # funName="mean"
-  # dataName="NEON_SingleAirTemperature"
-  # computeWeeklyMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+  source('sharedVariables.R')
+  source('NEON_Data_DownloadAndProcess.R')
+  source('computeWeeklyMetData.R')
+  funName="mean"
+  dataName="NEON_SingleAirTemperature"
+
+  # funName="sum"
+  # dataName="NEON_PrecipitationData"
+  
+  # if(!file.exists(paste0(dataPath,dataName,"_computedWeeklyData_",funName,"_",NEON_siteNames[s],".csv"))){
+  # print(NEON_siteNames[s])
+  #   computeWeeklyMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
   #                           dataPath=dataPath,funName=funName,nWeeks=8)
+  # }
+  
+  if(!file.exists(paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
+    print(NEON_siteNames[s])
+    computeTotalMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+                              dataPath=dataPath,funName=funName)
+  }
   
   funName="sum"
   dataName="NEON_PrecipitationData"
[…]

### 2023-02-17 computeWeeklyMetData_Script.R
merging

@@ -1,17 +1,17 @@
-# args = commandArgs(trailingOnly=TRUE)
-# print(args)
-# my_task_id=as.numeric(args[1])
-# num_tasks=as.numeric(args[2])
+args = commandArgs(trailingOnly=TRUE)
+print(args)
+my_task_id=as.numeric(args[1])
+num_tasks=as.numeric(args[2])
 fnames <- 1:47
-my_fnames=fnames#[seq((my_task_id+1),47,num_tasks)]
-source('sharedVariables.R')
-source('NEON_Data_DownloadAndProcess.R')
-source('computeWeeklyMetData.R')
+my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+#source('sharedVariables.R')
+#source('NEON_Data_DownloadAndProcess.R')
+#source('computeWeeklyMetData.R')
 
 for(s in my_fnames){
-  # source('sharedVariables.R')
-  # source('NEON_Data_DownloadAndProcess.R')
-  # source('computeWeeklyMetData.R')
+  source('sharedVariables.R')
+  source('NEON_Data_DownloadAndProcess.R')
+  source('computeWeeklyMetData.R')
   # funName="mean"
   # dataName="NEON_SingleAirTemperature"
   # computeWeeklyMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,

### 2023-02-17 computeWeeklyMetData_Script.R
inconsistency

@@ -12,6 +12,7 @@ for(s in my_fnames){
   source('sharedVariables.R')
   source('NEON_Data_DownloadAndProcess.R')
   source('computeWeeklyMetData.R')
+  p=2
   funName="mean"
   dataName="NEON_SingleAirTemperature"
 
@@ -35,7 +36,7 @@ for(s in my_fnames){
   
   if(!file.exists(paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
     print(NEON_siteNames[s])
-    computeTotalMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+    computeTotalMetDataFiles(p=p,siteID=NEON_siteNames[s],dataName=dataName,
                              dataPath=dataPath,funName=funName)
   }
 }

### 2023-02-17 NEON_Data_DownloadAndProcess.R
Updated to include soil temperature

@@ -260,9 +260,11 @@ gapFillFromERA_verticalProfiles <- function(dataName,dataPath,varName,funName){
     ERAdataName <- 't2m'
   }else if(dataName=="NEON_PrecipitationData"){ #Total precipitation
     ERAdataName <- "tp"
+  }else if(dataName=="NEON_SoilTemp"){#Soil temperature level 1
+    ERAdataName <- "stl1"
   }
   ERAdat <- ERAdat %>% filter(var==ERAdataName)
-  if(ERAdataName=="t2m"){
+  if(ERAdataName%in%c("t2m","stl1")){
     ERAdat$value <- as.numeric(ERAdat$value)-273 #Convert K to C
   }
   
@@ -273,7 +275,7 @@ gapFillFromERA_verticalProfiles <- function(dataName,dataPath,varName,funName){
   for(s in seq_along(NEON_siteNames)){
     siteName <- NEON_siteNames[s]
     print(siteName)
-
+    
     siteDat <- allData %>% filter(siteID==siteName)
     if(dataName=="NEON_PrecipitationData"){
       siteDat$verticalPosition <- "top"
@@ -293,31 +295,45 @@ gapFillFromERA_verticalProfiles <- function(dataName,dataPath,varName,funName){
     }else if(funName=="sum"){
       ERAdatSite$ERAValue <- ERAdatSite$sum
     }
-
+    
     if(varName=='tempSingleMean'){
       siteDat$NEON_value <- siteDat$tempSingleMean
       siteDat <- siteDat %>% dplyr::select(-tempSingleMean)
     }else if(varName=='precipBulk'){
       siteDat$NEON_value <- siteDat$precipBulk
       siteDat <- siteDat %>% dplyr::select(-precipBulk)
+    }else if(varName=='soilTempMean'){
+      siteDat$NEON_value <- siteDat$soilTempMean
+      siteDat <- siteDat %>% dplyr::select(-soilTempMean)
     }
     ERAdatSite <- ERAdatSite %>% dplyr::select(date,siteID,ERAValue)
     allDayMet <- matrix(nrow=0,ncol=ncol(ERAdatSite)) ##
+    if(length(siteHeights)==0){
+      newERAdatSite <- ERAdatSite
+      newERAdatSite$verticalPosition <- 100
+      allDayMet <- rbind(allDayMet,newERAdatSite)
+    }
[…]

### 2023-02-17 manuscriptCode_phenologyAndMycorrhizae.Rmd

@@
   calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
-  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
+  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName[f])
 }
@@
 
-for(f in seq_along(funTypes)){
+for(f in seq_along(funNames)){
+  print(funNames[f])
   calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
+    gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
 }

### 2023-02-17 computeWeeklyMetData.R
updated

@@ -54,9 +54,12 @@ calculateTotalWeather <- function(X,dataName,dat){
   phenoRow=X
   weekDat <- dat %>% filter(siteID==as.character(phenoRow[1]),as.Date(date)%in%seq((as.Date(as.character(phenoRow[2]))-120),
                                                                                    (as.Date(as.character(phenoRow[2]))-1),by="day"))
-  if(dataName%in%c('NEON_SingleAirTemperature')){
+  if(dataName==('NEON_SingleAirTemperature')){
     weekDat <- weekDat %>% group_by(verticalPosition) %>% summarise(GDD=calculateGDD(tempSingleMean),
                                                                     CDD=calculateCDD(tempSingleMean))
+  }else if(dataName==('NEON_SoilTemp')){
+    weekDat <- weekDat %>% group_by(verticalPosition) %>% summarise(soil_GDD=calculateGDD(soilTempMean_mean),
+                                                                    soil_CDD=calculateCDD(soilTempMean_mean))
   }else if(dataName=="NEON_PrecipitationData"){
     weekDat <- weekDat %>% summarise(sumPrecip=sum(precipBulk)) 
   }
@@ -65,7 +68,7 @@ calculateTotalWeather <- function(X,dataName,dat){
   return(weekDat)
 }
 
-computeTotalMetDataFiles <- function(p,siteID,dataName,dataPath,funName,nWeeks){
+computeTotalMetDataFiles <- function(p,siteID,dataName,dataPath,funName){
   siteName <- siteID
   phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
   phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],siteID==siteName)
@@ -74,12 +77,20 @@ computeTotalMetDataFiles <- function(p,siteID,dataName,dataPath,funName,nWeeks){
     phenoDat <- phenoDat %>%
       dplyr::select(siteID,date) %>% unique()
     
-    metDat <- read.csv(paste0(dataPath,dataName,"Dailydata_",funName,".csv"))
+    metDat <- read.csv(paste0(dataPath,dataName,'Dailydata_',funName,'_ERAgapFilled.csv'))
     
[…]

### 2023-02-17 combineAllData.R
Updated combined data fixing issues and adding new variables

@@ -1,13 +1,14 @@
 #Load all NEON data 
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
-library(data.table)
+#library(data.table)
+source('computeWeeklyMetData.R')
 
 #NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
 p=2 #For only breaking leaf buds 
 phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
 phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p]) %>%
-  dplyr::select(siteID,year,dayOfYear,individualID,canopyPosition,plantStatus,stemDiameter,
+  dplyr::select(siteID,year,date,dayOfYear,individualID,canopyPosition,plantStatus,stemDiameter,
                 maxCanopyDiameter,percentCover,height,scientificName,growthForm,Mycorrhizal.type)
 #write.csv(phenoDat,file="phenoDat.csv",row.names=FALSE,quote=FALSE)
 
@@ -47,39 +48,148 @@ print("loaded soilProp")
 #NEON Single Air Temp at Various Heights ----
 dataName="NEON_SingleAirTemperature"
 funName="mean"
-tempDat <- read.csv(paste0(dataPath,dataName,"_computedWeeklyData_",funName,"_",'HARV',".csv"))
-tempDat <- tempDat %>% mutate(year=lubridate::year(tempDat$date)) %>% dplyr::select(-date,X)
+rm(phenoDat,soilPropDat,rootDat,litterDat,foliarTraitDat)
+allWeekDatList <- lapply(X=NEON_siteNames,FUN=readTotalMetDataFiles,p=p,
+                         dataName=dataName,dataPath=dataPath,funName=funName)
+allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
+rm(allWeekDatList)
 
+#tempDat <- read.csv(paste0(dataPath,dataName,"_computedWeeklyData_",funName,"_",'HARV',".csv"))
+#tempDat <- allWeeks %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)
+
+tempDat <- pivot_wider(allWeeks,names_from=verticalPosition,values_from=c(GDD,CDD))
+rm(allWeeks)
[…]

### 2023-03-20 manuscriptCode_phenologyAndMycorrhizae.Rmd
Updated to allow for more DD baselines

@@
 combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
-combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
+combineNEONdata_PhenoObs(saveType="firstOfPhenophase")
 combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
+combineNEONdata_PhenoObs(saveType="allStatusPhenophase",p=2)
+combineNEONdata_PhenoObs(saveType="allStatusPhenophase",p=3)
 ```
@@
 for(f in seq_along(funTypes)){
-  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
-  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName[f])
+  # calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
+  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
 }

### 2023-03-20 combineAllData.R

@@ -3,13 +3,36 @@ source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
 #library(data.table)
 source('computeWeeklyMetData.R')
+library('purrr')
 
 #NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
 p=2 #For only breaking leaf buds 
-phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
-phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p]) %>%
-  dplyr::select(siteID,year,date,dayOfYear,individualID,canopyPosition,plantStatus,stemDiameter,
+p=3 #For colored leaves
+#phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_AllStatus_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+phenoDat$phenoStatus <- "no"
+if(p==2){
+  phenoDat$phenoStatus[phenoDat$phenophaseIntensity=="11 to 100"] <- "yes"
+}else if(p==3){
+  phenoDat$phenoStatus[phenoDat$phenophaseIntensity=="5-24%"] <- "yes"
+}
+
+
+subPhenoDat <- phenoDat %>% filter(phenoStatus=="yes") %>%
+  group_by(year,individualID) %>% slice(1:1) %>% 
+  dplyr::select(year,date,individualID) 
+phenoDat <- left_join(phenoDat,subPhenoDat,by=c('year','individualID'))
+phenoDat <- phenoDat %>% filter(date.x <= date.y,!is.na(height))
+names(phenoDat)[names(phenoDat)=="date.x"] <- "date"
+
+phenoDat <- phenoDat %>%
+  dplyr::select(siteID,year,date,dayOfYear,individualID,phenoStatus,canopyPosition,plantStatus,stemDiameter,
                 maxCanopyDiameter,percentCover,height,scientificName,growthForm,Mycorrhizal.type)
[…]

### 2023-03-20 computeWeeklyMetData_Script.R

@@ -13,9 +13,11 @@ for(s in my_fnames){
   source('NEON_Data_DownloadAndProcess.R')
   source('computeWeeklyMetData.R')
   p=3 #Colored leaves
+  
   siteID=NEON_siteNames[s]
   funName="mean"
   dataName="NEON_SingleAirTemperature"
+  for(baseTemp in seq(0,20,5)){
 
   # funName="sum"
   # dataName="NEON_PrecipitationData"
@@ -26,27 +28,28 @@ for(s in my_fnames){
   #                           dataPath=dataPath,funName=funName,nWeeks=8)
   # }
 
-  if(!file.exists(paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
+  if(!file.exists(paste0(dataPath,dataName,"_",baseTemp,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
     print(NEON_siteNames[s])
     computeTotalMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
-                              dataPath=dataPath,funName=funName)
+                              dataPath=dataPath,funName=funName,baseTemp=baseTemp)
+  }
   }
 
-  funName="sum"
-  dataName="NEON_PrecipitationData"
-
-  if(!file.exists(paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
-    print(NEON_siteNames[s])
-    computeTotalMetDataFiles(p=p,siteID=NEON_siteNames[s],dataName=dataName,
-                             dataPath=dataPath,funName=funName)
-  }
-  
-  funName="mean"
-  dataName="NEON_SoilTemp"
-  
-  if(!file.exists(paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
-    print(NEON_siteNames[s])
-    computeTotalMetDataFiles(p=p,siteID=NEON_siteNames[s],dataName=dataName,
-                             dataPath=dataPath,funName=funName)
-  }
+  # funName="sum"
+  # dataName="NEON_PrecipitationData"
+  # 
[…]

### 2023-03-20 createModels.R

@@ -1,14 +1,280 @@
 source('sharedVariables.R')
 library(caTools)
 library('xgboost')
+library(randomForest)
+library('mgcv')
+options(stringsAsFactors = FALSE)
 
-p=2
+#Load Data and General Prep ----
+p=3
 load(file=paste0("allCombinedNEONDat_",gsub(" ","",NEON_phenophase_names[p]),".RData")) #Loaded as allComDat
-
+combinedDrought <- read.csv(file="droughtsAtNEON.csv")
 
 set.seed(0)
 specificCol <- "phenoStatus"
-selectAllComDat <- allComDat # %>% filter(growthForm=="Deciduous broadleaf")
+selectAllComDat <- allComDat %>% filter(growthForm=="Deciduous broadleaf")
+selectAllComDat <- left_join(selectAllComDat,combinedDrought,by=c("siteID","year"))
+selectAllComDat$month <- lubridate::month(as.Date(selectAllComDat$dayOfYear,
+                           origin=paste0((selectAllComDat$year-1),"-12-31")))
+selectAllComDat$dy <- lubridate::day(as.Date(selectAllComDat$dayOfYear,
+                                                  origin=paste0((selectAllComDat$year-1),"-12-31")))
+
+selectAllComDat$drought <- NA
+selectAllComDat$drought[selectAllComDat$month==1] <- selectAllComDat$X1[selectAllComDat$month==1]
+selectAllComDat$drought[selectAllComDat$month==2 &selectAllComDat$dy<15] <- selectAllComDat$X1[selectAllComDat$month==2 &selectAllComDat$dy<15]
+selectAllComDat$drought[selectAllComDat$month==2 &selectAllComDat$dy>14] <- selectAllComDat$X2[selectAllComDat$month==2 &selectAllComDat$dy>14]
+
+selectAllComDat$drought[selectAllComDat$month==3 &selectAllComDat$dy<15] <- selectAllComDat$X2[selectAllComDat$month==3 &selectAllComDat$dy<15]
+selectAllComDat$drought[selectAllComDat$month==3 &selectAllComDat$dy>14] <- selectAllComDat$X3[selectAllComDat$month==3 &selectAllComDat$dy>14]
+
[…]

### 2023-03-20 computeWeeklyMetData_Script.R
merging

@@ -19,7 +19,7 @@ for(s in my_fnames){
 
   if(!file.exists(paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
     print(NEON_siteNames[s])
-    computeTotalMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+    computeTotalMetDataFiles(p=p,siteID=NEON_siteNames[s],dataName=dataName,
                               dataPath=dataPath,funName=funName)
   }
 

### 2023-03-20 computeWeeklyMetData_Script.R
inconsistency

@@ -30,7 +30,7 @@ for(s in my_fnames){
 
   if(!file.exists(paste0(dataPath,dataName,"_",baseTemp,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",siteID,".csv"))){
     print(NEON_siteNames[s])
-    computeTotalMetDataFiles(p=2,siteID=NEON_siteNames[s],dataName=dataName,
+    computeTotalMetDataFiles(p=p,siteID=NEON_siteNames[s],dataName=dataName,
                               dataPath=dataPath,funName=funName,baseTemp=baseTemp)
   }
   }

### 2023-03-20 computeWeeklyMetData.R
added baseTemp to reading

@@ -91,11 +91,19 @@ computeTotalMetDataFiles <- function(p,siteID,dataName,dataPath,funName,baseTemp
   }
 }
 
-readTotalMetDataFiles <- function(p,X,dataName,dataPath,funName){
-  if(file.exists(file=paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",X,".csv"))){
-    siteDat <- read.csv(file=paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",X,".csv"),header=TRUE)
-    siteDat$X <- NULL
-    return(siteDat)
+readTotalMetDataFiles <- function(p,X,dataName,dataPath,funName,baseTemp){
+  if(dataName=="NEON_SingleAirTemperature"){
+    if(file.exists(file=paste0(dataPath,dataName,"_",baseTemp,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",X,".csv"))){
+      siteDat <- read.csv(file=paste0(dataPath,dataName,"_",baseTemp,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",X,".csv"),header=TRUE)
+      siteDat$X <- NULL
+      return(siteDat)
+    }
+  }else{
+    if(file.exists(file=paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",X,".csv"))){
+      siteDat <- read.csv(file=paste0(dataPath,dataName,"_computedTotalMetData_",gsub(" ","",NEON_phenophase_names[p]),"_",funName,"_",X,".csv"),header=TRUE)
+      siteDat$X <- NULL
+      return(siteDat)
+    }
   }
 }
 

### 2023-03-21 manuscriptCode_currentScript.R
stacking soil moisture

@@ -1,67 +1,77 @@
-# args = commandArgs(trailingOnly=TRUE)
-# print(args)
-# my_task_id=as.numeric(args[1])
-# num_tasks=as.numeric(args[2])
-# fnames <- 10:47
-# my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+args = commandArgs(trailingOnly=TRUE)
+print(args)
+my_task_id=as.numeric(args[1])
+num_tasks=as.numeric(args[2])
+fnames <- 1:47
+my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
+
+for(s in my_fnames){
+  #Load all NEON data 
+  source('sharedVariables.R')
+  source('NEON_Data_DownloadAndProcess.R')
+  #library(data.table)
+  dataName="NEON_SoilMoisture"
+  NEON_ID='DP1.00094.001'
+  
+  IDnum <- strsplit(NEON_ID,"[.]")[[1]][2]
+  print(s)
+  savePath <- paste0(dataPath,dataName,'/',NEON_siteNames[s])
+  stackByTable(paste0(savePath,'/filesToStack',IDnum))
+}
+
+
+# #NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
+# p=2 #For only breaking leaf buds 
+# phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))   
+# phenoDat <- phenoDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p]) %>%
+#   dplyr::select(siteID,year,dayOfYear,individualID,canopyPosition,plantStatus,stemDiameter,
+#                 maxCanopyDiameter,percentCover,height,scientificName,growthForm,Mycorrhizal.type)
+# #write.csv(phenoDat,file="phenoDat.csv",row.names=FALSE,quote=FALSE)
+# phenoDat <- phenoDat %>% filter(growthForm=="Deciduous broadleaf")
 # 
-# for(s in my_fnames){
-#Load all NEON data 
-source('sharedVariables.R')
-source('NEON_Data_DownloadAndProcess.R')
-library(data.table)
+# print("loaded PhenoDat")
+# #NEON Soil Physical and Chemical Properties ----
+# dataName <- "NEON_soilProperties"
[…]

### 2023-03-21 manuscriptCode_currentScript.R
trying

@@ -2,7 +2,7 @@ args = commandArgs(trailingOnly=TRUE)
 print(args)
 my_task_id=as.numeric(args[1])
 num_tasks=as.numeric(args[2])
-fnames <- 1:47
+fnames <- 47:1
 my_fnames=fnames[seq((my_task_id+1),47,num_tasks)]
 
 for(s in my_fnames){

### 2023-03-21 createVerticalProfileLRs.R
Updating for soil moisture

@@ -5,8 +5,10 @@ summaryStats <- c('mean','max','min','sum')
 #varName <- 'tempSingleMean'
 #dataName="NEON_PrecipitationData"
 #varName="precipBulk"
-dataName="NEON_SoilTemp"
-varName <- 'soilTempMean'
+# dataName="NEON_SoilTemp"
+# varName <- 'soilTempMean'
+dataName="NEON_SoilMoisture"
+varName <- 'soilMoistureMean'
 
 ERAdat <- read.csv(paste0(dataPath,'ERA5_metData.csv'),header=TRUE)
 if(dataName=="NEON_SingleAirTemperature"){
@@ -17,6 +19,9 @@ if(dataName=="NEON_SingleAirTemperature"){
   summaryStats <- "sum"
 }else if(dataName=="NEON_SoilTemp"){#Soil temperature level 1
   ERAdataName <- "stl1"
+}else if(dataName=="NEON_SoilMoisture"){#Volumetric soil water layer 1
+  ERAdataName <- "swvl1"
+  summaryStats <- c("mean","min","max")
 }#else if(dataName==){ #Surface pressure
 #   ERAdataName <- "sp"
 # }else if(dataName==){ #2m dewpoint temperature
@@ -25,9 +30,7 @@ if(dataName=="NEON_SingleAirTemperature"){
 #   ERAdataName <- "u10"
 # }else if(dataName==){ #10 metre V wind component
 #   ERAdataName <- "v10"
-# }else if(dataName==){#Soil temperature level 1
-#   ERAdataName <- "stl1"
-# }else if(dataName==){#Soil temperature level 2
+#else if(dataName==){#Soil temperature level 2
 #   ERAdataName <- "stl2"
 # }else if(dataName==){#Soil temperature level 3
 #   ERAdataName <- "stl3"
@@ -97,6 +100,9 @@ for(summaryStat in summaryStats){
       }else if(varName=='soilTempMean'){
         siteDat$NEON_value <- siteDat$soilTempMean
         siteDat <- siteDat %>% dplyr::select(-soilTempMean)
+      }else if(varName=="soilMoisture"){
+        siteDat$NEON_value <- siteDat$soilMoistureMean
+        siteDat <- siteDat %>% dplyr::select(-soilMoistureMean)
       }
       
       fittedModels <- siteDat %>% group_by(week,verticalPosition) %>% 

### 2023-03-27 manuscriptCode_phenologyAndMycorrhizae.Rmd
Adding the rest of the files before cleaning up

@@
   print(funNames[f])
-  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
+  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
     gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
 }
+```
+
+##NEON Soil Moisture
+```{r}
+dataName="NEON_SoilMoisture"
+NEON_ID='DP1.00094.001'
+if(!file.exists(paste0(dataPath,"/",dataName))){
+  dir.create(paste0(dataPath,"/",dataName))
+}
+
+if(downloadData){
+  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE,includedSeq=43:47) #No 30
+}
+
+selectColumns <- c('horizontalPosition','verticalPosition','VSWCMean','VSWCFinalQF')
+inFileName <- "SWS_30_minute.csv"
+varName <- 'VSWCMean'
+
+combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
+                inFileName=inFileName,dataPath=dataPath)
+
+#for(f in seq_along(funNames)[2:3]){
+f=1
+  print(funNames[f])
+  #calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
+  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
+#}
 ```

### 2023-03-27 combineAllData.R

@@ -72,8 +72,9 @@ print("loaded soilProp")
 dataName="NEON_SingleAirTemperature"
 funName="mean"
 rm(phenoDat,soilPropDat,rootDat,litterDat,foliarTraitDat)
+baseTemp <- 20
 allWeekDatList <- lapply(X=NEON_siteNames,FUN=readTotalMetDataFiles,p=p,
-                         dataName=dataName,dataPath=dataPath,funName=funName)
+                         dataName=dataName,dataPath=dataPath,funName=funName,baseTemp=baseTemp)
 allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
 rm(allWeekDatList)
 
@@ -134,6 +135,20 @@ rm(allWeeks)
 
 allComDat <- left_join(allComDat,soilTempDat,by=c('siteID','date'))
 rm(soilTempDat)
+
+#NEON Soil Moisture ----
+dataName="NEON_SoilMoisture"
+funName="mean"
+allWeekDatList <- lapply(X=NEON_siteNames,FUN=readTotalMetDataFiles,p=p,
+                         dataName=dataName,dataPath=dataPath,funName=funName)
+allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
+rm(allWeekDatList)
+
+soilMoistureDat <- pivot_wider(allWeeks,names_from=verticalPosition,values_from=soil_moisture)
+rm(allWeeks)
+
+allComDat <- left_join(allComDat,soilMoistureDat,by=c('siteID','date'))
+rm(soilMoistureDat)
 
 #Photoperiod ----
 photoperiodDat <- read.csv(file=paste0(dataPath,'NEON_sunlightTimes.csv'),header=TRUE)

### 2023-03-27 createModels.R

@@ -63,12 +63,15 @@ selectAllComDat$phenoStatus <- as.factor(selectAllComDat$phenoStatus)
 
 selectAllComDat$GDD_10 <- as.numeric(selectAllComDat$GDD_10)
 selectAllComDat$CDD_10 <- as.numeric(selectAllComDat$CDD_10)
+selectAllComDat$CDD_closest <- as.numeric(selectAllComDat$CDD_closest)
 selectAllComDat$daylength <- as.numeric(selectAllComDat$daylength)
-selectAllComDat$sumPrecip <- as.numeric(selectAllComDat$sumPrecip)
-selectAllComDat$soil_GDD_508 <- as.numeric(selectAllComDat$soil_GDD_508)
-selectAllComDat$soil_CDD_508 <- as.numeric(selectAllComDat$soil_CDD_508)
+selectAllComDat$soilMoisture <- as.numeric(selectAllComDat$`501`)
+
+#selectAllComDat$sumPrecip <- as.numeric(selectAllComDat$sumPrecip)
+#selectAllComDat$soil_GDD_508 <- as.numeric(selectAllComDat$soil_GDD_508)
+#selectAllComDat$soil_CDD_508 <- as.numeric(selectAllComDat$soil_CDD_508)
 selectAllComDat$drought <- as.numeric(selectAllComDat$drought)
-selectAllComDat$averageDrought <- as.numeric(selectAllComDat$averageDrought)
+#selectAllComDat$averageDrought <- as.numeric(selectAllComDat$averageDrought)
 
 selectAllComDat$Shade.tolerance <- as.numeric(selectAllComDat$Shade.tolerance)
 selectAllComDat$stemDiameter <- as.numeric(selectAllComDat$stemDiameter)
@@ -80,6 +83,8 @@ selectAllComDat$canopyPosition <- as.factor(selectAllComDat$canopyPosition)
 selectAllComDat$CNratio <- as.numeric(selectAllComDat$CNratio)
 selectAllComDat$field_mean_annual_temperature_C <- as.numeric(selectAllComDat$field_mean_annual_temperature_C)
 selectAllComDat$field_mean_annual_precipitation_mm <- as.numeric(selectAllComDat$field_mean_annual_precipitation_mm)
+
+selectAllComDat <- selectAllComDat %>% filter(!is.na(CDD_10))
 
[…]

### 2023-03-27 determineCDDbaseTemps.R

@@ -1,0 +1,142 @@
+#Determine CDD basetemps for each site in non-drought years
+source('sharedVariables.R')
+source('NEON_Data_DownloadAndProcess.R')
+#library(data.table)
+source('computeWeeklyMetData.R')
+library('purrr')
+
+#Load and Combine Data----
+#NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
+
+p=3 #For colored leaves
+phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_AllStatus_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+phenoDat$phenoStatus <- "no"
+if(p==2){
+  phenoDat$phenoStatus[phenoDat$phenophaseIntensity=="11 to 100"] <- "yes"
+}else if(p==3){
+  phenoDat$phenoStatus[phenoDat$phenophaseIntensity=="5-24%"] <- "yes"
+}
+
+subPhenoDat <- phenoDat %>% filter(phenoStatus=="yes") %>%
+  group_by(year,individualID) %>% slice(1:1) %>% 
+  dplyr::select(year,date,individualID) 
+phenoDat <- left_join(phenoDat,subPhenoDat,by=c('year','individualID'))
+#phenoDat <- phenoDat %>% filter((date.x <= date.y),!is.na(height))
+phenoDat <- phenoDat %>% filter((date.x <= date.y & date.x >= (as.Date(date.y)-14)),!is.na(height))
+names(phenoDat)[names(phenoDat)=="date.x"] <- "date"
+
+phenoDat <- phenoDat %>% filter(growthForm=="Deciduous broadleaf") %>%
+  dplyr::select(siteID,date,year,phenoStatus,height)
+
+rm(subPhenoDat)
+
+print("loaded PhenoDat")
+
+#Load Temperature ----
+dataName="NEON_SingleAirTemperature"
+funName="mean"
+
+for(baseTemp in seq(0,20,5)){
+  #baseTemp <- 0
+  print(baseTemp)
+  allWeekDatList <- lapply(X=NEON_siteNames,FUN=readTotalMetDataFiles,p=p,
+                           dataName=dataName,dataPath=dataPath,funName=funName,baseTemp=baseTemp)
+  allWeeks <-rbindlist(allWeekDatList,fill=TRUE)
[…]

### 2023-03-27 identifyingDroughtsAtNEONsites.R

@@ -1,0 +1,46 @@
+library(sf)
+library(tidyverse)
+dataPath <- "Data/"
+
+siteData <- read_csv(paste0(dataPath,'NEON_Field_Site_Metadata_20220412.csv'))
+siteData <- siteData %>% filter(field_site_type%in%c("Gradient Terrestrial","Core Terrestrial"))
+
+divs <- read_sf('CONUS_CLIMATE_DIVISIONS.shp/GIS.OFFICIAL_CLIM_DIVISIONS.shp')
+siteData <- siteData %>% filter(field_site_type%in%c("Gradient Terrestrial","Core Terrestrial"))
+
+pnts <- data.frame(
+  "x" = siteData$field_longitude,
+  "y" = siteData$field_latitude)
+
+# create a points collection
+pnts_sf <- do.call("st_sfc",c(lapply(1:nrow(pnts), 
+                                     function(i) {st_point(as.numeric(pnts[i, ]))}), list("crs" = 4326))) 
+
+pnts_trans <- st_transform(pnts_sf, 2163) # apply transformation to pnts sf
+tt1_trans <- st_transform(divs, 2163)      # apply transformation to polygons sf
+
+# intersect and extract state name
+pnts$region <- apply(st_intersects(tt1_trans, pnts_trans, sparse = FALSE), 2, 
+                     function(col) { 
+                       tt1_trans[which(col), ]$CLIMDIV
+                     })
+pnts <- cbind(pnts,siteData$field_site_id)
+#pnts$region[[c(2,5,9,13,15,20,30,41)]] <- NA
+for(i in c(2,5,9,13,15,20,30,41)){
+  pnts$region[[i]] <- NA
+}
+
+pnts <- pnts %>% mutate(region=as.character(unlist(region)),siteID=siteData$field_site_id) %>%
+  dplyr::select(siteID,region)
+
+droughtData <- read.table('climdiv-pdsidv-v1.0.0-20230206.txt')
+colnames(droughtData) <- c("ID",seq(1,12))
+droughtData$ID[nchar(droughtData$ID)<10] <- paste0("0",droughtData$ID[nchar(droughtData$ID)<10])
+droughtData <- droughtData %>% mutate(year=substr(ID,7,10),region=substr(ID,1,4)) %>%
+  dplyr::select(-ID)
+combinedDrought <- left_join(pnts,droughtData,by="region")
+
+write.csv(combinedDrought,file="droughtsAtNEON.csv",row.names = FALSE,quote=FALSE)
+
+
+

### 2023-03-27 verticallyScaleMetData.R

@@ -1,0 +1,49 @@
+#Looking into vertically scaling weather data
+#Look at if the temperature data along the tower is all taken together
+library('broom')
+
+tempDat <- read.csv('Data/NEON_SingleAirTemperatureALLdata.csv')
+tempDat <- tempDat %>% filter(finalQF==0) %>% filter(!is.na(tempSingleMean))
+fittedModelDat <- tempDat %>% group_by(siteID,startDateTime) %>% mutate(n=n()) %>% filter(n>1)
+
+fittedModels <- fittedModelDat %>% group_by(siteID,startDateTime) %>% 
+  do(model = lm(tempSingleMean ~ verticalPosition,data=.))
+
+fittedModelsTidied <- fittedModels %>% summarise(tidy(model))
+fittedModelsFit <- fittedModels %>% summarise(glance(model))
+fittedModels <- cbind(fittedModels,fittedModelsFit$r.squared)
+
+newDat <- matrix(nrow=nrow(fittedModelsTidied),ncol=3)
+
+ct <- 1
+for(i in 1:nrow(fittedModels)){
+  if(i%%1000==0){
+    print(i)
+  }
+  newDat[ct,1] <- as.character(fittedModels[i,1])
+  newDat[ct,2] <- as.character(fittedModels[i,2])
+  newDat[ct,3] <- as.character(fittedModels[i,4])
+  ct <- ct + 1
+  newDat[ct,1] <- as.character(fittedModels[i,1])
+  newDat[ct,2] <- as.character(fittedModels[i,2])
+  newDat[ct,3] <- as.character(fittedModels[i,4])
+  ct <- ct + 1
+}
+colnames(newDat) <- c('siteID','startDateTime','r.squared')
+fittedModelSummary <- cbind(newDat,fittedModelsTidied)
+save(fittedModelSummary,file="fittedAirTempModels.RData")
+
+
+load("fittedAirTempModels.RData")
+
+for(s in seq_along(NEON_siteNames)){
+  site <- NEON_siteNames[s]
+  siteDat <- fittedModelSummary %>% filter(siteID==site)
+  plot(density(as.numeric(siteDat$r.squared)),main=site)
+  siteDat <- siteDat %>% filter(r.squared>0.9,term=="verticalPosition") %>% 
+    mutate(date=as.Date(startDateTime)) %>%
+    group_by(date)%>%summarise(n=n())
[…]

### 2023-03-27 combineAllData.R
Cleaned up combineData and added some models

@@ -1,14 +1,13 @@
 #Load all NEON data 
 source('sharedVariables.R')
 source('NEON_Data_DownloadAndProcess.R')
-#library(data.table)
 source('computeWeeklyMetData.R')
-library('purrr')
 
-#NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
 p=2 #For only breaking leaf buds 
 p=3 #For colored leaves
-#phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
+baseTemp=20
+
+#NEON Phenology Observations (and vegetation structural characteristics and mycorrhizae association) ----
 phenoDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_AllStatus_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
 phenoDat$phenoStatus <- "no"
 if(p==2){
@@ -17,25 +16,25 @@ if(p==2){
   phenoDat$phenoStatus[phenoDat$phenophaseIntensity=="5-24%"] <- "yes"
 }
 
-
 subPhenoDat <- phenoDat %>% filter(phenoStatus=="yes") %>%
-  group_by(year,individualID) %>% slice(1:1) %>% 
-  dplyr::select(year,date,individualID) 
-phenoDat <- left_join(phenoDat,subPhenoDat,by=c('year','individualID'))
+  group_by(year,individualID,height) %>% slice(1:1) %>% 
+  dplyr::select(year,date,individualID,height) 
+phenoDat <- left_join(phenoDat,subPhenoDat,by=c('year','individualID','height'))
 phenoDat <- phenoDat %>% filter(date.x <= date.y,!is.na(height))
 names(phenoDat)[names(phenoDat)=="date.x"] <- "date"
 
 phenoDat <- phenoDat %>%
-  dplyr::select(siteID,year,date,dayOfYear,individualID,phenoStatus,canopyPosition,plantStatus,stemDiameter,
-                maxCanopyDiameter,percentCover,height,scientificName,growthForm,Mycorrhizal.type)
+  dplyr::select(siteID,year,date,dayOfYear,individualID,phenoStatus,canopyPosition,plantStatus,
[…]

### 2023-03-27 createJAGSmodel_drought.R

@@ -1,0 +1,99 @@
+library(rjags)
+library(runjags)
+source('sharedVariables.R')
+source('runMCMC_Model.R')
+set.seed(0)
+
+
+#Load and Organize Data ----
+p=3
+load(file=paste0("allCombinedNEONDat_",gsub(" ","",NEON_phenophase_names[p]),".RData")) #Loaded as allComDat
+
+selectAllComDat <- allComDat %>% filter(Mycorrhizal.type%in%c("AM","EcM"))
+
+subSelectAllComDat <- selectAllComDat[sample.int(nrow(selectAllComDat),10000,replace=FALSE),]
+
+drought <- cbind(subSelectAllComDat$individualID,subSelectAllComDat$soilMoisture)
+colnames(drought) <- c("individualID","drought")
+drought=as.data.frame(drought) %>% group_by(individualID) %>% mutate(rowNum=row_number()) %>%
+  pivot_wider(names_from=rowNum,values_from=drought)
+drought$individualID <- NULL
+
+CDD <- cbind(subSelectAllComDat$individualID,subSelectAllComDat$CDD_10)
+colnames(CDD) <- c("individualID","CDD")
+CDD=as.data.frame(CDD) %>% group_by(individualID) %>% mutate(rowNum=row_number()) %>%
+  pivot_wider(names_from=rowNum,values_from=CDD)
+CDD$individualID <- NULL
+
+phenoStatus <- cbind(subSelectAllComDat$individualID,subSelectAllComDat$phenoStatus)
+colnames(phenoStatus) <- c("individualID","phenoStatus")
+numObs <- as.data.frame(phenoStatus) %>% group_by(individualID) %>% summarize(n=n())
+
+phenoStatus=as.data.frame(phenoStatus) %>% group_by(individualID) %>% mutate(rowNum=row_number()) %>%
+  pivot_wider(names_from=rowNum,values_from=phenoStatus)
+numObs <- left_join(phenoStatus,numObs,by="individualID")
+numObs <- numObs$n
+
+phenoStatus$individualID <- NULL
+
+JAGSdat <- list(drought=matrix(as.numeric(as.matrix(drought)),ncol=ncol(drought))[numObs>10,],
+                CDD=matrix(as.numeric(as.matrix(CDD)),ncol=ncol(CDD))[numObs>10,],
[…]

### 2023-03-27 effectOfDroughtOnCDD.R

@@ -1,0 +1,120 @@
+#Drought Differences on CDD Needed for Senescence
+source('sharedVariables.R')
+library(caTools)
+library('xgboost')
+library(randomForest)
+library('mgcv')
+options(stringsAsFactors = FALSE)
+
+set.seed(0)
+
+#Load Data and General Prep ----
+p=3
+load(file=paste0("allCombinedNEONDat_",gsub(" ","",NEON_phenophase_names[p]),".RData")) #Loaded as allComDat
+
+subDat <- allComDat %>% filter(phenoStatus==1) %>%
+  dplyr::select(siteID,year,daylength,individualID,scientificName,Mycorrhizal.type,CDD_closest,soilMoisture,height,canopyPosition)
+
+#Basic T-Tests ----
+subDat2 <- subDat %>% group_by(individualID,year,height) %>% unique() %>%
+  mutate(droughtBin=cut(drought,breaks=c(-6,-2,0,8))) %>%
+  group_by(siteID,Mycorrhizal.type,individualID,droughtBin) %>% 
+  summarize(meanCDD=mean(CDD_closest),n=n())
+
+subDat3 <- pivot_wider(subDat2,names_from=droughtBin,values_from=meanCDD)
+#names(subDat3) <- c('siteID',"Mycorrhizal.type","individualID",'DroughtYear',"Good","Exclude","NA")
+# names(subDat3)[names(subDat3)=="(-6,-2]"] <- "DroughtYear"
+# names(subDat3)[names(subDat3)=="(-1,4]"] <- "Good"
+# names(subDat3)[names(subDat3)=="(-2,-1]"] <- "Exclude"
+
+names(subDat3)[names(subDat3)=="(-6,-2]"] <- "DroughtYear"
+names(subDat3)[names(subDat3)=="(0,8]"] <- "Good"
+names(subDat3)[names(subDat3)=="(-2,0]"] <- "Exclude"
+#names(subDat3) <- c('siteID',"Mycorrhizal.type","individualID","Exclude","DroughtYear","Good","NA")
+
+subDat4 <- subDat3 %>% summarize(droughtDiffCDD=Good-DroughtYear) %>% filter(!is.na(droughtDiffCDD))
+droughtDiff_AM <- subDat4 %>% filter(Mycorrhizal.type=="AM")
+droughtDiff_AM <- droughtDiff_AM$droughtDiffCDD
[…]

### 2023-03-27 createJAGSmodel_drought.R
updated JAGS model

@@ -8,8 +8,8 @@ set.seed(0)
 #Load and Organize Data ----
 p=3
 load(file=paste0("allCombinedNEONDat_",gsub(" ","",NEON_phenophase_names[p]),".RData")) #Loaded as allComDat
-
-selectAllComDat <- allComDat %>% filter(Mycorrhizal.type%in%c("AM","EcM"))
+allComDat$phenoStatus <- as.numeric(as.character(allComDat$phenoStatus))
+selectAllComDat <- allComDat %>% filter(Mycorrhizal.type%in%c("AM","EcM"),!is.na(soilMoisture))
 
 subSelectAllComDat <- selectAllComDat[sample.int(nrow(selectAllComDat),10000,replace=FALSE),]
 
@@ -57,26 +57,26 @@ generalModel = "
 model {
 #### Process Model
 for(i in 1:N){
-CDDCrit[i] ~ dnorm(CDDCrit_mean,CDDCrit_tau) #Random effect
+#CDDCrit[i] ~ dnorm(CDDCrit_mean,CDDCrit_tau) #Random effect
+k[i] ~ dnorm(k_mean,k_tau) #Random effect
 for(j in 1:numObs[i]){    
-phenoProb[i,j] <- ifelse(CDD[i,j]>CDDCrit[i],p,(1-p)) #1 for senescence and 0 for no
+phenoProb[i,j] <- ifelse(CDD[i,j]>CDDCrit[i,j],p,(1-p)) #1 for senescence and 0 for no
 phenoStatus[i,j] ~ dbern(phenoProb[i,j]) 
+CDDCrit[i,j] <- exp(k[i]*(drought[i,j]))
 }
 }
-
-#CDDCrit[i] <- exp(k*(drought[i]))
 
 #### Priors
-#k ~ dunif(0.01,1)
+k_mean ~ dunif(0.01,10)
+k_tau ~ dunif(0.1,50)
 #CDDmean ~ dunif(0,1000)
 #tau ~ dunif(0,0.01)
 #CDDCrit ~dunif(0,400)
-CDDCrit_mean ~ dunif(0,400)
-CDDCrit_tau ~ dunif(0,0.00001)
+#CDDCrit_mean ~ dunif(0,400)
+#CDDCrit_tau ~ dunif(0,0.00001)
 p ~ dbeta(10,1)
 }
 "
-
 
 #Run Model ----
 nchain=5
@@ -84,7 +84,8 @@ j.model   <- jags.model(file = textConnection(generalModel),
[…]
